---
title: "Analysis Code"
author: "Lorenzo Ricolfi"
output:
  html_document:
    code_folding: show
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    toc_depth: 3
    number_sections: no
    theme: cerulean
  pdf_document:
    toc: yes
    toc_depth: '2'
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#devtools::install_github("EIvimeyCook/ShinyDigitise")
library(tidyr)
library(dplyr)
library(here)
library(lmtest)
library(data.table)
library(metaDigitise)
library(sandwich)
library(metafor)
library(orchaRd)
library(ggplot2)
#library(shinyDigitise)
```

# Raw data extracion - MetaDigitise
```{r, eval=FALSE}
dat <- metaDigitise("~/PhD/GitHub/PFAS_Trophic_Magnification/metaDigitise")
dat <- shinyDigitise("~/PhD/GitHub/PFAS_Trophic_Magnification/metaDigitise")
#write.csv(dat, file = "metaDigitise/MetaDigitise_Martin_2004_10r.csv")
```

# Data wrangling
```{r}
# study_data <- read.csv(here("data/study_data.csv"))
# fw_data <- read.csv(here("data/fw_data.csv"))
# PFAS_data <- read.csv(here("data/PFAS_data.csv"))
# TMF_data <- read.csv(here("data/TMF_data.csv"))
# appr_data <- read.csv(here("data/appr_data.csv"))

TMF_data <- read.csv(here("data/data_draft.csv"))
FW_data <- read.csv(here("data/fw_data_draft.csv"))

TMF_data <- TMF_data %>%
  mutate(across(everything(), ~ ifelse(. == "na", NA, .)))

function1 <- function(data) {
  # Convert necessary columns to numeric, handling any potential issues
  data <- data %>%
    mutate(
      TMF_lower_95CI = as.numeric(TMF_lower_95CI),
      TMF_upper_95CI = as.numeric(TMF_upper_95CI),
      TMF_se = as.numeric(TMF_se),
      TMS_lower_95CI = as.numeric(TMS_lower_95CI),
      TMS_upper_95CI = as.numeric(TMS_upper_95CI),
      TMS_se = as.numeric(TMS_se),
      TMS = as.numeric(TMS),
      TMF = as.numeric(TMF),
      pvalue_adj = as.numeric(pvalue_adj),
      TMS_calculated = as.numeric(TMS_calculated),
      TMS_se_calculated = as.numeric(TMS_se_calculated)
    ) %>%
    mutate(
      TMF_se = ifelse(is.na(TMF_se) & !is.na(TMF_lower_95CI) & !is.na(TMF_upper_95CI),
                      (TMF_upper_95CI - TMF_lower_95CI) / 1.96, TMF_se),
      TMS_se = ifelse(is.na(TMS_se) & !is.na(TMS_lower_95CI) & !is.na(TMS_upper_95CI),
                      (TMS_upper_95CI - TMS_lower_95CI) / 1.96, TMS_se),
      TMF = ifelse(is.na(TMF) & !is.na(TMS),
                   ifelse(TMF_formula == "10^slope", 10^TMS, exp(TMS)), TMF),
      z_value = ifelse(is.na(TMS_se) & !is.na(pvalue_adj),
                       qnorm(1 - pvalue_adj / 2), NA),
      TMS = ifelse(is.na(TMS) & !is.na(TMF),
                   ifelse(TMF_formula == "10^slope", log10(TMF), log(TMF)), TMS),
      TMS_se = ifelse(is.na(TMS_se) & !is.na(TMS) & !is.na(z_value),
                      TMS / z_value, TMS_se),
      TMS_se = ifelse(is.na(TMS) & !is.na(TMF) & !is.na(z_value),
                      ifelse(TMF_formula == "10^slope", log10(TMF) / z_value, log(TMF) / z_value), TMS_se),
      TMF_se = ifelse(is.na(TMF_se) & !is.na(TMS_se),
                      ifelse(TMF_formula == "10^slope", 10^TMS_se, exp(TMS_se)), TMF_se),
      TMF = ifelse(is.na(TMF) & !is.na(TMS_calculated),
                   ifelse(TMF_formula == "10^slope", 10^TMS_calculated, exp(TMS_calculated)), TMF),
      TMF_se = ifelse(is.na(TMF_se) & !is.na(TMS_se_calculated),
                      ifelse(TMF_formula == "10^slope", 10^TMS_se_calculated, exp(TMS_se_calculated)), TMF_se),
      TMF = ifelse(is.na(TMF) & !is.na(TMS),
                   ifelse(TMF_formula == "10^slope", 10^TMS, exp(TMS)), TMF),
      TMF_se = ifelse(is.na(TMF_se) & !is.na(TMS_se),
                      ifelse(TMF_formula == "10^slope", 10^TMS_se, exp(TMS_se)), TMF_se)
    )
  
  return(data)
}

# Apply the function
TMF_data <- function1(TMF_data)

# Count the number of rows with non-NA values in both TMF and TMF_se
TMF_data %>%
  filter(!is.na(TMF) & !is.na(TMF_se)) %>%
  nrow()
# [1] 879
# Count the number of rows with non-NA values in TMF
TMF_data %>%
  filter(!is.na(TMF)) %>%
  nrow()
# [1] 916

# Filter rows with NA in either TMF or TMF_se
TMF_data_na_rows <- TMF_data %>%
  filter(is.na(TMF) | is.na(TMF_se)) %>% 
  as.data.table()

TMF_data <- TMF_data %>%
  filter(!is.na(TMF) | !is.na(TMF_se)) %>%
  mutate(
    ln_TMF = log(TMF),
    ln_TMF_se = TMF_se / TMF # Taylor approximation
  )
```

# Intercept meta-analytic model

Determine the random effect structure

The random effects model is used to account for between-study heterogeneity, which is the variability in effect sizes among the studies being analyzed. When determining the random effect structure, we are trying to identify the sources of this heterogeneity and to quantify the degree to which it is present in the data.

```{r, eval=FALSE}
ma_all_random_effects <- rma.mv(yi = ln_TMF,
                                V = ln_TMF_se,
             random = list(~1|Study_ID, # Between-study effect
                           ~1|FW_ID, # Between food webs effect
                           ~1|PFAS_ID, # Between type of PFAS effect
                           ~1|TMS_ID # Within-study effect
              ),
             test = "t",
             data = TMF_data)

save(ma_all_random_effects, file = here("Rdata", "ma_all_random_effects.RData"))
```


```{r}
load(here("RData", "ma_all_random_effects.RData"))
summary(ma_all_random_effects)
i2_ml(ma_all_random_effects)
#   I2_Total I2_Study_ID    I2_FW_ID  I2_PFAS_ID   I2_TMS_ID 
#  66.209617   20.694604   10.453998   27.188562    7.872453
I2 <- orchaRd::i2_ml(ma_all_random_effects)
orchaRd::orchard_plot(ma_all_random_effects,
             mod = "1",
             group = "Study_ID", 
             xlab = "ln_TMF",
             alpha = 1,
             trunk.size = 0.7,
             branch.size = 1.5,
             twig.size = 0.3,
             k.pos = "right",
             colour = FALSE,
             fill = FALSE) +  
  annotate(geom = "text",
           x = 1.2,
           y = 2.8, 
           label = paste0("italic(I)^{2} == ", round(I2[1],4)),
           color ="black",
           parse = TRUE) +
  
  scale_size_continuous(range = c(1, 7)) + # change point scaling
  theme(panel.border = element_rect(colour = "black", 
                                             fill=NA,
                                             size=1.3), # border around the plot
                 text = element_text(size = 9), # change font sizes
                 legend.title = element_text(size = 8),
                 legend.text = element_text(size = 7),
        axis.text.y = element_blank()) +
  xlab("Intercept")
```
