---
title: "Analysis Code"
author: "Lorenzo Ricolfi"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    toc_depth: 3
    number_sections: no
    theme: cerulean
  pdf_document:
    toc: yes
    toc_depth: '2'
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

The following packages are required to run the code in this script.
```{r, results='hide'}
#devtools::install_github("EIvimeyCook/ShinyDigitise")
#library(shinyDigitise)
pacman::p_load(tidyr,        # For tidying data, including reshaping and separating data into columns.
               dplyr,        # For data manipulation, including filtering, selecting, and summarizing data.
               stringr,      # For string manipulation, including pattern matching and text extraction.
               readr,        # For reading rectangular data (csv, tsv, fwf, etc.) into R efficiently.
               here,         # For constructing file paths relative to the root of the project directory.
               lmtest,       # For conducting diagnostic tests and hypothesis tests on linear models.
               dm,           # For working with data models and relational data within R.
               data.table,   # For fast and efficient data manipulation, particularly with large datasets.
               metaDigitise, # For extracting and digitizing data from plots in scientific literature.
               clubSandwich, # For computing robust standard errors in meta-analysis, particularly in clustered data.
               metafor,      # For conducting meta-analyses, including univariate and multivariate models.
               orchaRd,      # For visualizing meta-analysis results, including bubble plots and forest plots.
               ggplot2,      # For creating complex and customizable visualizations using the grammar of graphics.
               MuMIn,        # For model selection and model averaging, particularly in regression models.
               kableExtra,   # Enhances the formatting and styling capabilities of tables.
               patchwork,    # Facilitates combining multiple ggplot2 plots into a single layout.
               ggalluvial,   # Extends ggplot2 to create alluvial diagrams for categorical data flows.
               ggbreak,      # For breaking and rescaling ggplot2 axes to handle extreme values.
               rnaturalearth,# For accessing map data from Natural Earth for geographical visualizations.
               rnaturalearthdata, # Provides the datasets (map layers) used with rnaturalearth.
               officer,      # For creating and editing Microsoft Word and PowerPoint documents.
               flextable,    # For creating customizable and publication-ready tables.
               ggsci,        # Provides scientific journal and science-themed color palettes for ggplot2.
               forcats)      # For working with categorical variables (factors), including reordering and recoding.


```

```{r, eval=FALSE}
# metaDigitise and shinyDigitise for data extraction from plots
dat <- metaDigitise("~/PhD/GitHub/PFAS_Trophic_Magnification/metaDigitise")
dat <- shinyDigitise("~/PhD/GitHub/PFAS_Trophic_Magnification/metaDigitise")
```

# Data uploading and wrangling

We need to perform data wrangling to optimally structure the data for analysis. The following code chunk outlines the steps taken, along with brief descriptions of each.
```{r, results='hide', warning=FALSE}
study_data <- read.csv(here("data/study_data.csv"))
fw_data <- read.csv(here("data/fw_data.csv"))
PFAS_data <- read.csv(here("data/PFAS_data.csv"))
TMF_data <- read.csv(here("data/TMF_data.csv"))
RoB_data <- read.csv(here("data/RoB_data.csv"))

# Replacing "na" strings with actual NA values
TMF_data <- TMF_data %>%
  mutate(across(everything(),
                ~ ifelse(. == "na", NA, .)))

function1 <- function(data) {
  # Convert necessary columns to numeric, handling any potential issues
  data <- data %>%
    mutate(
      TMF_lower_95CI = as.numeric(TMF_lower_95CI),
      TMF_upper_95CI = as.numeric(TMF_upper_95CI),
      TMF_se = as.numeric(TMF_se),
      TMS_lower_95CI = as.numeric(TMS_lower_95CI),
      TMS_upper_95CI = as.numeric(TMS_upper_95CI),
      TMS_se = as.numeric(TMS_se),
      TMS = as.numeric(TMS),
      TMF = as.numeric(TMF),
      pvalue_adj = as.numeric(pvalue_adj),
      TMS_calculated = as.numeric(TMS_calculated),
      TMS_se_calculated = as.numeric(TMS_se_calculated)
    ) %>%
    mutate(
      # Calculate TMF_se if missing and TMF 95% CI is available
      TMF_se = ifelse(is.na(TMF_se) & !is.na(TMF_lower_95CI) & !is.na(TMF_upper_95CI),
                      (TMF_upper_95CI - TMF_lower_95CI) / 1.96, TMF_se),
      # Calculate TMS_se if missing and TMS 95% CI is available
      TMS_se = ifelse(is.na(TMS_se) & !is.na(TMS_lower_95CI) & !is.na(TMS_upper_95CI),
                      (TMS_upper_95CI - TMS_lower_95CI) / 1.96, TMS_se),
      # Calculate TMF if missing and TMS is available
      TMF = ifelse(is.na(TMF) & !is.na(TMS),
                   ifelse(TMF_formula == "10^slope", 10^TMS, exp(TMS)), TMF),
      # Calculate z_value if TMS_se is missing and pvalue_adj is available 
      z_value = ifelse(is.na(TMS_se) & !is.na(pvalue_adj),
                       qnorm(1 - pvalue_adj / 2), NA),
      # Calculate TMS if missing and TMF is available
      TMS = ifelse(is.na(TMS) & !is.na(TMF),
                   ifelse(TMF_formula == "10^slope", log10(TMF), log(TMF)), TMS),
      # Calculate TMS_se if missing, TMS, and z_value are available
      TMS_se = ifelse(is.na(TMS_se) & !is.na(TMS) & !is.na(z_value),
                      TMS / z_value, TMS_se),
      # Calculate TMS_se if TMS is missing, but TMF and z_value are available
      TMS_se = ifelse(is.na(TMS) & !is.na(TMF) & !is.na(z_value),
                      ifelse(TMF_formula == "10^slope", log10(TMF) / z_value, log(TMF) / z_value), TMS_se),
      # Calculate TMF_se if missing and TMS_se is available 
      TMF_se = ifelse(is.na(TMF_se) & !is.na(TMS_se),
                      ifelse(TMF_formula == "10^slope", 10^TMS_se, exp(TMS_se)), TMF_se),
      # Calculate TMF if missing and TMS_calculated is available
      TMF = ifelse(is.na(TMF) & !is.na(TMS_calculated),
                   ifelse(TMF_formula == "10^slope", 10^TMS_calculated, exp(TMS_calculated)), TMF),
      # Calculate TMF_se if missing and TMS_se_calculated is available
      TMF_se = ifelse(is.na(TMF_se) & !is.na(TMS_se_calculated),
                      ifelse(TMF_formula == "10^slope", 10^TMS_se_calculated, exp(TMS_se_calculated)), TMF_se)
    )
  # Return the modified data
  return(data)
}

# Apply the function
TMF_data <- function1(TMF_data)

# Count the number of rows with non-NA values in both TMF and TMF_se
TMF_data %>%
  filter(!is.na(TMF) & !is.na(TMF_se)) %>%
  nrow()
# [1] 1009


TMF_data <- TMF_data %>%
  filter(!is.na(TMF) | !is.na(TMF_se)) %>%
  mutate(
    ln_TMF = log(TMF),
    ln_TMF_se = TMF_se / TMF, # Taylor approximation
    Sample_type = factor(Sample_type), 
    Sample_type = relevel(Sample_type, ref = "whole-organisms only")
  ) 
  
# Data cleaning
TMF_data <- TMF_data %>% 
  select(-(starts_with("Initial"))) %>% 
  select(-(starts_with("X"))) %>% 
  select(-(ends_with("comment"))) %>%  #
  filter(!(Study_ID %in% c("S_018", "S_055"))) %>% 
  select(-("Study_ID")) %>% 
  select(-("Censored_data_strategy")) %>% 
  select(-("Undetected_strategy_LOQ")) %>%
  select(-("Undetected_strategy_LOD"))

PFAS_data <- PFAS_data %>% 
  select(-(starts_with("Initial"))) %>% 
  select(-(starts_with("X"))) %>% 
  select(-(ends_with("comment"))) 

fw_data <- fw_data %>% 
  select(-(starts_with("Initial"))) %>% 
  select(-(starts_with("X"))) %>% 
  select(-(ends_with("comment"))) %>% 
  filter(!(Study_ID %in% c("S_018", "S_055"))) 

study_data <- study_data %>% 
  select(-(starts_with("Initials"))) %>% 
  select(-(starts_with("X"))) %>% 
  select(-(ends_with("comment"))) %>%  
  filter(!is.na(Study_ID) & Study_ID != "") %>%  
  mutate(Regression_variable = case_when(
    grepl("TL", Linear_regression_formula) ~ "TL",
    grepl("δ15N", Linear_regression_formula) ~ "δ15N",
    TRUE ~ NA_character_
  )) %>%
  mutate(year_publication = as.numeric(str_extract(Author_year, "(?<=_)\\d{4}"))) %>% 
  filter(!(Study_ID %in% c("S_018", "S_055"))) 

RoB_data <- RoB_data %>%
  select(-(starts_with("Initials"))) %>%
  select(-(ends_with("comment"))) %>% 
  select(-(ends_with("details"))) %>% 
  select(-(starts_with("X"))) %>% 
  filter(!(Study_ID %in% c("S_018", "S_055"))) %>%
  select(-("Study_ID"))

TMF_data <- TMF_data %>%
  # Correct mislabelings in the PFAS_ID column (TMF_data data table)
  mutate(PFAS_ID = case_when(
    PFAS_ID == "PFDoDa" ~ "PFDoDA",
    PFAS_ID == "br-PFDoDa" ~ "br-PFDoDA",
    TRUE ~ PFAS_ID
  )) %>% 
  # Filter the data to remove rows where Sample_type is NA or an empty string
  filter(!is.na(Sample_type) & Sample_type != "")

PFAS_data <- PFAS_data %>%
  # Correct mislabeling in the PFAS_ID column (PFAS_data data table)
  mutate(PFAS_ID = case_when(
    PFAS_ID == "cis-PFECHS " ~ "cis-PFECHS",
    TRUE ~ PFAS_ID
  ))

# Fixing latitude and longitude data
fw_data <- fw_data %>%
  # Trim whitespace
  mutate(Latitude_DD = str_trim(Latitude_DD)) %>%
  # Remove the ° symbol and any non-numeric characters
  mutate(Latitude_DD = str_replace_all(Latitude_DD, "[^0-9.-]", "")) %>%
  # Convert to numeric
  mutate(Latitude_DD = as.numeric(Latitude_DD)) %>%
  # Trim whitespace
  mutate(Longitude_DD = str_trim(Longitude_DD)) %>%
  # Remove the ° symbol and any non-numeric characters
  mutate(Longitude_DD = str_replace_all(Longitude_DD, "[^0-9.-]", "")) %>%
  # Convert to numeric
  mutate(Longitude_DD = as.numeric(Longitude_DD))

fw_data <- fw_data %>%
  mutate(Breathing_type_fw = case_when(
    Species_composition %in% c(
      "fish only"
    ) ~ "water-breathing only",
    
    Species_composition %in% c(
      "fish and other species", "no fish"
    ) ~ "not water-breathing only",
    
    TRUE ~ NA_character_  
  )) %>% 
  mutate(
    Ecosystem = factor(Ecosystem),
    Ecosystem = relevel(Ecosystem, ref = "marine"))
    

fw_data <- fw_data %>%
  mutate(Breathing_type = case_when(
    Species_highest_TL %in% c(
      "Delphinapterus leucas", "Delphinus truncatus", "Larus hyperboreus", 
      "Channa asiatica", "Argyrosomus regius", "Larus crassirostris", 
      "Neophocaena", "Pusa hispida", "Sousa chinensis", 
      "Catharacta maccormicki", "Buteo hemilasius", "Canis lupus", 
      "Accipiter nisus", "Accipiter cooperii"
    ) ~ "Air breathing",
    
    Species_highest_TL %in% c(
      "Boreogadus saida", "Barbus barbus", "Squalius cephalus", 
      "Cololabis saira", "Salvelinus alpinus", "Salvelinus namaycush", 
      "Micropterus salmoides", "Notothenia coriiceps", "Esox lucius", 
      "Pagrosomus major", "Lateolabrax japonicas", "Thryssa mysiax", 
      "Trichiurus lepturus", "Hexagrammos otakii", "Rapana venosa", 
      "Sander lucioperca", "Salvelinus fontinalis", "Morone saxatilis", 
      "Channa argus", "Micropterus dolomieu", "Johnius belengeri", 
      "Trematomus eulepidotus", "Miichthys miiuy", "Ophiocephalus argus Cantor", 
      "Liza carinatus", "Sander vitreus", "Sebastes schlegeli", 
      "Hemibarbus maculates", "Merlangius merlangus", "Gaidropsarus vulgaris", 
      "Clarias macrocephalus", "Carassius auratus", "Oreochromis niloticus", 
      "Phoca vitulina", "Parabramis pekinensis", "Lateolabrax sp.", 
      "Sarda sarda"
    ) ~ "Water breathing",
    
    Species_highest_TL %in% c(
      "Hydropsychidae", "Polychaeta", "Zygoptera", "Lithobiomorph", 
      "Araneae"
    ) ~ "Water breathing through skin",  # Many aquatic larvae breathe through skin

    TRUE ~ NA_character_  # Assign NA for any species not in the lists
  ))

# The following function finds the highest and lowest trophic level processing TL_values for each row. Then, we also calculate the length of the food web using these values.

process_TL_extremes <- function(TL_string) {
  # Split the string by commas
  values <- unlist(strsplit(TL_string, ","))
  
  # Process each value
  processed_values <- sapply(values, function(value) {
    value <- str_trim(value) # Trim any whitespace
    
    # Skip processing if the value is NA or empty
    if (is.na(value) || value == "") {
      return(NA)
    }
    
    # Check if it's a range (e.g., 3.12-3.64)
    if (str_detect(value, "-")) {
      range_values <- as.numeric(unlist(strsplit(value, "-")))
      return(range_values)
    
    # Check if it's a value with error (e.g., 1.83±0.09)
    } else if (str_detect(value, "±")) {
      mean_value <- as.numeric(unlist(strsplit(value, "±"))[1])
      return(mean_value)
    
    # Otherwise, it's a simple numeric value
    } else {
      return(as.numeric(value))
    }
  })
  
  # Unlist the processed values and remove NAs
  processed_values <- unlist(processed_values)
  processed_values <- processed_values[!is.na(processed_values)]
  
  # Return the highest and lowest values, handle empty processed_values
  if (length(processed_values) == 0) {
    return(list(highest = NA, lowest = NA))
  } else {
    return(list(highest = max(processed_values, na.rm = TRUE), 
                lowest = min(processed_values, na.rm = TRUE)))
  }
}

# Apply the function to each row in the TL_values column to get TL_highest and TL_lowest
fw_data <- fw_data %>%
  mutate(TL_extremes = lapply(TL_values, process_TL_extremes)) %>%
  mutate(TL_highest = sapply(TL_extremes, function(x) x$highest),
         TL_lowest = sapply(TL_extremes, function(x) x$lowest)) %>%
  select(-TL_extremes)  # Remove the temporary TL_extremes column

fw_data <- fw_data %>%
  # Create a new column for the difference
  mutate(fw_length = TL_highest - TL_lowest)

# The following code creates a data model object called data_dm_no_keys using the dm() function, with the tables st, sp, pfas, co, sa, and me.
data_dm_no_keys <- dm(study_data, PFAS_data, fw_data, TMF_data, RoB_data)
data_dm_no_keys #printing the data_dm_no_keys object, which displays the structure and content of the data model
data_dm_no_keys$study_data #accessing the study_data table from the data model using $ operator and printing it
data_dm_no_keys[c("study_data", "PFAS_data")] #accessing the columns "study_data" and "PFAS_data" from the data model using indexing and printing the corresponding data

# The following code adds primary keys to the data_dm_no_keys data model using the dm_add_pk() function. It specifies the table and the corresponding column(s) to be used as primary keys for each table. The resulting data model with only primary keys is stored in the data_dm_only_pks object and printed. Next, foreign keys are added to the data_dm_only_pks data model using the dm_add_fk() function. It specifies the table, columns, and the referenced table for each foreign key constraint. The resulting data model with both primary and foreign keys is stored in the data_dm_all_keys object and printed.
data_dm_only_pks <- data_dm_no_keys %>% 
  dm_add_pk(table = study_data, columns = Study_ID) %>%
  dm_add_pk(RoB_data, Appraisal_ID) %>% 
  dm_add_pk(PFAS_data, PFAS_ID) %>% 
  dm_add_pk(fw_data, FW_ID) %>% 
  dm_add_pk(TMF_data, TMF_ID)
data_dm_only_pks

data_dm_all_keys <- 
  data_dm_only_pks %>%
  dm_add_fk(table = fw_data, columns = Study_ID, ref_table = study_data) %>%
  dm_add_fk(table = TMF_data, columns = FW_ID, ref_table = fw_data) %>% 
  dm_add_fk(table = TMF_data, columns = PFAS_ID, ref_table = PFAS_data) %>%
  dm_add_fk(table = study_data, columns = Appraisal_ID, ref_table = RoB_data)
data_dm_all_keys

# Create a palette of 70 colors using a range from a selection of base colors
color_palette <- colorRampPalette(c("red", "blue", "green", "purple", "orange", "pink", "yellow"))(70)

# The following code creates a new table (i.e., 'TMF_data2') that merges 'study_data', 'PFAS_data', 'fw_data', and 'TMF_data' tables.
TMF_data2 <- 
  data_dm_all_keys %>%
  dm_select_tbl(TMF_data, RoB_data, fw_data, PFAS_data, study_data) %>%
  dm_flatten_to_tbl(.start = TMF_data, .recursive = TRUE, .join = left_join) 

colnames(TMF_data2)
# Count the number of studies with non-NA values in both TMF and TMF_se
TMF_data2 %>%
  filter(!is.na(TMF) & !is.na(TMF_se)) %>%
  distinct(Study_ID) %>%
  count()
# [1] 64

# Save the table
#write.csv(TMF_data2, here("Rdata/TMF_data2.csv"), row.names = FALSE)
```

```{r, echo=FALSE}
# Data model visualization:
figS23 <- data_dm_all_keys %>% 
  dm_draw()
 # Data model integrity check:
data_dm_all_keys %>% 
  dm_examine_constraints()
```

# VCV matrix

The following code creates a variance-covariance matrix (VCV) using the vcalc function:
```{r}
VCV <- vcalc(vi = TMF_data2$ln_TMF_se^2, #Specifies the variance of the effect sizes
             cluster = TMF_data2$FW_ID, #Indicates the clustering variable
             obs = TMF_data2$TMF_ID, #Identifies each unique observation by its TMF_ID, allowing the function to calculate covariances between effect sizes that share a cluster.
             rho = 0.5) #Sets the assumed correlation between effect sizes within the same cluster. This correlation reflects how much the effect sizes are expected to covary within the same food web.
```

# Functions

The following chunks modify the OrchaRd plot function to display model outputs on the natural log scale (ln_TMF) while presenting the plots on the original scale (TMF), enhancing the visual interpretation of the results, along with minor aesthetic changes. The last chunk modifies the bubble_plot function for minor aesthetic changes. The code creates 3 modified functions: orchard_plot_new, orchard_plot_new2, and bubble_plot_new.

```{r, warning=FALSE}
orchard_plot_new <- function (object, mod = "1", group, xlab, N = NULL, alpha = 0.5, 
    angle = 90, cb = TRUE, k = TRUE, g = TRUE, tree.order = NULL, 
    trunk.size = 1, branch.size = 1.2, twig.size = 0.5, transfm = c("none", 
        "tanh", "invlogit", "percent", "percentr"), condition.lab = "Condition", 
    legend.pos = c("bottom.right", "bottom.left", "top.right", 
        "top.left", "top.out", "bottom.out", "none"), k.pos = c("right", 
        "left", "none"), colour = FALSE, fill = TRUE, weights = "prop", 
    by = NULL, at = NULL, upper = TRUE, flip = TRUE) 
{
    transfm <- match.arg(NULL, choices = transfm)
    legend.pos <- match.arg(NULL, choices = legend.pos)
    k.pos <- match.arg(NULL, choices = k.pos)
    if (any(class(object) %in% c("robust.rma", "rma.mv", "rma", 
        "rma.uni"))) {
        if (mod != "1") {
            results <- orchaRd::mod_results(object, mod, group, 
                N, by = by, at = at, weights = weights, upper = upper)
        }
        else {
            results <- orchaRd::mod_results(object, mod = "1", 
                group, N, by = by, at = at, weights = weights, 
                upper = upper)
        }
    }
    if (any(class(object) %in% c("orchard"))) {
        results <- object
    }
    mod_table <- results$mod_table
    data_trim <- results$data
    data_trim$moderator <- factor(data_trim$moderator, levels = mod_table$name, 
        labels = mod_table$name)
    data_trim$scale <- (1/sqrt(data_trim[, "vi"]))
    legend <- "Precision (1/SE)"
    if (!is.null(tree.order) & length(tree.order) != nlevels(data_trim[, 
        "moderator"])) {
        stop("Length of 'tree.order' does not equal number of categories in moderator")
    }
    if (!is.null(tree.order)) {
        data_trim$moderator <- factor(data_trim$moderator, levels = tree.order, 
            labels = tree.order)
        mod_table <- mod_table %>% dplyr::arrange(factor(name, 
            levels = tree.order))
    }
    if (is.null(N) == FALSE) {
        data_trim$scale <- data_trim$N
        legend <- paste0("Sample Size ($\\textit{N}$)")
    }
    if (transfm == "tanh") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- Zr_to_r(mod_table[, cols])
        data_trim$yi <- Zr_to_r(data_trim$yi)
        label <- xlab
    }
    if (transfm == "invlogit") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- lapply(mod_table[, cols], function(x) metafor::transf.ilogit(x))
        data_trim$yi <- metafor::transf.ilogit(data_trim$yi)
        label <- xlab
    }
    if (transfm == "percentr") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- lapply(mod_table[, cols], function(x) (exp(x) - 
            1) * 100)
        data_trim$yi <- (exp(data_trim$yi) - 1) * 100
        label <- xlab
    }
    if (transfm == "percent") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- lapply(mod_table[, cols], function(x) exp(x))
        data_trim$yi <- (exp(data_trim$yi))
        label <- xlab
    }
    else {
        label <- xlab
    }
    mod_table$K <- as.vector(by(data_trim, data_trim[, "moderator"], 
        function(x) length(x[, "yi"])))
    mod_table$g <- as.vector(num_studies(data_trim, moderator, 
        stdy)[, 2])
    group_no <- length(unique(mod_table[, "name"]))
    cbpl <- c("grey69", 
                 "grey69", 
                 "grey69",
                 "grey69", 
                 "grey69", 
                 "grey69", 
                 "grey69", 
                 "grey69"
)
    if (colour == TRUE) {
        color <- as.factor(data_trim$stdy)
        color2 <- NULL
    }
    else {
        color <- data_trim$mod
        color2 <- mod_table$name
    }
    if (fill == TRUE) {
        fill <- color
    }
    else {
        fill <- NULL
    }
    if (names(mod_table)[2] == "condition") {
        condition_no <- length(unique(mod_table[, "condition"]))
        plot <- ggplot2::ggplot() + ggbeeswarm::geom_quasirandom(data = data_trim, 
            ggplot2::aes(y = yi, x = moderator, size = scale, 
                colour = color, fill = fill), alpha = alpha, 
            shape = 21) + ggplot2::geom_hline(yintercept = 1, 
            linetype = 2, colour = "red", alpha = 1, size = 0.4) + 
            ggplot2::geom_linerange(data = mod_table, ggplot2::aes(x = name, 
                ymin = lowerCL, ymax = upperCL), size = branch.size, 
                position = ggplot2::position_dodge2(width = 0.3)) + 
            ggplot2::geom_pointrange(data = mod_table, ggplot2::aes(y = estimate, 
                x = name, ymin = lowerPR, ymax = upperPR, shape = as.factor(condition), 
                fill = color2), fill = "red", size = trunk.size, position = ggplot2::position_dodge2(width = 0.3), 
                linewidth = twig.size) + ggplot2::scale_shape_manual(values = 20 + 
            (1:condition_no)) + ggplot2::theme_bw() + ggplot2::guides(fill = "none", 
            colour = "none") + ggplot2::theme(legend.position = c(0, 
            1), legend.justification = c(0, 1)) + ggplot2::theme(legend.title = ggplot2::element_text(size = 9)) + 
            ggplot2::theme(legend.direction = "horizontal") + 
            ggplot2::theme(legend.background = ggplot2::element_blank()) + 
            ggplot2::labs(y = label, x = "", size = latex2exp::TeX(legend)) + 
            ggplot2::labs(shape = condition.lab) + ggplot2::theme(axis.text.y = ggplot2::element_text(size = 10, 
            colour = "black", hjust = 0.5, angle = angle))
        if (flip) {
            plot <- plot + ggplot2::coord_flip()
        }
    }
    else {
        plot <- ggplot2::ggplot() + ggbeeswarm::geom_quasirandom(data = data_trim, 
            ggplot2::aes(y = yi, x = moderator, size = scale, 
                colour = color, fill = fill), alpha = alpha, 
            shape = 21) + ggplot2::geom_hline(yintercept = 1, 
            linetype = 2, colour = "red", alpha = 1, size = 0.4) + 
            ggplot2::geom_linerange(data = mod_table, ggplot2::aes(x = name, 
                ymin = lowerCL, ymax = upperCL), size = branch.size) + 
            ggplot2::geom_pointrange(data = mod_table, ggplot2::aes(y = estimate, 
                x = name, ymin = lowerPR, ymax = upperPR, fill = color2), fill = "red",
                size = trunk.size, linewidth = twig.size, shape = 21) + 
            ggplot2::theme_bw() + ggplot2::guides(fill = "none", 
            colour = "none") + ggplot2::theme(legend.title = ggplot2::element_text(size = 9)) + 
            ggplot2::theme(legend.direction = "horizontal") + 
            ggplot2::theme(legend.background = ggplot2::element_blank()) + 
            ggplot2::labs(y = label, x = "", size = latex2exp::TeX(legend)) + 
            ggplot2::theme(axis.text.y = ggplot2::element_text(size = 10, 
                colour = "black", hjust = 0.5, angle = angle))
        if (flip) {
            plot <- plot + ggplot2::coord_flip()
        }
    }
    if (legend.pos == "bottom.right") {
        plot <- plot + ggplot2::theme(legend.position = c(1, 
            0), legend.justification = c(1, 0))
    }
    else if (legend.pos == "bottom.left") {
        plot <- plot + ggplot2::theme(legend.position = c(0, 
            0), legend.justification = c(0, 0))
    }
    else if (legend.pos == "top.right") {
        plot <- plot + ggplot2::theme(legend.position = c(1, 
            1), legend.justification = c(1, 1))
    }
    else if (legend.pos == "top.left") {
        plot <- plot + ggplot2::theme(legend.position = c(0, 
            1), legend.justification = c(0, 1))
    }
    else if (legend.pos == "top.out") {
        plot <- plot + ggplot2::theme(legend.position = "top")
    }
    else if (legend.pos == "bottom.out") {
        plot <- plot + ggplot2::theme(legend.position = "bottom")
    }
    else if (legend.pos == "none") {
        plot <- plot + ggplot2::theme(legend.position = "none")
    }
    if (cb == TRUE) {
        plot <- plot + ggplot2::scale_fill_manual(values = cbpl) + 
            ggplot2::scale_colour_manual(values = cbpl)
    }
    if (k == TRUE && g == FALSE && k.pos == "right") {
        plot <- plot + ggplot2::annotate("text", y = (max(data_trim$yi) + 
            (max(data_trim$yi) * 0.1)), x = (seq(1, group_no, 
            1) + 0.3), label = paste("italic(k)==", mod_table$K[1:group_no]), 
            parse = TRUE, hjust = "right", size = 2)
    }
    else if (k == TRUE && g == FALSE && k.pos == "left") {
        plot <- plot + ggplot2::annotate("text", y = (min(data_trim$yi) + 
            3), x = (seq(1, group_no, 
            1) + 0.3), label = paste("italic(k)==", mod_table$K[1:group_no]), 
            parse = TRUE, hjust = "left", size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "right") {
        plot <- plot + ggplot2::annotate("text", y = (max(data_trim$yi) + 
            (max(data_trim$yi) * 0.1)), x = (seq(1, group_no, 
            1) + 0.3), label = paste("italic(k)==", mod_table$K[1:group_no], 
            "~", "(", mod_table$g[1:group_no], ")"), parse = TRUE, 
            hjust = "right", size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "left") {
        plot <- plot + ggplot2::annotate("text", y = (min(data_trim$yi) + 
            3), x = (seq(1, group_no, 
            1) + 0.3), label = paste("italic(k)==", mod_table$K[1:group_no], 
            "~", "(", mod_table$g[1:group_no], ")"), parse = TRUE, 
            hjust = "left", size = 2)
    }
    else if (k == TRUE && g == FALSE && k.pos %in% c("right", 
        "left", "none") == FALSE) {
        plot <- plot + ggplot2::annotate("text", y = k.pos, x = (seq(1, 
            group_no, 1) + 0.3), label = paste("italic(k)==", 
            mod_table$K[1:group_no]), parse = TRUE, size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos %in% c("right", 
        "left", "none") == FALSE) {
        plot <- plot + ggplot2::annotate("text", y = k.pos, x = (seq(1, 
            group_no, 1) + 0.3), label = paste("italic(k)==", 
            mod_table$K[1:group_no], "~", "(", mod_table$g[1:group_no], 
            ")"), parse = TRUE, size = 2)
    }
    return(plot)
}
```

```{r, warning=FALSE}
orchard_plot_new2 <- function (object, mod = "1", group, xlab, N = NULL, alpha = 0.5, 
    angle = 90, cb = TRUE, k = TRUE, g = TRUE, tree.order = NULL, 
    trunk.size = 1, branch.size = 1.2, twig.size = 0.5, transfm = c("none", 
        "tanh", "invlogit", "percent", "percentr"), condition.lab = "Condition", 
    legend.pos = c("bottom.right", "bottom.left", "top.right", 
        "top.left", "top.out", "bottom.out", "none"), k.pos = c("right", 
        "left", "none"), colour = FALSE, fill = TRUE, weights = "prop", 
    by = NULL, at = NULL, upper = TRUE, flip = TRUE) 
{
    transfm <- match.arg(NULL, choices = transfm)
    legend.pos <- match.arg(NULL, choices = legend.pos)
    k.pos <- match.arg(NULL, choices = k.pos)
    if (any(class(object) %in% c("robust.rma", "rma.mv", "rma", 
        "rma.uni"))) {
        if (mod != "1") {
            results <- orchaRd::mod_results(object, mod, group, 
                N, by = by, at = at, weights = weights, upper = upper)
        }
        else {
            results <- orchaRd::mod_results(object, mod = "1", 
                group, N, by = by, at = at, weights = weights, 
                upper = upper)
        }
    }
    if (any(class(object) %in% c("orchard"))) {
        results <- object
    }
    mod_table <- results$mod_table
    data_trim <- results$data
    data_trim$moderator <- factor(data_trim$moderator, levels = mod_table$name, 
        labels = mod_table$name)
    data_trim$scale <- (1/sqrt(data_trim[, "vi"]))
    legend <- "Precision (1/SE)"
    if (!is.null(tree.order) & length(tree.order) != nlevels(data_trim[, 
        "moderator"])) {
        stop("Length of 'tree.order' does not equal number of categories in moderator")
    }
    if (!is.null(tree.order)) {
        data_trim$moderator <- factor(data_trim$moderator, levels = tree.order, 
            labels = tree.order)
        mod_table <- mod_table %>% dplyr::arrange(factor(name, 
            levels = tree.order))
    }
    if (is.null(N) == FALSE) {
        data_trim$scale <- data_trim$N
        legend <- paste0("Sample Size ($\\textit{N}$)")
    }
    if (transfm == "tanh") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- Zr_to_r(mod_table[, cols])
        data_trim$yi <- Zr_to_r(data_trim$yi)
        label <- xlab
    }
    if (transfm == "invlogit") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- lapply(mod_table[, cols], function(x) metafor::transf.ilogit(x))
        data_trim$yi <- metafor::transf.ilogit(data_trim$yi)
        label <- xlab
    }
    if (transfm == "percentr") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- lapply(mod_table[, cols], function(x) (exp(x) - 
            1) * 100)
        data_trim$yi <- (exp(data_trim$yi) - 1) * 100
        label <- xlab
    }
    if (transfm == "percent") {
        cols <- sapply(mod_table, is.numeric)
        mod_table[, cols] <- lapply(mod_table[, cols], function(x) exp(x))
        data_trim$yi <- (exp(data_trim$yi))
        label <- xlab
    }
    else {
        label <- xlab
    }
    mod_table$K <- as.vector(by(data_trim, data_trim[, "moderator"], 
        function(x) length(x[, "yi"])))
    mod_table$g <- as.vector(num_studies(data_trim, moderator, 
        stdy)[, 2])
    group_no <- length(unique(mod_table[, "name"]))
    cbpl <- c("grey69", 
                 "grey69", 
                 "grey69",
                 "grey69", 
                 "grey69", 
                 "grey69", 
                 "grey69", 
                 "grey69"
)
    if (colour == TRUE) {
        color <- as.factor(data_trim$stdy)
        color2 <- NULL
    }
    else {
        color <- data_trim$mod
        color2 <- mod_table$name
    }
    if (fill == TRUE) {
        fill <- color
    }
    else {
        fill <- NULL
    }
    if (names(mod_table)[2] == "condition") {
        condition_no <- length(unique(mod_table[, "condition"]))
        plot <- ggplot2::ggplot() + ggbeeswarm::geom_quasirandom(data = data_trim, 
            ggplot2::aes(y = yi, x = moderator, size = scale, 
                colour = color, fill = fill), alpha = alpha, 
            shape = 21) + ggplot2::geom_hline(yintercept = 1, 
            linetype = 2, colour = "red", alpha = 1) + 
            ggplot2::geom_linerange(data = mod_table, ggplot2::aes(x = name, 
                ymin = lowerCL, ymax = upperCL), size = branch.size, 
                position = ggplot2::position_dodge2(width = 0.3)) + 
            ggplot2::geom_pointrange(data = mod_table, ggplot2::aes(y = estimate, 
                x = name, ymin = lowerPR, ymax = upperPR, shape = as.factor(condition), 
                fill = color2), fill = "red", size = trunk.size, position = ggplot2::position_dodge2(width = 0.3), 
                linewidth = twig.size) + ggplot2::scale_shape_manual(values = 20 + 
            (1:condition_no)) + ggplot2::theme_bw() + ggplot2::guides(fill = "none", 
            colour = "none") + ggplot2::theme(legend.position = c(0, 
            1), legend.justification = c(0, 1)) + ggplot2::theme(legend.title = ggplot2::element_text(size = 9)) + 
            ggplot2::theme(legend.direction = "horizontal") + 
            ggplot2::theme(legend.background = ggplot2::element_blank()) + 
            ggplot2::labs(y = label, x = "", size = latex2exp::TeX(legend)) + 
            ggplot2::labs(shape = condition.lab) + ggplot2::theme(axis.text.y = ggplot2::element_text(size = 10, 
            colour = "black", hjust = 0.5, angle = angle))
        if (flip) {
            plot <- plot + ggplot2::coord_flip()
        }
    }
    else {
        plot <- ggplot2::ggplot() + ggbeeswarm::geom_quasirandom(data = data_trim, 
            ggplot2::aes(y = yi, x = moderator, size = scale, 
                colour = color, fill = fill), alpha = alpha, 
            shape = 21) + ggplot2::geom_hline(yintercept = 1, 
            linetype = 2, colour = "red", alpha = 1) + 
            ggplot2::geom_linerange(data = mod_table, ggplot2::aes(x = name, 
                ymin = lowerCL, ymax = upperCL), size = branch.size) + 
            ggplot2::geom_pointrange(data = mod_table, ggplot2::aes(y = estimate, 
                x = name, ymin = lowerPR, ymax = upperPR, fill = color2), fill = "red",
                size = trunk.size, linewidth = twig.size, shape = 21) + 
            ggplot2::theme_bw() + ggplot2::guides(fill = "none", 
            colour = "none") + ggplot2::theme(legend.title = ggplot2::element_text(size = 9)) + 
            ggplot2::theme(legend.direction = "horizontal") + 
            ggplot2::theme(legend.background = ggplot2::element_blank()) + 
            ggplot2::labs(y = label, x = "", size = latex2exp::TeX(legend)) + 
            ggplot2::theme(axis.text.y = ggplot2::element_text(size = 10, 
                colour = "black", hjust = 0.5, angle = angle))
        if (flip) {
            plot <- plot + ggplot2::coord_flip()
        }
    }
    if (legend.pos == "bottom.right") {
        plot <- plot + ggplot2::theme(legend.position = c(1, 
            0), legend.justification = c(1, 0))
    }
    else if (legend.pos == "bottom.left") {
        plot <- plot + ggplot2::theme(legend.position = c(0, 
            0), legend.justification = c(0, 0))
    }
    else if (legend.pos == "top.right") {
        plot <- plot + ggplot2::theme(legend.position = c(1, 
            1), legend.justification = c(1, 1))
    }
    else if (legend.pos == "top.left") {
        plot <- plot + ggplot2::theme(legend.position = c(0, 
            1), legend.justification = c(0, 1))
    }
    else if (legend.pos == "top.out") {
        plot <- plot + ggplot2::theme(legend.position = "top")
    }
    else if (legend.pos == "bottom.out") {
        plot <- plot + ggplot2::theme(legend.position = "bottom")
    }
    else if (legend.pos == "none") {
        plot <- plot + ggplot2::theme(legend.position = "none")
    }
    if (cb == TRUE) {
        plot <- plot + ggplot2::scale_fill_manual(values = cbpl) + 
            ggplot2::scale_colour_manual(values = cbpl)
    }
    if (k == TRUE && g == FALSE && k.pos == "right") {
        plot <- plot + ggplot2::annotate("text", y = (max(data_trim$yi) + 
            (max(data_trim$yi) * 0.1)), x = (seq(1, group_no, 
            1) + 0.4), label = paste("italic(k)==", mod_table$K[1:group_no]), 
            parse = TRUE, hjust = "right", size = 2)
    }
    else if (k == TRUE && g == FALSE && k.pos == "left") {
        plot <- plot + ggplot2::annotate("text", y = (min(data_trim$yi) + 
            3), x = (seq(1, group_no, 
            1) + 0.4), label = paste("italic(k)==", mod_table$K[1:group_no]), 
            parse = TRUE, hjust = "left", size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "right") {
        plot <- plot + ggplot2::annotate("text", y = (max(data_trim$yi) + 
            (max(data_trim$yi) * 0.1)), x = (seq(1, group_no, 
            1) + 0.4), label = paste("italic(k)==", mod_table$K[1:group_no], 
            "~", "(", mod_table$g[1:group_no], ")"), parse = TRUE, 
            hjust = "right", size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "left") {
        plot <- plot + ggplot2::annotate("text", y = (min(data_trim$yi) + 
            3), x = (seq(1, group_no, 
            1) + 0.4), label = paste("italic(k)==", mod_table$K[1:group_no], 
            "~", "(", mod_table$g[1:group_no], ")"), parse = TRUE, 
            hjust = "left", size = 2)
    }
    else if (k == TRUE && g == FALSE && k.pos %in% c("right", 
        "left", "none") == FALSE) {
        plot <- plot + ggplot2::annotate("text", y = k.pos, x = (seq(1, 
            group_no, 1) + 0.4), label = paste("italic(k)==", 
            mod_table$K[1:group_no]), parse = TRUE, size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos %in% c("right", 
        "left", "none") == FALSE) {
        plot <- plot + ggplot2::annotate("text", y = k.pos, x = (seq(1, 
            group_no, 1) + 0.4), label = paste("italic(k)==", 
            mod_table$K[1:group_no], "~", "(", mod_table$g[1:group_no], 
            ")"), parse = TRUE, size = 2)
    }
    return(plot)
}
```

```{r, warning=FALSE}
bubble_plot_new <- function (object, mod, group = NULL, xlab = "Moderator", ylab = "Effect size", 
    N = "none", alpha = 0.5, cb = TRUE, k = TRUE, g = FALSE, 
    transfm = c("none", "tanh", "invlogit", "percent", "percentr"), 
    est.lwd = 1, ci.lwd = 0.5, pi.lwd = 0.5, est.col = "black", 
    ci.col = "black", pi.col = "black", legend.pos = c("top.left", 
        "top.right", "bottom.right", "bottom.left", "top.out", 
        "bottom.out", "none"), k.pos = c("top.right", "top.left", 
        "bottom.right", "bottom.left", "none"), condition.nrow = 2, 
    weights = "prop", by = NULL, at = NULL, cond_levels = NULL) 
{
    transfm <- match.arg(NULL, choices = transfm)
    legend.pos <- match.arg(NULL, choices = legend.pos)
    k.pos <- match.arg(NULL, choices = k.pos)
    label <- xlab
    if (missing(group)) {
        stop("Please specify the 'group' argument by providing the name of the grouping variable. See ?bubble_plot")
    }
    if (is.numeric(by)) {
        k = FALSE
        g = FALSE
    }
    if (any(class(object) %in% c("robust.rma", "rma.mv", "rma", 
        "rma.uni"))) {
        if (mod != "1") {
            results <- orchaRd::mod_results(object, mod, group, 
                by = by, at = at, weights = weights)
        }
        else {
            results <- orchaRd::mod_results(object, mod = "1", 
                group, by = by, at = at, weights = weights)
        }
    }
    if (any(class(object) %in% c("orchard"))) {
        results <- object
    }
    mod_table <- results$mod_table
    data_trim <- results$data
    data_trim$scale <- (1/sqrt(data_trim[, "vi"]))
    legend <- "Precision (1/SE)"
    if (any(N != "none")) {
        data_trim$scale <- data_trim$N
        legend <- paste0("Sample Size ($\\textit{N}$)")
    }
    if (transfm != "none") {
        excluded_cols <- which(colnames(mod_table) %in% c("condition", 
            "moderator"))
        mod_table[, -excluded_cols] <- transform_data(mod_table[, 
            -excluded_cols], transfm)
        data_trim$yi <- transform_data(data_trim$yi, transfm)
    }
    if (is.null(data_trim$condition) == TRUE) {
        effect_num <- nrow(data_trim)
        group_num <- length(unique(data_trim$stdy))
        dat_text <- data.frame(K = effect_num, G = group_num)
    }
    else {
        if (!is.null(cond_levels)) {
            data_trim$condition <- factor(data_trim$condition, 
                levels = cond_levels, labels = cond_levels, ordered = TRUE)
        }
        else {
            data_trim$condition <- factor(data_trim$condition, 
                levels = mod_table$condition, labels = mod_table$condition)
        }
        effect_num <- as.vector(by(data_trim, data_trim[, "condition"], 
            function(x) base::length(x[, "yi"])))
        group_num <- as.vector(by(data_trim, data_trim[, "condition"], 
            function(x) base::length(base::unique(x[, "stdy"]))))
        dat_text <- data.frame(K = effect_num, G = group_num, 
            condition = as.vector(base::levels(data_trim$condition)))
    }
    if (is.null(data_trim$condition) == TRUE) {
        plot <- ggplot2::ggplot() + ggplot2::geom_point(data = data_trim, 
            ggplot2::aes(x = moderator, y = yi, size = scale), 
            shape = 21, alpha = alpha, fill = "grey90") + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = lowerPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", lwd = pi.lwd, 
            colour = pi.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = upperPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", lwd = pi.lwd, 
            colour = pi.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = lowerCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", lwd = ci.lwd, 
            colour = ci.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = upperCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", lwd = ci.lwd, 
            colour = ci.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = estimate), method = "loess", 
            formula = y ~ x, se = FALSE, lwd = est.lwd, colour = est.col) + 
            ggplot2::labs(x = xlab, y = ylab, size = legend, 
                parse = TRUE) + ggplot2::guides(fill = "none", 
            colour = "none") + ggplot2::theme_bw() + ggplot2::theme(legend.direction = "horizontal") + 
            ggplot2::theme(legend.background = ggplot2::element_blank()) + 
            ggplot2::theme(axis.text.y = ggplot2::element_text(size = 10, 
                colour = "black", hjust = 0.5, angle = 90))
    }
    else if (is.character(data_trim$condition) == TRUE || is.factor(data_trim$condition) == 
        TRUE) {
        plot <- ggplot2::ggplot() + ggplot2::geom_point(data = data_trim, 
            ggplot2::aes(x = moderator, y = yi, size = scale, 
                fill = condition), shape = 21, alpha = alpha) + 
            ggplot2::geom_smooth(data = mod_table, ggplot2::aes(x = moderator, 
                y = lowerPR), method = "loess", formula = y ~ 
                x, se = FALSE, lty = "dotted", lwd = pi.lwd, 
                colour = pi.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = upperPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", lwd = pi.lwd, 
            colour = pi.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = lowerCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", lwd = ci.lwd, 
            colour = ci.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = upperCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", lwd = ci.lwd, 
            colour = ci.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = estimate), method = "loess", 
            formula = y ~ x, se = FALSE, lwd = est.lwd, colour = est.col) + 
            ggplot2::facet_wrap(ggplot2::vars(condition), nrow = condition.nrow) + 
            ggplot2::labs(x = xlab, y = ylab, size = legend, 
                parse = TRUE) + ggplot2::guides(fill = "none", 
            colour = "none") + ggplot2::theme_bw() + ggplot2::theme(legend.direction = "horizontal") + 
            ggplot2::theme(legend.background = ggplot2::element_blank()) + 
            ggplot2::theme(axis.text.y = ggplot2::element_text(size = 10, 
                colour = "black", hjust = 0.5, angle = 90))
    }
    else {
        plot <- ggplot2::ggplot() + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = lowerPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", lwd = pi.lwd, 
            colour = pi.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = upperPR), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dotted", lwd = pi.lwd, 
            colour = pi.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = lowerCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", lwd = ci.lwd, 
            colour = ci.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = upperCL), method = "loess", 
            formula = y ~ x, se = FALSE, lty = "dashed", lwd = ci.lwd, 
            colour = ci.col) + ggplot2::geom_smooth(data = mod_table, 
            ggplot2::aes(x = moderator, y = estimate), method = "loess", 
            formula = y ~ x, se = FALSE, lwd = est.lwd, colour = est.col) + 
            ggplot2::facet_wrap(ggplot2::vars(condition), nrow = condition.nrow) + 
            ggplot2::labs(x = xlab, y = ylab, size = legend, 
                parse = TRUE) + ggplot2::guides(fill = "none", 
            colour = "none") + ggplot2::theme_bw()
    }
    plot <- switch(legend.pos, bottom.right = plot + ggplot2::theme(legend.position = "inside", 
        legend.justification = c(1, 0)), bottom.left = plot + 
        ggplot2::theme(legend.position = "inside", legend.justification = c(0, 
            0)), top.right = plot + ggplot2::theme(legend.position = "inside", 
        legend.justification = c(1, 1)), top.left = plot + ggplot2::theme(legend.position = "inside", 
        legend.justification = c(0, 1)), top.out = plot + ggplot2::theme(legend.position = "top"), 
        bottom.out = plot + ggplot2::theme(legend.position = "bottom"), 
        none = plot + ggplot2::theme(legend.position = "none"), 
        plot)
    if (k == TRUE && g == FALSE && k.pos == "top.right") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = Inf, 
            y = Inf), label = paste("italic(k)==", dat_text$K), 
            parse = TRUE, hjust = 2, vjust = 2.2,size = 2)
    }
    else if (k == TRUE && g == FALSE && k.pos == "top.left") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = -Inf, 
            y = Inf), label = paste("italic(k)==", dat_text$K), 
            parse = TRUE, hjust = -0.5, vjust = 2.2, size = 2)
    }
    else if (k == TRUE && g == FALSE && k.pos == "bottom.right") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = Inf, 
            y = -Inf), label = paste("italic(k)==", rev(dat_text$K)), 
            parse = TRUE, hjust = 2, vjust = -1.8, size = 2)
    }
    else if (k == TRUE && g == FALSE && k.pos == "bottom.left") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = -Inf, 
            y = -Inf), label = paste("italic(k)==", dat_text$K), 
            parse = TRUE, hjust = -0.5, vjust = -1.8, size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "top.right") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = Inf, 
            y = Inf), label = paste("italic(k)==", dat_text$K, 
            "~", "(", dat_text$G, ")"), parse = TRUE, hjust = 1.5, 
            vjust = 2.2, size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "top.left") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = -Inf, 
            y = Inf), label = paste("italic(k)==", dat_text$K, 
            "~", "(", dat_text$G, ")"), parse = TRUE, hjust = -0.5, 
            vjust = 2.2, size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "bottom.right") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = Inf, 
            y = -Inf), label = paste("italic(k)==", dat_text$K, 
            "~", "(", dat_text$G, ")"), parse = TRUE, hjust = 1.5, 
            vjust = -0.8, size = 2)
    }
    else if (k == TRUE && g == TRUE && k.pos == "bottom.left") {
        plot <- plot + ggplot2::geom_text(data = dat_text, mapping = ggplot2::aes(x = -Inf, 
            y = -Inf), label = paste("italic(k)==", dat_text$K, 
            "~", "(", dat_text$G, ")"), parse = TRUE, hjust = -0.5, 
            vjust = -0.8, size = 2)
    }
    return(plot)
}
```

The following code defines a standardized function to fit multivariate meta-analytic models. We are going to use this function to run all single-moderator models below.

```{r, results='hide'}
run_model <- function(data, formula){
  data <- as.data.frame(data) # convert data set into a data frame to calculate VCV matrix 
  VCV <- impute_covariance_matrix(data$ln_TMF_se^2,
                                  cluster = data$FW_ID, 
                                  r = 0.5) # create VCV matrix for the specified data
  rma.mv(ln_TMF,
         VCV,
         mods = formula,
         random = list(~1|Study_ID, 
                       ~1|FW_ID, 
                       ~1|PFAS_ID, 
                       ~1|TMF_ID
                       ),
         test = "t",
         data = data,
         sparse = TRUE)
}
```

# Intercept meta-analytic model

Determine the random effect structure:
The random effects model accounts for between-study heterogeneity, which reflects the variability in effect sizes across the studies being analyzed. In determining the random effect structure, we aim to identify the sources of this heterogeneity and quantify its extent within the data. This step is crucial for accurately modeling the variation and ensuring that the results are generalizable beyond the specific studies included in the analysis.

--> **NOTE!** Model outputs are on the natural log scale (ln TMF), whereas the plots on the original scale (TMF).
```{r, eval=FALSE, include=TRUE}
mod <- rma.mv(yi = ln_TMF, # Natural logarithm of the Trophic Magnification Factor
              V = VCV, # Variance co-variance matrix
              random = list(~1|Study_ID, # Between-study effect
                            ~1|FW_ID, # Between food webs effect
                            ~1|PFAS_ID, # Between type of PFAS effect
                            ~1|TMF_ID # Within-study effect
                            ),
              test = "t", 
              sparse = T,
              data = TMF_data2)

save(mod, file = here("Rmodels", "mod.RData"))

fig2A_data <- TMF_data2 %>% 
  select(TMF_ID, FW_ID, PFAS_ID, Study_ID, ln_TMF, ln_TMF_se)

write_csv(fig2A_data, here("Rdata", "fig2A_data.csv"))
```

```{r, warning=FALSE}
load(here("Rmodels", "mod.RData"))
tab_mod <-readRDS(here("Rdata", "tab_mod.RDS"))
summary(mod)
i2_ml(mod)

I2 <- orchaRd::i2_ml(mod)
fig2A <- orchard_plot_new(mod,
                        transfm = "percent",
                        mod = "1",
                        group = "Study_ID", 
                        xlab = "ln_TMF",
                        k.pos = "left",
                        alpha = 0.5,
                        trunk.size = 0.5,
                        branch.size = 0.8,
                        twig.size = 0.2,
                        colour = FALSE,
                        fill = FALSE) +  
  annotate(geom = "text",
           x = 1.3,
           y = 7.5, 
           label = paste0("italic(I)^{2} == ", round(I2[1],4)),
           size = 2,
           color ="black",
           parse = TRUE) +
  scale_size_continuous(range = c(1, 3)) + # change point scaling
  theme(panel.border = element_rect(colour = "black", 
                                    fill = NA,
                                    size = 0.5), # border around the plot
        plot.title = element_text(face = "bold", size = 8),
       legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
       legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_blank(),
       axis.text.x = element_text(size = 7)) +
  #ylim(NA, 10) +
  xlab("Intercept") +
  ylab("TMF") +
  ggtitle("A") +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, by = 1))

fig2A
```

```{r, eval=FALSE}
ggsave(here("figs","fig2A.png"),
       width = 8,
       height = 4)
```

The red dotted line represents TMF = 1, the threshold indicating trophic magnification when exceeded, and biodilution when below.
Next, we'll plot the same graph with a zoomed-out view (no scale_y_continuous restrictions).

```{r, warning=FALSE}
figS6 <- orchard_plot_new(mod,
                        transfm = "percent",
                        mod = "1",
                        group = "Study_ID", 
                        xlab = "ln_TMF",
                        k.pos = "left",
                        alpha = 0.6,
                        trunk.size = 1.5,
                        branch.size = 2.7,
                        twig.size = 0.4,
                        colour = FALSE,
                        fill = FALSE) +  
  annotate(geom = "text",
           x = 1.3,
           y = 13.5, 
           label = paste0("italic(I)^{2} == ", round(I2[1],4)),
           size = 4,
           color ="black",
           parse = TRUE) +
  scale_size_continuous(range = c(1, 10)) + # change point scaling
  theme(panel.border = element_rect(colour = "black", 
                                    fill = NA,
                                    size = 1.3), # border around the plot
       legend.title = element_text(size = 13),
        legend.text = element_text(size = 11),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_blank(),
       axis.text.x = element_text(size = 13)) +
  #ylim(NA, 10) +
  xlab("Intercept") +
  ylab("TMF")

figS6
```

```{r, eval=FALSE}
ggsave(here("figs/supplements","figS6.png"),
       width = 8,
       height = 4)
```

# Terrestrial vs Aquatic
```{r}
TMF_data2_ecogroups <- TMF_data2 %>%
  mutate(Ecosystem_group = ifelse(Ecosystem == "terrestrial", 
                                  "Terrestrial", 
                                  "Aquatic"))
```

```{r, eval=FALSE, include=TRUE}
mod_ecogroup <- rma.mv(
  yi = ln_TMF, 
  V = VCV, 
  mods = ~ Ecosystem_group, # Add Ecosystem_group as a moderator
  random = list(
    ~1 | Study_ID,
    ~1 | FW_ID,
    ~1 | PFAS_ID,
    ~1 | TMF_ID
  ),
  test = "t",
  sparse = TRUE,
  data = TMF_data2_ecogroups # Use the updated dataset
)

save(mod_ecogroup, file = here("Rmodels", "mod_ecogroup.RData"))
```

```{r, warning=FALSE}
load(here("Rmodels", "mod_ecogroup.RData"))
summary(mod_ecogroup)
r2_ecogroup <- r2_ml(mod_ecogroup, TMF_data2_ecogroups)

figS4 <- orchard_plot_new(
  mod_ecogroup,
  transfm = "percent",
  mod = "Ecosystem_group", # Specify the moderator
  group = "Study_ID",
  xlab = "ln_TMF",
  k.pos = "left",
  alpha = 0.6,
  trunk.size = 1.5,
  branch.size = 2.7,
  twig.size = 0.4,
  colour = FALSE,
  fill = FALSE
) + 
  scale_size_continuous(range = c(1, 10)) +
  annotate(geom = "text",
           x = 2.4,
           y = 8, 
           label = paste0("italic(R)^{2} == ", round(r2_ecogroup[1],4)),
           color ="black",
           parse = TRUE, 
           size = 5) +
  theme(
    panel.border = element_rect(colour = "black", fill = NA, size = 1.3),
    #plot.title = element_text(face = "bold", size = 15),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 11),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_blank(),
    axis.text.y = element_text(size = 13),
    axis.text.x = element_text(size = 13)
  ) +
  scale_y_continuous(limits = c(0, 11), breaks = seq(0, 11, by = 1)) +
  xlab("Intercept") +
  ylab("TMF") 

figS4
```

```{r, eval=FALSE}
ggsave(here("figs/supplements","figS4.png"),
       width = 10,
       height = 6)
```

# Subcategory meta-regression analysis

```{r}
TMF_data3 <- TMF_data2 %>% 
  filter(!PFAS_ID %in% c("ΣPFAS", "ΣPFCA", "ΣPFSA", "ΣPFCs", "PFODA")) %>%  # PFODA removed because NA
  #filter(n_distinct(Study_ID) > 1) %>%
  ungroup() %>%
  mutate(PFAS_ID = case_when(
    PFAS_ID == "6:2 Cl-PFESA" ~ "F-53B",
    PFAS_ID == "8:2 Cl-PFESA" ~ "F-53B",
    PFAS_ID == "F53B" ~ "F-53B",
    PFAS_ID == "3m-PFOS" ~ "PFOS",
    PFAS_ID == "4m-PFOS" ~ "PFOS",
    PFAS_ID == "5m-PFOS" ~ "PFOS",
    PFAS_ID == "br-EtFOSA" ~ "EtFOSA",
    PFAS_ID == "br-FOSA" ~ "FOSA",
    PFAS_ID == "br-PFDA" ~ "PFDA",
    PFAS_ID == "br-PFDoDA" ~ "PFDoDA",
    PFAS_ID == "br-PFOA" ~ "PFOA",
    PFAS_ID == "br-PFOS" ~ "PFOS",
    PFAS_ID == "br-PFTeDA" ~ "PFTeDA",
    PFAS_ID == "dm-PFOS" ~ "PFOS",
    PFAS_ID == "iso-PFOS" ~ "PFOS",
    PFAS_ID == "l-EtFOSA" ~ "EtFOSA",
    PFAS_ID == "l-FOSA" ~ "FOSA",
    PFAS_ID == "l-PFDA" ~ "PFDA",
    PFAS_ID == "l-PFDoDA" ~ "PFDoDA",
    PFAS_ID == "l-PFOA" ~ "PFOA",
    PFAS_ID == "l-PFOS" ~ "PFOS",
    PFAS_ID == "l-PFTeDA" ~ "PFTeDA",
    PFAS_ID == "mm-PFOS" ~ "PFOS",
    TRUE ~ PFAS_ID
  ))

k_n_data <- TMF_data3 %>% 
  group_by(PFAS_ID) %>%
  arrange(PFAS_ID) %>% 
  summarise(k = n(), n = length(unique(Study_ID)))

VCV_chem <- vcalc(vi = ln_TMF_se^2,
                  cluster = FW_ID, 
                  obs = TMF_ID,
                  subgroup = PFAS_ID, 
                  rho = 0.5,
                  data = TMF_data3)
```

## mod_chem
```{r, eval=FALSE, include=TRUE}
mod_chem <- rma.mv(ln_TMF ~ PFAS_ID - 1,
                   V = VCV_chem,
                   random = list(~ PFAS_ID | FW_ID),
                   struct = "DIAG",
                   test = "t", #to conunteract potential small sample size 
                   sparse = T,
                   data = TMF_data3,
                   #verbose = TRUE, 
                   control = list(iter.max = 1000, 
                                  rel.tol = 1e-8))
# Save the model
save(mod_chem, file = here("Rmodels", "mod_chem.RData"))
# Save the table
write.csv(TMF_data3, here("Rdata/TMF_data3.csv"), row.names = FALSE)
```

```{r, warning=FALSE}
load(here("Rmodels", "mod_chem.RData"))
summary(mod_chem)

res_tab1 <- broom::tidy(mod_chem)
res_tab1$ci.lb <- mod_chem$ci.lb
res_tab1$ci.ub <- mod_chem$ci.ub
res_tab1$pval <-mod_chem$pval
res_tab1 <- res_tab1 %>% 
  mutate(
    PFAS_ID = str_remove(term, "^PFAS_ID"),  # Remove 'PFAS_ID1: ' prefix
    estimate = exp(estimate),  # Convert estimates back to original scale
    ci.lb = exp(ci.lb),  # Convert lower CI back to original scale
    ci.ub = exp(ci.ub)   # Convert upper CI back to original scale
  ) %>% 
  arrange(PFAS_ID)

res_tab1 <- res_tab1 %>% 
  mutate(k = k_n_data$k) %>% 
  mutate(n = k_n_data$n)

# Prepare the data for plotting and order PFAS_ID by estimate value
plot_data1 <- res_tab1 %>%
  as.data.frame() %>% 
  filter(k > 10) %>% 
  arrange(estimate)

# Create the flipped forest plot
fig2B <- ggplot(plot_data1, aes(y = reorder(PFAS_ID, estimate), x = estimate)) +
  geom_point(aes(size = k),  # Make point size proportional to k
             color = ifelse(plot_data1$pval > 0.05, "grey", "black"),  # You can change the color if desired
             alpha = 1) +  # Add transparency for better visibility 
  scale_size(range = c(1.5, 4)) + # Set minimum size to 3 and maximum to 6
  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), 
                 height = 0.2,
                 size = 0.1,
                 alpha = ifelse(plot_data1$pval > 0.05, 0.6, 1)) +  # Horizontal error bars
  geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.4) +  # Reference line at 1
  geom_text(aes(label = paste0("k = ", k, " (", n, ")"), x = -0.18),
            hjust = 0, size = 2, # Add k values as text next to the points
            fontface = ifelse(plot_data1$pval < 0.05, "bold", "plain")) +  # Access pval outside aes()
  # Add "*" next to PFUnDA and PFNA
  # geom_text(data = subset(plot_data1, PFAS_ID %in% c("PFUnDA", "PFNA", "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA")),
  #           aes(x = -0.21, label = "*"), size = 9, color = "black") +
  # geom_text(data = subset(plot_data1, PFAS_ID %in% c("PFUnDA", "PFNA", "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA")),
  #           aes(x = ci.lb, label = "*"),
  #           hjust = 1.2, vjust = 0.7, size = 6, color = "black") +
  xlab("TMF") +
  ylab("PFAS") +
  ggtitle("B") +
  theme_minimal() +  # Use a minimal theme
  theme(legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 0.5),
         plot.title = element_text(face = "bold", size = 8),
       legend.title = element_text(size = 7),
        legend.text = element_text(size = 7),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 6),
       axis.text.x = element_text(size = 8)) +  
   #scale_x_break(c(4, 6)) +
   scale_x_continuous(breaks = seq(0, 4, by = 1), limits = c(-0.21, 4))
  
fig2B
```

```{r, eval=FALSE}
# Combine plots with specified heights
fig2 <- fig2A / fig2B + 
  plot_layout(heights = c(1, 2))

# Save the combined plot
ggsave(here("figs", "fig2.pdf"), plot = fig2, width = 160, height = 120, units = "mm", dpi = 600)

fig2B_data <- plot_data1 %>% 
  select(PFAS_ID, k, n, estimate, std.error, statistic, p.value, ci.lb, ci.ub, pval)

write_csv(fig2B_data, here("Rdata", "fig2B_data.csv"))
```

Now, we have a look to all chemicals regardless of the number of effect sizes.

```{r}
plot_data1_full <- res_tab1 %>%
  as.data.frame() %>% 
  arrange(estimate)

# Create the flipped forest plot
figS1 <- ggplot(plot_data1_full, aes(y = reorder(PFAS_ID, estimate), x = estimate)) +
  geom_point(aes(size = k),  # Make point size proportional to k
             color = ifelse(plot_data1_full$pval > 0.05, "grey", "black"),  # You can change the color if desired
             alpha = 1) +  # Add transparency for better visibility 
  scale_size(range = c(3, 7)) + # Set minimum size to 3 and maximum to 6
  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), 
                 height = 0.2,
                 alpha = ifelse(plot_data1_full$pval > 0.05, 0.6, 1)) +  # Horizontal error bars
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +  # Reference line at 1
  geom_text(aes(label = paste0("k = ", k, " (", n, ")"), x = -1.7),
            hjust = 0, size = 3.5, # Add k values as text next to the points
            fontface = ifelse(plot_data1_full$pval < 0.05, "bold", "plain")) +  # Access pval outside aes()
  xlab("TMF") +
  ylab("PFAS") +
  theme_minimal() +  # Use a minimal theme
  theme(axis.text.y = element_text(size = 10),  # Adjust y-axis text size
        axis.text.x = element_text(size = 10),  # Adjust x-axis text size
        #axis.text.x.top = element_blank(),  # Remove x-axis labels from the top
        axis.title = element_text(size = 11),
        legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 1)) +
  scale_x_continuous(breaks = c(seq(0, 13, by = 1), seq(18, 19, by = 1), seq(23, 25, by = 1)),
                     limits = c(-1.7, 25)) +  # Combine breaks
  scale_x_break(c(13, 18)) +
  scale_x_break(c(19.4, 23))
```

```{r, eval=FALSE}
# Save the  plot
ggsave(here("figs/supplements", "figS1.png"), plot = figS1, width = 9, height = 14, dpi = 300)
```

Let's run a few similar models to see what one has the lowest AICc value (better fit).

## mod_chem2

mod_chem2 is identical to mod_chem but with the addition of an independent random factor (i.e., ~ 1 | TMF_ID). 

```{r, eval=FALSE}
mod_chem2 <- rma.mv(ln_TMF ~ PFAS_ID - 1,
                     V = VCV_chem,
                     random = list(~ PFAS_ID | FW_ID, 
                                   ~ 1 | TMF_ID), 
                     struct = "DIAG",
                     est = "t",
                     sparse = T,
                     data = TMF_data3,
                     #verbose = TRUE, 
                     control=list(iter.max=1000, 
                                  rel.tol=1e-8))

# Save the model
save(mod_chem2, file = here("Rdata", "mod_chem2.RData"))
```

```{r, warning=FALSE, echo=FALSE}
load(here("Rmodels", "mod_chem2.RData"))
summary(mod_chem2)

res_tab2 <- broom::tidy(mod_chem2)
res_tab2$ci.lb <- mod_chem2$ci.lb
res_tab2$ci.ub <- mod_chem2$ci.ub
res_tab2$pval <-mod_chem2$pval
res_tab2 <- res_tab2 %>% 
  mutate(
    PFAS_ID = str_remove(term, "^PFAS_ID"),  # Remove 'PFAS_ID1: ' prefix
    estimate = exp(estimate),  # Convert estimates back to original scale
    ci.lb = exp(ci.lb),  # Convert lower CI back to original scale
    ci.ub = exp(ci.ub)   # Convert upper CI back to original scale
  ) %>% 
  arrange(PFAS_ID)

res_tab2 <- res_tab2 %>% 
  mutate(k = k_n_data$k) %>% 
  mutate(n = k_n_data$n)

# Prepare the data for plotting and order PFAS_ID by estimate value
plot_data2 <- res_tab2 %>%
  as.data.frame() %>% 
  filter(k > 10) %>% 
  arrange(estimate)

# Create the flipped forest plot
forest_plot3 <- ggplot(plot_data2, aes(y = reorder(PFAS_ID, estimate), x = estimate)) +
  geom_point(aes(size = k),  # Make point size proportional to k
             color = ifelse(plot_data2$pval > 0.05, "grey", "black"),  # You can change the color if desired
             alpha = 1) +  # Add transparency for better visibility 
  scale_size(range = c(5, 13)) + # Set minimum size to 3 and maximum to 6
  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), 
                 height = 0.2,
                 alpha = ifelse(plot_data2$pval > 0.05, 0.6, 1)) +  # Horizontal error bars
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +  # Reference line at 1
  geom_text(aes(label = paste0("k = ", k, " (", n, ")"), x = -0.18),
            hjust = 0, size = 6, # Add k values as text next to the points
            fontface = ifelse(plot_data2$pval < 0.05, "bold", "plain")) +  # Access pval outside aes()
  # Add "*" next to PFUnDA and PFNA
  # geom_text(data = subset(plot_data2, PFAS_ID %in% c("PFUnDA", "PFNA", "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA")),
  #           aes(x = -0.21, label = "*"), size = 9, color = "black") +
  # geom_text(data = subset(plot_data2, PFAS_ID %in% c("PFUnDA", "PFNA", "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA")),
  #           aes(x = ci.lb, label = "*"),
  #           hjust = 1.2, vjust = 0.7, size = 6, color = "black") +
  xlab("TMF") +
  ylab("PFAS") +
  #ggtitle("B") +
  theme_minimal() +  # Use a minimal theme
  theme(legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 1),
         plot.title = element_text(face = "bold", size = 16),
       legend.title = element_text(size = 15),
        legend.text = element_text(size = 14),
        axis.title.x = element_text(size = 17),
        axis.title.y = element_text(size = 17),
        axis.text.y = element_text(size = 16),
       axis.text.x = element_text(size = 16)) +  
   #scale_x_break(c(4, 6)) +
   scale_x_continuous(breaks = seq(0, 4, by = 1), limits = c(-0.21, 4))
  
forest_plot3
```

Now, let's check the profile likelihood of model parameters for which we have at least 10 effect sizes.

```{r, eval=FALSE}
# Identify the indices of the variance components for the parameters
parameter_indices <- c(17, 47, 32, 51, 42, 33, 50, 20, 40, 34, 49, 46, 30, 36, 48, 31, 38)

# Initialize a list to store the results for each parameter
profile_results <- list()

# Loop through each index
for (i in parameter_indices) {
  # Get the profile data for the current variance component
  dat_ll <- profile(mod_chem2, tau2 = i)
  
  # Extract ll (log-likelihood) and sigma
  ll_values <- dat_ll$ll
  tau_values <- dat_ll$tau2
  
  # Store the results in the list
  profile_results[[i]] <- data.frame(
    parameter_index = i,
    tau2 = tau_values,
    log_likelihood = ll_values
  )
}

# Combine all results into a single data frame
mod_chem2_profile_results <- do.call(rbind, profile_results)
```
## mod_chem3

In mod-chem3, ~ 1 | TMF_ID and ~ 1 | FW_ID specifies independent random intercepts for TMF_ID and FW_ID. This structure does not allow for varying slopes but instead models each TMF_ID and each FW_ID with separate random intercepts, treating them independently.

```{r, eval=FALSE}
mod_chem3 <- rma.mv(ln_TMF ~ PFAS_ID - 1,
                     V = VCV_chem,
                     random = list(~ 1|FW_ID,
                                   ~ 1|Study_ID,
                                   ~ 1|TMF_ID), 
                     #struct = "DIAG",
                     est = "t",
                     sparse = T,
                     data = TMF_data3,
                     #verbose = TRUE, 
                     control=list(iter.max=1000, 
                                  rel.tol=1e-8))

# Save the model
save(mod_chem3, file = here("Rmodels", "mod_chem3.RData"))
```

```{r, warning=FALSE, echo=FALSE}
load(here("Rmodels", "mod_chem3.RData"))
summary(mod_chem3)

res_tab3 <- broom::tidy(mod_chem3)
res_tab3$ci.lb <- mod_chem3$ci.lb
res_tab3$ci.ub <- mod_chem3$ci.ub
res_tab3$pval <-mod_chem3$pval
res_tab3 <- res_tab3 %>% 
  mutate(
    PFAS_ID = str_remove(term, "^PFAS_ID"),  # Remove 'PFAS_ID1: ' prefix
    estimate = exp(estimate),  # Convert estimates back to original scale
    ci.lb = exp(ci.lb),  # Convert lower CI back to original scale
    ci.ub = exp(ci.ub)   # Convert upper CI back to original scale
  ) %>% 
  arrange(PFAS_ID)

res_tab3 <- res_tab3 %>% 
  mutate(k = k_n_data$k) %>% 
  mutate(n = k_n_data$n)

# Prepare the data for plotting and order PFAS_ID by estimate value
plot_data3 <- res_tab3 %>%
  as.data.frame() %>% 
  filter(k > 10) %>% 
  arrange(estimate)

# Create the flipped forest plot
forest_plot4 <- ggplot(plot_data3, aes(y = reorder(PFAS_ID, estimate), x = estimate)) +
  geom_point(aes(size = k),  # Make point size proportional to k
             color = ifelse(plot_data3$pval > 0.05, "grey", "black"),  # You can change the color if desired
             alpha = 1) +  # Add transparency for better visibility 
  scale_size(range = c(5, 13)) + # Set minimum size to 3 and maximum to 6
  geom_errorbarh(aes(xmin = ci.lb, xmax = ci.ub), 
                 height = 0.2,
                 alpha = ifelse(plot_data3$pval > 0.05, 0.6, 1)) +  # Horizontal error bars
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +  # Reference line at 1
  geom_text(aes(label = paste0("k = ", k, " (", n, ")"), x = -0.18),
            hjust = 0, size = 6, # Add k values as text next to the points
            fontface = ifelse(plot_data3$pval < 0.05, "bold", "plain")) +  # Access pval outside aes()
  # Add "*" next to PFUnDA and PFNA
  # geom_text(data = subset(plot_data3, PFAS_ID %in% c("PFUnDA", "PFNA", "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA")),
  #           aes(x = -0.21, label = "*"), size = 9, color = "black") +
  # geom_text(data = subset(plot_data3, PFAS_ID %in% c("PFUnDA", "PFNA", "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA")),
  #           aes(x = ci.lb, label = "*"),
  #           hjust = 1.2, vjust = 0.7, size = 6, color = "black") +
  xlab("TMF") +
  ylab("PFAS") +
  #ggtitle("B") +
  theme_minimal() +  # Use a minimal theme
  theme(legend.position = "none",
        panel.border = element_rect(colour = "black", fill = NA, size = 1),
         plot.title = element_text(face = "bold", size = 16),
       legend.title = element_text(size = 15),
        legend.text = element_text(size = 14),
        axis.title.x = element_text(size = 17),
        axis.title.y = element_text(size = 17),
        axis.text.y = element_text(size = 16),
       axis.text.x = element_text(size = 16)) +  
   #scale_x_break(c(4, 6)) +
   scale_x_continuous(breaks = seq(0, 4, by = 1), limits = c(-0.21, 4))
  
forest_plot4
```

While mod_chem has more variance components and hence a greater risk of overfitting, the lower AICc (mod_chem = 4122 and mod_chem2 = 6731) suggests that the additional complexity is justified by the improved fit to the data. This indicates that mod_chem is likely capturing meaningful interaction variability between PFAS_ID and FW_ID that mod_chem2 does not account for, making it a better model for these data despite having more parameters.


## PFOS reference - Comparison model
We are going to compare each compound against PFOS (the compound with the largest effect size and sample size). By doing so, we can assess what compounds have a mean estimate lower than PFOS.

```{r, eval=FALSE}
TMF_data3$PFAS_ID <- factor(TMF_data3$PFAS_ID)
# Relevel PFAS_ID so that PFOS is the reference level
TMF_data3$PFAS_ID <- relevel(TMF_data3$PFAS_ID, ref = "PFOS")
```

```{r, eval=FALSE}
# Fit the model
mod_chem_contr <- rma.mv(ln_TMF ~ PFAS_ID,
                   V = VCV_chem,
                   random = list(~ PFAS_ID | FW_ID), 
                   struct = "DIAG",
                   test = "t",
                   sparse = TRUE,
                   data = TMF_data3,
                   control = list(iter.max = 1000, 
                                  rel.tol = 1e-8))

# Save the model
save(mod_chem_contr, file = here("Rmodels", "mod_chem_contr.RData"))
```

```{r, eval=FALSE}
load(here("Rmodels", "mod_chem_contr.RData"))
summary(mod_chem_contr)
```

## Means for (un)regulated compounds

```{r}
# Regulation levels
lacking <- c("6:2ClPFESA", "PFDS", "PFBA", "PFPeA","PFHxA")
REACH <- c("PFDA", "PFUnDA", "PFTrDA", "PFDoDA", "PFTeDA", "PFHpA", "PFBS")
SCPoPs <- c("PFOS", "br-PFOS", "l-PFOS", "PFNA", "FOSA", "PFHxS", "PFOA")

plot_data4 <- TMF_data2

# Add the regulation column based on PFAS_ID
plot_data4$regulation <- ifelse(plot_data4$PFAS_ID %in% lacking, "none",
                          ifelse(plot_data4$PFAS_ID %in% REACH, "REACH",
                          ifelse(plot_data4$PFAS_ID %in% SCPoPs, "SCPoPs", NA)))

plot_data4$regulation <- factor(plot_data4$regulation, levels = c("none", "REACH", "SCPoPs"))

# Remove rows where the regulation column is NA
plot_data4 <- plot_data4 %>% filter(!is.na(regulation))
```

```{r, eval=FALSE}
regulation_model <- run_model(plot_data4, ~ regulation -1)
save(regulation_model, file = here("Rmodels", "regulation_model.RData"))
```

```{r}
load(here("Rmodels", "regulation_model.RData"))
summary(regulation_model)
r2_regulation <- r2_ml(regulation_model, plot_data4)
predict.rma(regulation_model, newmods = c(1, 0, -1), transf = exp, addx = T)
predict.rma(regulation_model, newmods = c(1, -1, 0), transf = exp, addx = T)
```

```{r}
figS14 <- orchard_plot_new(regulation_model,
             transfm = "percent",
             mod = "regulation",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             colour = "black",
             fill = FALSE,
             trunk.size = 1,
             branch.size = 3.1,
             twig.size = 0.5) +
  annotate(geom = "text",
           x = 3.4,
           y = 8, 
           label = paste0("italic(R)^{2} == ", round(r2_regulation[1],4)),
           color ="black",
           parse = TRUE, 
           size = 4) +
  #ggtitle("c)")+
  theme(#plot.title = element_text(face = "bold", size = 16),
       legend.title = element_text(size = 13),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(size = 13),
       axis.text.x = element_text(size = 13)) +
  #ggtitle("C") +
  xlab("International regulation") +
  ylab("TMF") +
  #scale_y_break(c(11, 13)) +
  scale_y_continuous(limits = c(0, 11), breaks = seq(0, 11, by = 1))

figS14
```

```{r, eval=FALSE}
ggsave(here("figs/supplements", "figS14.png"), plot = fig_regulation, width = 9, height = 5, dpi = 300)
```

# World map location of food webs

```{r}
# Formatting coordinates

coords <- fw_data %>%
  # Round Latitude and Longitude
  mutate(
    Latitude = round(Latitude_DD, 0),  
    Longitude = round(Longitude_DD, 0)
  ) %>%
  # group_by(Latitude_DD, Longitude_DD, Ecosystem) %>%
  # reframe(
  #   count_FW = n(),  # Count how many FW_IDs share the same (rounded) Latitude and Longitude
  # ) %>%
  # rename(
  #   Latitude = Latitude_DD,
  #   Longitude = Longitude_DD
  # ) %>% 
  # mutate(
  #   Ecosystem = fct_recode(Ecosystem,
  #                          "estuarine/brackish/tidal" = "estuarine",
  #                          "estuarine/brackish/tidal" = "brackish",
  #                          "estuarine/brackish/tidal" = "tidal")) %>% 
  mutate(Ecosystem = ifelse(Ecosystem == "terrestrial", 
                                  "Terrestrial", 
                                  "Aquatic"))


# Load the world map data
world <- ne_countries(scale = "medium", returnclass = "sf")

# Plot the map with clusters and counts
w_map <- ggplot(data = world) +
  geom_sf(fill = "grey80") +  # Plot the world map
  geom_jitter(data = coords, aes(x = Longitude, y = Latitude, color = Ecosystem, alpha = 0.7), size = 2, width = 1.2, height = 1.2) + 
  theme(
    panel.background = element_rect(fill = "white"),  
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    axis.title.x = element_text(size = 8), 
    axis.title.y = element_text(size = 8),  
    panel.border = element_rect(colour = "black", fill = NA, size = 1),
    plot.margin = margin(t = 10, r = 10, b = 5, l = 5),
    legend.position = c(0.04, 0.15),  # adjust these numbers to fine-tune location
    legend.justification = c(0, 0),
    legend.direction = "horizontal",  # Display the legend horizontally
    legend.background = element_rect(fill = "transparent", color = NA),
    legend.key = element_rect(fill = "transparent", color = NA),
    legend.key.size = unit(0.2, "cm"),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6)) +
  guides(size = "none", alpha = "none", color = guide_legend(nrow = 2, byrow = TRUE, override.aes = list(size = 2))) +
  scale_color_manual(values = c("#114B5F", "#FB8B24")) +
  labs(color = "Ecosystem type:")

w_map
```

```{r, echo=FALSE, eval=FALSE}
# Save the  plot
ggsave(here("figs", "fig1.pdf"), plot = w_map, width = 170, height = 110, dpi = 600, units = 'mm')

fig1_data <- coords %>% 
  select(FW_ID, Ecosystem, Location, Latitude_DD, Longitude_DD)
write_csv(fig1_data, here("Rdata", "fig1_data.csv"))
```

# Single-moderator meta-regression models

In our meta-analysis, we have 4 categories of predictors:

-  Predictors belonging to the **research methods**.
-  Predictors belonging to the **geographical location** of food webs.
-  Predictors belonging to the **biological and ecological characteristics of food webs**.
-  Predictors belonging to the **PFAS characteristics**.

## Research methods

### Sample type: whole-organism or organ/tissue-specific analysis

```{r}
TMF_data2 <- TMF_data2 %>% 
  mutate(Sample_type = recode(
    Sample_type,
    "specific tissues and whole-organisms" = "specific tissues \n and whole-organisms",
    "whole-organisms only" = "whole-organisms \n only"
  ))
```

```{r, eval=FALSE}
sum(is.na(TMF_data2$Sample_type)) #checking the amount of NAs
#[1] 0
sample_model <- run_model(TMF_data2, ~ Sample_type -1)
save(sample_model, file = here("Rmodels", "sample_model.RData"))
```

```{r, echo=FALSE, warning=FALSE, fig.cap="Note: Maximum TMF value set to 10"}
load(here("Rmodels", "sample_model.RData"))
summary(sample_model)
r2_sample <- r2_ml(sample_model, TMF_data2)

fig3A <- orchard_plot_new2(sample_model,
                           transfm="percent",
             mod = "Sample_type",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 3.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_sample[1],4)),
           color ="black",
           parse = TRUE, 
           size = 2) +
  theme(plot.title = element_text(face = "bold", size  = 10),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.18),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Samples type") +
  #ylab("TMF") +
  ggtitle("A") +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#597802", "#114B5F", "#FB8B24"))

fig3A

predict.rma(sample_model, newmods = c(-1, 0, 1), transf = exp, addx = T)
```

```{r, echo=FALSE, eval=FALSE}
figS7 <- orchard_plot_new2(sample_model,
                           transfm="percent",
             mod = "Sample_type",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 3.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_sample[1],4)),
           color ="black",
           parse = TRUE, 
           size = 2) +
  theme(plot.title = element_text(face = "bold", size  = 10),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.18),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Samples type") +
  ylab("TMF") +
  scale_fill_manual(values = c("#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#597802", "#114B5F", "#FB8B24"))

ggsave(here("figs/supplements","figS7.png"),
       width = 8,
       height = 6)

fig3A_data <- TMF_data2 %>% 
  select(Study_ID, FW_ID, PFAS_ID, Sample_type, ln_TMF, ln_TMF_se)

write_csv(fig3A_data, here("Rdata", "fig3A_data.csv"))
```

### Concentration determination method

```{r, include=FALSE}
sum(is.na(TMF_data2$Conc_determ_method))
#[1] 16
TMF_data2_norm <- TMF_data2 %>%
  filter(!is.na(Conc_determ_method) & Conc_determ_method != "")
sum(is.na(TMF_data2_norm$Conc_determ_method))
#[1] 0

TMF_data2_norm <- TMF_data2_norm %>%
  mutate(Conc_determ_method = recode(
    Conc_determ_method,
    "polar lipid equivalent corrected concentrations" = "lw",
    "wet weight concentrations (ww)" = "ww",
    "protein equivalent corrected concentrations (pw)" = "pw",
    "lipid equivalent corrected concentrations (lw)" = "lw",
    "dry weight concentrations (dw)" = "dw",
    "apparent chemical activities corrected concentrations" = "aca",
    "albumin equivalent corrected concentrations" = "aq",
    "fresh weight (fw)" = "fw")) %>%
  group_by(Conc_determ_method) %>%
  filter(n_distinct(Study_ID) > 1) %>%
  ungroup()
```

```{r, eval=FALSE, warning=FALSE}
norm_model <- run_model(TMF_data2_norm, ~ Conc_determ_method - 1)
save(norm_model, file = here("Rmodels", "norm_model.RData"))
```

```{r, eval=FALSE, fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "norm_model.RData"))
summary(norm_model)
r2_norm <- r2_ml(norm_model, TMF_data2_norm)
   # R2_marginal R2_conditional 
   #  0.05408518     0.89910329 

fig_norm <- orchard_plot_new(norm_model,
                             transfm="percent",
             mod = "Conc_determ_method",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             colour = "black",
             fill = FALSE,
             trunk.size = 1,
             branch.size = 1,
             twig.size = 0.5) +
  annotate(geom = "text",
           x = 4.4,
           y = 10, 
           label = paste0("italic(R)^{2} == ", round(r2_norm[1],4)),
           color ="black",
           parse = TRUE, 
           size = 2) +
  #ggtitle("c)")+
  theme(plot.title = element_text(size = 18),
       legend.title = element_text(size = 11),
        legend.text = element_text(size = 9),
        legend.position = c(1, 0.15),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 14),
       axis.text.x = element_text(size = 14)) +
  ylim(NA, 12) +
  ylab("TMF")

fig_norm
```

```{r, include=FALSE}
TMF_data2_norm <- TMF_data2_norm %>%
  mutate(Normalization = recode(
    Conc_determ_method,
    "lw" = "Normalized",
    "ww" = "Not normalized",
    "pw" = "Normalized",
    "dw" = "Not normalized"
    ))
```

```{r, eval=FALSE, warning=FALSE}
norm_model2 <- run_model(TMF_data2_norm, ~ Normalization)
save(norm_model2, file = here("Rmodels", "norm_model2.RData"))
```

```{r, echo=FALSE, fig.cap="Note: Maximum TMF value set to 10"}
load(here("Rmodels", "norm_model2.RData"))
summary(norm_model2)
r2_norm2 <- r2_ml(norm_model2, TMF_data2_norm)

fig3B <- orchard_plot_new2(norm_model2,
                               transfm="percent",
             mod = "Normalization",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 2.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_norm2[1],4)),
           color ="black",
           parse = TRUE, 
           size = 2) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 10),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.23),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Determination method") +
  #ylab("TMF") +
  ggtitle("B") +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#114B5F", "#FB8B24"))

fig3B
```

```{r, eval=FALSE}
figS8 <- orchard_plot_new2(norm_model2,
                               transfm="percent",
             mod = "Normalization",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 2.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_norm2[1],4)),
           color ="black",
           parse = TRUE, 
           size = 2) +
  theme(plot.title = element_text(face = "bold", size  = 10),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.23),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Determination method") +
  ylab("TMF") +
  scale_fill_manual(values = c("#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#114B5F", "#FB8B24"))

ggsave(here("figs/supplements","figS8.png"),
       width = 8,
       height = 4)

fig3B_data <- TMF_data2_norm %>% 
  select(Study_ID, FW_ID, PFAS_ID, Normalization, ln_TMF, ln_TMF_se)

write_csv(fig3B_data, here("Rdata", "fig3B_data.csv"))
```

### Undetected strategy - Limit of Detection (LOD)

```{r, include=FALSE}
TMF_data2_undetected_strategy <- TMF_data2 %>%
  group_by(Censored_data_strategy) %>%
  summarise(
    n_effect_size = n(),
    n_study = n_distinct(Study_ID) 
  ) %>% 
  arrange(desc(n_study))

# Create a flextable
undetected_strategy_table <- flextable(TMF_data2_undetected_strategy)

undetected_strategy_table <- undetected_strategy_table %>%
  set_header_labels(n_effect_size = "Number of TMFs", n_study = "Number of Studies") %>%
  autofit()

# Create a new Word document
doc <- read_docx()

# Add the flextable to the Word document
doc <- body_add_flextable(doc, undetected_strategy_table)
```


```{r, eval=FALSE}
# Save the document
print(doc, target = "Rdata/undetected_strategy_table.docx")
```

Table for meta-regression analysis:
```{r}
# Recode the 'Censored_data_strategy' column
TMF_data2_undetected_strategy2 <- TMF_data2 %>%
  mutate(Censored_data_strategy = recode(Censored_data_strategy,
         
    # The limit value divided by two or squared root of two group
    "The LOQ value divided by two" = "Division by two or sqrt of two",
    "The MDL value divided by two" = "Division by two or sqrt of two",
    "The LOD value divided by two" = "Division by two or sqrt of two",
    "The LOD value divided by two or detection frequency multiplied by LOD value or imputation" = "Division by two or sqrt of two",
    "The LOD value divided by the square root of two" = "Division by two or sqrt of two",
    "The LOD value divided by the square root of two for values < LOD. The LOQ value divided by two for values < LOQ." = "Division by two or sqrt of two",
    "The LOQ value divided by the square root of two" = "Division by two or sqrt of two",
    
    # Substitution with zero group
    "Zero for values < LOD" = "Substitution with zero",
    "Zero for undetected. The MDL value divided by two for values < MDL." = "Substitution with zero",
    "Zero for values < LOD. The LOQ value divided by the square root of two for values < LOQ." = "Substitution with zero",
    "Zero for values < LOD. The LOQ value divided by two for values < LOQ." = "Substitution with zero",
    "Zero for values < LOQ. The LOD value divided by two for values < LOD." = "Substitution with zero",
    
    # Exclusion of data group
    "Exclusion of data if values were < LOD." = "Exclusion of data",
    "Exclusion of data if values were < LOQ." = "Exclusion of data",
    "Exclusion of data if values were < MDL." = "Exclusion of data",
    "Exclusion of values < LOD. The LOQ value divided by two for values < LOQ." = "Exclusion of data",
    
    # Others group
    "Imputation method" = "Others",
    "Models accounting for values below the LOD." = "Others",
    "Three method comparison" = "Others",
    
    # Random numbers group
    "Random numbers below half of the MDL" = "Random numbers",
    "Random numbers between 0 and the LOD value" = "Random numbers",
    "Random numbers between 0 and the LOD value divided by two" = "Random numbers",
    "Random numbers between 0 and the MDL value" = "Random numbers",
    
  )) %>% 
  mutate(Censored_data_strategy = fct_relevel(Censored_data_strategy, 
                                              "Division by two or sqrt of two")) %>% 
  filter(Censored_data_strategy != "Not provided") %>% 
  group_by(Censored_data_strategy) %>%
  mutate(
    n_effect_size = n(),
    n_study = n_distinct(Study_ID) 
  ) %>% 
  arrange(desc(n_study))

TMF_data2_undetected_strategy2$Censored_data_strategy <- factor(
  TMF_data2_undetected_strategy2$Censored_data_strategy, 
  levels = c("Others", "Exclusion of data", "Not provided", 
             "Division by two or sqrt of two", "Random numbers", "Substitution with zero"))

TMF_data2_undetected_strategy2 <- TMF_data2_undetected_strategy2 %>% 
mutate(Censored_data_strategy = recode(
    Censored_data_strategy,
    "Division by two or sqrt of two" = "Division by two \n or sqrt of two",
    "Substitution with zero" = "Substitution with \n zero"
  ))
```

```{r, eval=FALSE}
undetected_model <- run_model(TMF_data2_undetected_strategy2, ~ Censored_data_strategy -1)
save(undetected_model, file = here("Rmodels", "undetected_model.RData"))
```

```{r, echo=FALSE, fig.cap="Note: Maximum TMF value set to 10"}
load(here("Rmodels", "undetected_model.RData"))
summary(undetected_model)
r2_lod <- r2_ml(undetected_model, TMF_data2_undetected_strategy2)

fig3D <- orchard_plot_new2(undetected_model,
             transfm = "percent",
             mod = "Censored_data_strategy",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 5.4,
           y = 9,
           label = paste0("italic(R)^{2} == ", round(r2_lod[1],4)),
           color ="black",
           parse = TRUE,
           size = 2) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 10),
       legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.1),
       legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_text(size = 8)) +
  scale_size(range = c(0.5, 3)) +
  xlab("Treatment of undetected values") +
  ylab("TMF") +
  ggtitle("D") +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24"))
```

```{r, eval=FALSE}
figS10 <- orchard_plot_new2(undetected_model,
             transfm = "percent",
             mod = "Censored_data_strategy",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 5.4,
           y = 9,
           label = paste0("italic(R)^{2} == ", round(r2_lod[1],4)),
           color ="black",
           parse = TRUE,
           size = 2) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 10),
       legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.1),
       legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_text(size = 8)) +
  scale_size(range = c(0.5, 3)) +
  xlab("Treatment of undetected values") +
  ylab("TMF") +
  scale_fill_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24"))

ggsave(here("figs/supplements","figS10.png"),
       width = 8,
       height = 6)

fig3D_data <- TMF_data2_undetected_strategy2 %>% 
  select(Study_ID, FW_ID, PFAS_ID, Censored_data_strategy, ln_TMF, ln_TMF_se)

write_csv(fig3D_data, here("Rdata", "fig3D_data.csv"))
```


### N-isotope trophic enrichment factor (TEF)

```{r, include=FALSE}
sum(is.na(TMF_data2$TEF))
#[1] 98
TMF_data2_tef <- TMF_data2[complete.cases(TMF_data2[ , "TEF"]),]

TMF_data2_tef <- TMF_data2 %>%
  filter(!is.na(TEF) & TEF != "") %>%
  group_by(TEF) %>%
  filter(n_distinct(Study_ID) > 1) %>%
  ungroup()

sum(is.na(TMF_data2_tef$TEF))
#[1] 0
```

```{r, eval=FALSE}
tef_model <- run_model(TMF_data2_tef, ~ TEF-1)
save(tef_model, file = here("Rmodels", "tef_model.RData"))
```

```{r, echo=FALSE, fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "tef_model.RData"))
summary(tef_model)
r2_tef <- r2_ml(tef_model, TMF_data2_tef)
   # R2_marginal R2_conditional 
   #  0.04538842     0.88832187 

fig3C <- orchard_plot_new2(tef_model,
                            transfm="percent",
             mod = "TEF",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 4.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_tef[1],4)),
           color ="black",
           parse = TRUE, 
           size = 2) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 10),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.15),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Trophic Enrichment Factor") +
  ylab("TMF") +
  ggtitle("C") +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24"))
```

```{r, eval=FALSE, echo=FALSE}
figS9 <- orchard_plot_new2(tef_model,
                            transfm="percent",
             mod = "TEF",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.5,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.5,
             branch.size = 0.8,
             twig.size = 0.3) +
  annotate(geom = "text",
           x = 4.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_tef[1],4)),
           color ="black",
           parse = TRUE, 
           size = 2) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 10),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.15),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Trophic Enrichment Factor") +
  ylab("TMF") +
  scale_fill_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24"))

ggsave(here("figs/supplements","figS9.png"),
       width = 8,
       height = 5)

fig3C_data <- TMF_data2_tef %>% 
  select(Study_ID, FW_ID, PFAS_ID, TEF, ln_TMF, ln_TMF_se)

write_csv(fig3C_data, here("Rdata", "fig3C_data.csv"))
```

```{r, eval=FALSE, echo=FALSE}
# Combine plots with specified heights
fig3 <- (fig3A / fig3B) + fig3C + fig3D +
  plot_layout(heights = c(1.5, 1, 1.8, 2))

# Save the combined plot
ggsave(here("figs", "fig3.pdf"), plot = fig3, width = 180, height = 185, dpi = 600, units = 'mm')

```

### TL vs δ15N

```{r, include=FALSE}
sum(is.na(TMF_data2$Regression_variable)) #checking the amount of NAs
# [1] 10
TMF_data2_rv <- TMF_data2[complete.cases(TMF_data2[ , "Regression_variable"]),]

sum(is.na(TMF_data2_rv$Regression_variable))
#[1] 0
```

```{r, eval=FALSE}
rv_model <- run_model(TMF_data2_rv, ~ Regression_variable)
save(rv_model, file = here("Rmodels", "rv_model.RData"))
```

```{r, echo=FALSE, fig.cap="Note: Maximum TMF value set to 10"}
load(here("Rmodels", "rv_model.RData"))
summary(rv_model)
r2_rv <- r2_ml(rv_model, TMF_data2_rv)

fig_rv <- orchard_plot_new(rv_model,
                            transfm="percent",
             mod = "Regression_variable",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 45,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.6,
             branch.size = 3.1,
             twig.size = 0.5) +
  annotate(geom = "text",
           x = 2.4,
           y = 8, 
           label = paste0("italic(R)^{2} == ", round(r2_rv[1],4)),
           color ="black",
           parse = TRUE, 
           size = 4) +
  #ggtitle("c)")+
  theme(plot.title = element_text(size = 18),
       legend.title = element_text(size = 11),
        legend.text = element_text(size = 9),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 10),
       axis.text.x = element_text(size = 14)) +
  ylab("TMF") +
  ylim(NA, 10)

fig_rv
```

```{r, echo=FALSE, eval=FALSE}
ggsave(here("figs","regr_variab.png"),
       width = 8,
       height = 4)
```

## Geography

### Latitude

```{r, include=FALSE}
TMF_data2$Latitude_abs <- abs(TMF_data2$Latitude_DD)
```

```{r, eval=FALSE}
sum(is.na(TMF_data2$Latitude_abs)) #checking the amount of NAs
#[1] 0
lat_model <- run_model(TMF_data2, ~ scale(Latitude_abs))
save(lat_model, file = here("Rmodels", "lat_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "lat_model.RData"))
summary(lat_model)
r2_lat <- r2_ml(lat_model, TMF_data2)
   # R2_marginal R2_conditional 
   #  0.00220226     0.74106678 


lat_bubble <- orchaRd::mod_results(lat_model, 
                                   mod = "Latitude_abs", 
                                   group = "Study_ID")
                                   
  
fig5A <- bubble_plot_new(lat_bubble,
            mod = "Latitude_abs",
            group = "Study_ID",
            x = "Latitude_abs",
            y = "ln_TMF",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  geom_point(data = TMF_data2, aes(x = Latitude_abs,
                                   y = ln_TMF,
                                   size = 1/ln_TMF_se),
             color = "#597802",
             alpha = 0.2) +       
  annotate(geom ="text",
           x = 57,
           y = 3.1,
           label = paste0("italic(R)^{2} == ", round(r2_lat[1],4)),
           color = "black",
           parse = TRUE,
           size = 2) +
  #ggtitle("a)") +
  theme(plot.title = element_text(face = "bold", size = 9),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7)) +
  scale_size(range = c(0.5, 3)) +
  ggtitle("A") +
  xlab("Latitude (absolute value)") +
  ylab("ln TMF")
```

```{r, eval=FALSE}
fig5A_data <- TMF_data2 %>% 
  select(Study_ID, FW_ID, PFAS_ID, Latitude_abs, ln_TMF, ln_TMF_se)

write_csv(fig5A_data, here("Rdata", "fig5A_data.csv"))
```

### Geographic location

```{r}
# Generate a table with counts and percentages for each PFAS_ID and Location
combined_table <- TMF_data2 %>%
  mutate(
    PFAS_ID = case_when(
      PFAS_ID %in% c("6:2 Cl-PFESA", "8:2 Cl-PFESA") ~ "F-53B",
      TRUE ~ PFAS_ID  # Keep other PFAS_ID values unchanged
    )
  ) %>% 
  # Group by both PFAS_ID and Location
  count(PFAS_ID, Location) %>%
  # Calculate percentages within each PFAS_ID group
  group_by(PFAS_ID) %>%
  mutate(percentage = n / sum(n) * 100) %>%
  ungroup()  # Remove grouping for cleaner output

# View the result
combined_table

combined_table_wide <- combined_table %>%
  pivot_wider(
    names_from = Location,
    values_from = c(n, percentage),
    names_glue = "{Location}{ifelse(.value == 'n', '', paste0('_', .value))}"
  )

combined_table_wide
```

Counting the number of TMFs from different world regions for PFAS showing a statistically significant TMF above 1

```{r}
combined_table_wide2 <- combined_table_wide %>%
  filter(PFAS_ID %in% c("F-53B", "PFOS", "PFDA", "br-PFOS", "PFUnDA", "l-PFOS", "PFNA", "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA"))

# Define the desired PFAS_ID order
pfas_order <- c("F-53B", "PFOS", "PFDA", "br-PFOS", "PFUnDA", "l-PFOS", "PFNA", 
                        "PFTrDA", "PFDoDA", "FOSA", "PFHxS", "PFDS", "PFTeDA", "PFOA", 
                        "PFBA", "PFPeA", "PFHpA", "PFBS", "PFHxA")

# Reorder the factor levels in the PFAS_ID column
combined_table_wide2$PFAS_ID <- factor(combined_table_wide2$PFAS_ID, levels = pfas_order)

# Reorder the rows based on the new PFAS_ID order
combined_table_wide2 <- combined_table_wide2[order(combined_table_wide2$PFAS_ID), ]

# Define the desired column order
column_order <- c("PFAS_ID", "Antarctic Region", "Arctic Region", "East Asia", 
                          "West Asia", "Europe", "Mediterranean Region", "North America", "South America")

# Reorder columns
combined_table_wide2 <- combined_table_wide2[, column_order]

combined_table_wide2
```


```{r, include=FALSE}
sum(is.na(TMF_data2$Location)) #checking the amount of NAs
#[1] 0
TMF_data2_loc <- TMF_data2 %>%
  mutate(Location = recode(
    Location,
    "Arctic Region" = "Polar regions",
    "Antarctic Region" = "Polar regions")) %>%
  group_by(Location) %>%
  filter(n_distinct(Study_ID) > 1) %>%
  ungroup()
```

```{r, eval=FALSE}
location_model <- run_model(TMF_data2_loc, ~ Location - 1)
save(location_model, file = here("Rmodels", "location_model.RData"))
```

```{r, echo=FALSE, fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "location_model.RData"))
summary(location_model)
r2_location <- r2_ml(location_model, TMF_data2_loc)


figS2 <- orchard_plot_new(location_model,
                        transfm="percent",
             mod = "Location",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 45,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.6,
             branch.size = 3.1,
             twig.size = 0.5) +
  annotate(geom = "text",
           x = 4.4,
           y = 10, 
           label = paste0("italic(R)^{2} == ", round(r2_location[1],4)),
           color ="black",
           parse = TRUE, 
           size = 4) +
  #ggtitle("c)")+
  theme(plot.title = element_text(size = 18),
       legend.title = element_text(size = 11),
        legend.text = element_text(size = 9),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 11),
       axis.text.x = element_text(size = 11)) +
  ylab("TMF") +
  ylim(NA, 12)

figS2

#predict.rma(location_model, newmods = c(-1, 0, 1, 0), transf = exp, addx = T)
#predict.rma(location_model, newmods = c(0, -1, 1, 0), transf = exp, addx = T)
```

```{r, eval=FALSE, echo=FALSE}
ggsave(here("figs/supplements","figS2.png"),
       width = 9,
       height = 8)
```

## Bio/Ecological characteristics

### Type of breathing - top predator

```{r, include=FALSE}
sum(is.na(TMF_data2$Breathing_type)) #checking the amount of NAs
#[1] 133
TMF_data2_bt <- TMF_data2 %>%
  filter(!is.na(Breathing_type) & Breathing_type != "") %>% 
  mutate(Breathing_type = recode(
    Breathing_type,
    "Water breathing through skin" = "Water breathing",
    ))
sum(is.na(TMF_data2_bt$Breathing_type))
# [1] 0
```

```{r, eval=FALSE}
breath_model <- run_model(TMF_data2_bt, ~ Breathing_type)
save(breath_model, file = here("Rmodels", "breath_model.RData"))
```

```{r, echo=FALSE,fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "breath_model.RData"))
summary(breath_model)
r2_breath <- r2_ml(breath_model, TMF_data2_bt)


fig4A <- orchard_plot_new2(breath_model,
                               transfm="percent",
             mod = "Breathing_type",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.4,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.4,
             branch.size = 0.7,
             twig.size = 0.2) +
  annotate(geom = "text",
           x = 2.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_breath[1],4)),
           color ="black",
           parse = TRUE, 
           size = 1.8) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 8),
        legend.title = element_text(size = 5),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.3),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.y = element_text(size = 6),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Top predator") +
  ylab("TMF") +
  ggtitle("B") +
  #scale_y_break(c(11, 13)) +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24"))
```

```{r, eval=FALSE, echo=FALSE}
figS12 <- orchard_plot_new2(breath_model,
                               transfm="percent",
             mod = "Breathing_type",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.4,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.4,
             branch.size = 0.7,
             twig.size = 0.2) +
  annotate(geom = "text",
           x = 2.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_breath[1],4)),
           color ="black",
           parse = TRUE, 
           size = 1.8) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 8),
        legend.title = element_text(size = 5),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.3),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.y = element_text(size = 6),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Top predator") +
  ylab("TMF") +
  scale_fill_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24"))

ggsave(here("figs","figS12.png"),
       width = 8,
       height = 4)

fig4B_data <- TMF_data2_bt %>% 
  select(Study_ID, FW_ID, PFAS_ID, Breathing_type, ln_TMF, ln_TMF_se)

write_csv(fig4B_data, here("Rdata", "fig4B_data.csv"))
```

```{r, eval=FALSE}
TMF_data2_bt <- TMF_data2_bt %>% 
  mutate(int = interaction(Breathing_type,Sample_type, drop = T))
```

```{r, eval=FALSE}
breath_model_int <- run_model(TMF_data2_bt, ~ int)
save(breath_model_int, file = here("Rmodels", "breath_model_int.RData"))
```

```{r, echo=FALSE,fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "breath_model_int.RData"))
summary(breath_model_int)
r2_breath_int <- r2_ml(breath_model_int, TMF_data2_bt)



fig_breath_int <- orchard_plot_new(breath_model_int,
                               transfm="percent",
             mod = "int",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             colour = "black",
             fill = FALSE,
             trunk.size = 1,
             branch.size = 3.1,
             twig.size = 0.5) +
  annotate(geom = "text",
           x = 6.4,
           y = 8, 
           label = paste0("italic(R)^{2} == ", round(r2_breath_int[1],4)),
           color ="black",
           parse = TRUE, 
           size = 5) +
  #ggtitle("c)")+
  theme(legend.title = element_text(size = 13),
        legend.text = element_text(size = 12),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15),
        axis.text.y = element_text(size = 14),
       axis.text.x = element_text(size = 14)) +
  xlab("Interaction") +
  ylab("TMF") +
  #scale_y_break(c(11, 13)) +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24", "#E2EF70")) +
  scale_color_manual(values = c("#F28482", "#66101F", "#597802", "#114B5F", "#FB8B24", "#E2EF70"))

fig_breath_int
```

```{r, eval=FALSE, echo=FALSE}
ggsave(here("figs/supplements","breathing_type_tp_int.png"),
       width = 15,
       height = 7)
```

### Ecosystem type

```{r, include=FALSE}
TMF_data2 <- TMF_data2 %>%
  mutate(Ecosystem = recode(
    Ecosystem,
    "estuarine" = "estuarine/tidal/brackish",
    "brackish" = "estuarine/tidal/brackish",
    "tidal" = "estuarine/tidal/brackish"))
```

```{r, eval=FALSE}
sum(is.na(TMF_data2$Ecosystem)) #checking the amount of NAs
#[1] 0
eco_model <- run_model(TMF_data2, ~ Ecosystem -1)
save(eco_model, file = here("Rmodels", "eco_model.RData"))
```

```{r, echo=FALSE, warning=FALSE, fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "eco_model.RData"))
summary(eco_model)
r2_eco <- r2_ml(eco_model, TMF_data2)

fig_eco <- orchard_plot_new(eco_model,
                            transfm="percent",
                            mod = "Ecosystem",
                            group = "Study_ID",
                            xlab = "ln_TMF",
                            legend.pos = "bottom.right",
                            k.pos = "left",
                            angle = 45,
                            colour = "black",
                            fill = FALSE,
                            trunk.size = 0.6,
                            branch.size = 3.1,
                            twig.size = 0.5) +
  annotate(geom = "text",
           x = 4.4,
           y = 10, 
           label = paste0("italic(R)^{2} == ", round(r2_eco[1],4)),
           color ="black",
           parse = TRUE, 
           size = 4) +
  #ggtitle("c)")+
  theme(plot.title = element_text(size = 18),
       legend.title = element_text(size = 11),
        legend.text = element_text(size = 9),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 10),
       axis.text.x = element_text(size = 14)) +
  ylab("TMF") +
  ylim(NA, 12)

fig_eco
```

```{r, eval=FALSE, echo=FALSE}
ggsave(here("figs","ecosystem.png"),
       width = 8,
       height = 5)
```

### Marine vs freshwater

```{r}
TMF_data2_aquatic <- TMF_data2 %>%
  filter(Ecosystem == "marine" | Ecosystem == "freshwater")
```

```{r, eval=FALSE}
sum(is.na(TMF_data2_aquatic$Ecosystem)) #checking the amount of NAs
#[1] 0
eco_aq_model <- run_model(TMF_data2_aquatic, ~ Ecosystem)
save(eco_aq_model, file = here("Rmodels", "eco_aq_model.RData"))
```

```{r, echo=FALSE, warning=FALSE, fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "eco_aq_model.RData"))
summary(eco_aq_model)
r2_eco_aq <- r2_ml(eco_aq_model, TMF_data2_aquatic)

figS5 <- orchard_plot_new(eco_aq_model,
                            transfm="percent",
                            mod = "Ecosystem",
                            group = "Study_ID",
                            xlab = "ln_TMF",
                            legend.pos = "bottom.right",
                            k.pos = "left",
                            angle = 45,
                            colour = "black",
                            fill = FALSE,
                            trunk.size = 0.6,
                            branch.size = 3.1,
                            twig.size = 0.5) +
  annotate(geom = "text",
           x = 2.4,
           y = 10, 
           label = paste0("italic(R)^{2} == ", round(r2_eco_aq[1],4)),
           color ="black",
           parse = TRUE, 
           size = 4) +
  #ggtitle("c)")+
  theme(plot.title = element_text(size = 18),
       legend.title = element_text(size = 11),
        legend.text = element_text(size = 9),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 10),
       axis.text.x = element_text(size = 14)) +
  ylab("TMF") +
  ylim(NA, 12.5)

figS5
```

```{r, eval=FALSE, echo=FALSE}
ggsave(here("figs/supplements","figS5.png"),
       width = 8,
       height = 5)
```

### Type of breathing - food web

```{r, include=FALSE}
sum(is.na(TMF_data2$Breathing_type_fw))
# [1] 0

TMF_data2 <- TMF_data2 %>% 
  mutate(Breathing_type_fw = recode(
    Breathing_type_fw,
    "not water-breathing only" = "water and \n air breathing",
    "water-breathing only" = "water breathing \n only"
  ))
```

```{r, eval=FALSE}
bt_fw_model <- run_model(TMF_data2, ~ Breathing_type_fw)
save(bt_fw_model, file = here("Rmodels", "bt_fw_model.RData"))
```

```{r, echo=FALSE, warning=FALSE, fig.cap="Note: Maximum TMF value set to 12"}
load(here("Rmodels", "bt_fw_model.RData"))
summary(bt_fw_model)
r2_bt_fw <- r2_ml(bt_fw_model, TMF_data2)

fig4B <- orchard_plot_new2(bt_fw_model,
            transfm="percent",
             mod = "Breathing_type_fw",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
            alpha = 0.4,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.4,
             branch.size = 0.7,
             twig.size = 0.2) +
  annotate(geom = "text",
           x = 2.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_bt_fw[1],4)),
           color ="black",
           parse = TRUE, 
           size = 1.8) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 8),
        legend.title = element_text(size = 5),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.3),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.y = element_text(size = 6),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Organisms") +
  ylab("TMF") +
  ggtitle("A") +
  #scale_y_break(c(11, 13)) +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#114B5F", "#FB8B24")) #+
 # scale_y_break(c(11, 13))
```

```{r, eval=FALSE, echo=FALSE}
figS11 <- orchard_plot_new2(bt_fw_model,
            transfm="percent",
             mod = "Breathing_type_fw",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
            alpha = 0.4,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.4,
             branch.size = 0.7,
             twig.size = 0.2) +
  annotate(geom = "text",
           x = 2.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_bt_fw[1],4)),
           color ="black",
           parse = TRUE, 
           size = 1.8) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size  = 8),
        legend.title = element_text(size = 5),
        legend.text = element_text(size = 5),
        legend.position = c(1, 0.3),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.y = element_text(size = 6),
       axis.text.x = element_blank()) +
  scale_size(range = c(0.5, 3)) +
  xlab("Organisms") +
  ylab("TMF") +
  scale_fill_manual(values = c("#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#114B5F", "#FB8B24")) 

ggsave(here("figs","figS11.png"),
       width = 8,
       height = 4)

fig4A_data <- TMF_data2 %>% 
  select(Study_ID, FW_ID, PFAS_ID, Breathing_type_fw, ln_TMF, ln_TMF_se)

write_csv(fig4A_data, here("Rdata", "fig4A_data.csv"))
```

### Trophic position of the food web baseline

```{r, include=FALSE}
sum(is.na(TMF_data2$TL_lowest)) #checking the amount of NAs
#[1] 149
TMF_data2_TL_lowest <- TMF_data2[complete.cases(TMF_data2[ , "TL_lowest"]),]
sum(is.na(TMF_data2_TL_lowest$TL_lowest))
#[1] 0
```

```{r, eval=FALSE}
TL_lowest_model <- run_model(TMF_data2_TL_lowest, ~scale(TL_lowest))
save(TL_lowest_model, file = here("Rmodels", "TL_lowest_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "TL_lowest_model.RData"))
summary(TL_lowest_model)
r2_TL_lowest <- r2_ml(TL_lowest_model, TMF_data2_TL_lowest)
   # R2_marginal R2_conditional 
   #  0.02422045     0.88474369 


TL_lowest_bubble <- orchaRd::mod_results(TL_lowest_model, 
                                   mod = "TL_lowest", 
                                   group = "Study_ID")
                                   
  
fig5B <- bubble_plot_new(TL_lowest_bubble,
            mod = "TL_lowest",
            group = "Study_ID",
            x = "TL_lowest",
            y = "ln_TMF",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  geom_point(data = TMF_data2, aes(x = TL_lowest,
                                   y = ln_TMF,
                                   size = 1/ln_TMF_se),
             color = "#114B5F",
             alpha = 0.2) +   
  annotate(geom ="text",
           x = 3.1,
           y = 3.1,
           label = paste0("italic(R)^{2} == ", round(r2_TL_lowest[1],4)),
           color = "black",
           parse = TRUE,
           size = 2) +
  #ggtitle("a)") +
  theme(plot.title = element_text(face = "bold", size = 9),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 7)) +
  scale_size(range = c(0.5, 3)) +
  ggtitle("B") +
  xlab("Trophic level of the baseline organism") +
  ylab("ln TMF")
```

```{r, eval=FALSE, echo=FALSE}
fig5B_data <- TMF_data2_TL_lowest %>% 
  select(Study_ID, FW_ID, PFAS_ID, TL_lowest, ln_TMF, ln_TMF_se)

write_csv(fig5B_data, here("Rdata", "fig5B_data.csv"))
```

### Trophic position of the top predator

```{r, include=FALSE}
sum(is.na(TMF_data2$TL_highest)) #checking the amount of NAs
#[1] 149
TMF_data2_TL_highest <- TMF_data2[complete.cases(TMF_data2[ , "TL_highest"]),]
sum(is.na(TMF_data2_TL_highest$TL_highest))
#[1] 0
```

```{r, eval=FALSE}
TL_highest_model <- run_model(TMF_data2_TL_highest, ~scale(TL_highest))
save(TL_highest_model, file = here("Rmodels", "TL_highest_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "TL_highest_model.RData"))
summary(TL_highest_model)
r2_TL_highest <- r2_ml(TL_highest_model, TMF_data2_TL_highest)

TL_highest_bubble <- orchaRd::mod_results(TL_highest_model, 
                                   mod = "TL_highest", 
                                   group = "Study_ID")
                                   
fig5C <- bubble_plot_new(TL_highest_bubble,
            mod = "TL_highest",
            group = "Study_ID",
            x = "TL_highest",
            y = "ln_TMF",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  geom_point(data = TMF_data2, aes(x = TL_highest,
                                   y = ln_TMF,
                                   size = 1/ln_TMF_se),
             color = "#66101F",
             alpha = 0.2) +  
  annotate(geom ="text",
           x = 5,
           y = 3.1,
           label = paste0("italic(R)^{2} == ", round(r2_TL_highest[1],4)),
           color = "black",
           parse = TRUE,
           size = 2) +
  #ggtitle("a)") +
  theme(plot.title = element_text(face = "bold", size = 9),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7)) +
  scale_size(range = c(0.5, 3)) +
  ggtitle("C") +
  xlab("Trophic level of the top predator") +
  ylab("ln TMF")
```


```{r, eval=FALSE, echo=FALSE}
fig5C_data <- TMF_data2_TL_highest %>% 
  select(Study_ID, FW_ID, PFAS_ID, TL_highest, ln_TMF, ln_TMF_se)

write_csv(fig5C_data, here("Rdata", "fig5C_data.csv"))
```

### Food web length

```{r, include=FALSE}
sum(is.na(TMF_data2$fw_length)) #checking the amount of NAs
#[1] 149
TMF_data2_fw_length <- TMF_data2[complete.cases(TMF_data2[ , "fw_length"]),]
sum(is.na(TMF_data2_fw_length$fw_length))
#[1] 0
```

```{r, eval=FALSE}
fw_length_model <- run_model(TMF_data2_fw_length, ~scale(fw_length)-1)
save(fw_length_model, file = here("Rmodels", "fw_length_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "fw_length_model.RData"))
summary(fw_length_model)
r2_fw_length <- r2_ml(fw_length_model, TMF_data2_fw_length)
   # R2_marginal R2_conditional 
   #  0.02422045     0.88474369 


fw_length_bubble <- orchaRd::mod_results(fw_length_model, 
                                   mod = "fw_length", 
                                   group = "Study_ID")
                                   
  
fig5D <- bubble_plot_new(fw_length_bubble,
            mod = "fw_length",
            group = "Study_ID",
            x = "fw_length",
            y = "ln_TMF",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  geom_point(data = TMF_data2, aes(x = fw_length,
                                   y = ln_TMF,
                                   size = 1/ln_TMF_se),
             color = "#F28482",
             alpha = 0.2) +  
  annotate(geom ="text",
           x = 3.5,
           y = 3.1,
           label = paste0("italic(R)^{2} == ", round(r2_fw_length[1],4)),
           color = "black",
           parse = TRUE,
           size = 2) +
  #ggtitle("a)") +
  theme(plot.title = element_text(face = "bold", size = 9),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 7)) +
  scale_size(range = c(0.5, 3)) +
  ggtitle("D") +
  xlab("Number of trophic levels") +
  ylab("ln TMF")
```

```{r, eval=FALSE, echo=FALSE}
fig5D_data <- TMF_data2_fw_length %>% 
  select(Study_ID, FW_ID, PFAS_ID, fw_length, ln_TMF, ln_TMF_se)

write_csv(fig5D_data, here("Rdata", "fig5D_data.csv"))
```

### Number of species

```{r, eval=FALSE}
sum(is.na(TMF_data2$n_species)) #checking the amount of NAs
#[1] 0
n_species_model <- run_model(TMF_data2, ~scale(n_species))
save(n_species_model, file = here("Rmodels", "n_species_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "n_species_model.RData"))
summary(n_species_model)

r2_n_species <- r2_ml(n_species_model, TMF_data2)

n_species_bubble <- orchaRd::mod_results(n_species_model, 
                                   mod = "n_species", 
                                   group = "Study_ID")
                                   
  
fig_n_species <- bubble_plot(n_species_bubble,
            mod = "n_species",
            group = "Study_ID",
            x = "n_species",
            y = "ln_TMF",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  annotate(geom ="text",
           x = 30,
           y = 4,
           label = paste0("italic(R)^{2} == ", round(r2_n_species[1],4)),
           color = "black",
           parse = TRUE,
           size = 4) +
  #ggtitle("a)") +
  theme(plot.title = element_text(size = 16),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        axis.title.x = element_text(size = 14),
        axis.title.y = element_text(size = 14),
        axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12)) +
  xlab("Number of species in the food web")

fig_n_species
```

```{r, eval=FALSE, echo=FALSE}
ggsave(here("figs","n_species.png"),
       width = 8,
       height = 5)
```

## PFAS properties

### carbon chain length

```{r, include=FALSE}
sum(is.na(TMF_data2$ccl)) #checking the amount of NAs
#[1] 23
TMF_data2_ccl <- TMF_data2[complete.cases(TMF_data2[ , "ccl"]),]
sum(is.na(TMF_data2_ccl$ccl))
#[1] 0
```

```{r, eval=FALSE}
ccl_model <- run_model(TMF_data2_ccl, ~scale(ccl))
save(ccl_model, file = here("Rmodels", "ccl_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "ccl_model.RData"))
summary(ccl_model)
r2_ccl <- r2_ml(ccl_model, TMF_data2_ccl)

ccl_bubble <- orchaRd::mod_results(ccl_model, 
                                   mod = "ccl", 
                                   group = "Study_ID")
                                   
  
fig5E <- bubble_plot_new(ccl_bubble,
            mod = "ccl",
            group = "Study_ID",
            x = "ccl",
            y = "ln_TMF",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  geom_point(data = TMF_data2, aes(x = ccl,
                                   y = ln_TMF,
                                   size = 1/ln_TMF_se),
             color = "#DDC9B4",
             alpha = 0.2) +  
  annotate(geom ="text",
           x = 12,
           y = 3,
           label = paste0("italic(R)^{2} == ", round(r2_ccl[1],4)),
           color = "black",
           parse = TRUE,
           size = 2) +
  ggtitle("E") +
  theme(plot.title = element_text(face = "bold", size = 9),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        axis.text.y = element_text(size = 7),
        axis.text.x = element_text(size = 7)) +
  scale_size(range = c(0.5, 3)) +
  xlab("Carbon chain length") +
  ylab("ln TMF") +
  scale_x_continuous(limits = c(3, 15), breaks = seq(3, 15, by = 3))
```

```{r, eval=FALSE, echo=FALSE}
fig5E_data <- TMF_data2_ccl %>% 
  select(Study_ID, FW_ID, PFAS_ID, ccl, ln_TMF, ln_TMF_se)

write_csv(fig5E_data, here("Rdata", "fig5E_data.csv"))
```

### perfluoroalkyl chain length

```{r, include=FALSE}
sum(is.na(TMF_data2$perfluoroalkyl_ccl)) #checking the amount of NAs
#[1] 30
TMF_data2_p_ccl <- TMF_data2[complete.cases(TMF_data2[ , "perfluoroalkyl_ccl"]),]
sum(is.na(TMF_data2_p_ccl$perfluoroalkyl_ccl))
#[1] 0
```

```{r, eval=FALSE}
p_ccl_model <- run_model(TMF_data2_p_ccl, ~scale(perfluoroalkyl_ccl))
save(p_ccl_model, file = here("Rmodels", "p_ccl_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "p_ccl_model.RData"))
summary(p_ccl_model)
r2_p_ccl <- r2_ml(p_ccl_model, TMF_data2_p_ccl)

p_ccl_bubble <- orchaRd::mod_results(p_ccl_model, 
                                   mod = "perfluoroalkyl_ccl", 
                                   group = "Study_ID")
                                   
  
figS3 <- bubble_plot(p_ccl_bubble,
            mod = "perfluoroalkyl_ccl",
            group = "Study_ID",
            x = "perfluoroalkyl_ccl",
            y = "ln_TMF",
            est.lwd = 1,
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  geom_point(data = TMF_data2_p_ccl, aes(x = perfluoroalkyl_ccl,
                                   y = ln_TMF,
                                   size = 1/ln_TMF_se),
             color = "#DDC9B4",
             alpha = 0.2) +  
  annotate(geom ="text",
           x = 14,
           y = 3,
           label = paste0("italic(R)^{2} == ", round(r2_p_ccl[1],4)),
           color = "black",
           parse = TRUE,
           size = 5) +
  #ggtitle("E") +
  theme(plot.title = element_text(face = "bold", size = 18),
        legend.title = element_text(size = 15),
        legend.text = element_text(size = 14),
        axis.title.x = element_text(size = 17),
        axis.title.y = element_text(size = 17),
        axis.text.y = element_text(size = 16),
        axis.text.x = element_text(size = 16)) +
  xlab("Perfluoroalkyl chain length") +
  ylab("ln TMF") +
  scale_x_continuous(limits = c(3, 15), breaks = seq(3, 15, by = 3))

figS3
```

```{r, eval=FALSE}
ggsave(here("figs/supplements","figS3.png"),
       width = 8,
       height = 4)
```

### PFAS class

```{r, include=FALSE}
sum(is.na(TMF_data2$Class))
#[1] 8
TMF_data2_class <- TMF_data2[complete.cases(TMF_data2[ , "Class"]),]
sum(is.na(TMF_data2_class$Class))
#[1] 0

TMF_data2_class <- TMF_data2_class %>% 
  mutate(Class = recode(
    Class,
    "Precursor and/or intermediate" = "Precursors",
    "PFSA" = "PFSAs",
    "PFCA" = "PFCAs",
    "Emerging PFAS" = "Emerging"
  ))
```

```{r, eval=FALSE}
class_model <- run_model(TMF_data2_class, ~ Class-1)

save(class_model, file = here("Rmodels", "class_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "class_model.RData"))
summary(class_model)
r2_class <- r2_ml(class_model, TMF_data2_class)

fig4C <- orchard_plot_new2(class_model,
             transfm="percent",
             mod = "Class",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.4,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.4,
             branch.size = 0.7,
             twig.size = 0.2) +
  annotate(geom = "text",
           x = 4.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_class[1],4)),
           color ="black",
           parse = TRUE, 
           size = 1.8) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size = 8),
       legend.title = element_text(size = 5),
        legend.text = element_text(size = 5),
       legend.position = c(1, 0.18),
       legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 7),
       #axis.title.x = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.y = element_text(size = 6),
       axis.text.x = element_text(size = 6)) +
  scale_size(range = c(0.5, 3)) +
  ggtitle("C") +
  xlab("PFAS class") +
  ylab("TMF") +
  #scale_y_break(c(11, 13)) +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24"))
```

```{r, eval=FALSE}
figS13 <- orchard_plot_new2(class_model,
             transfm="percent",
             mod = "Class",
             group = "Study_ID",
             xlab = "ln_TMF",
             legend.pos = "bottom.right",
             k.pos = "left",
             angle = 0,
             alpha = 0.4,
             colour = "black",
             fill = FALSE,
             trunk.size = 0.4,
             branch.size = 0.7,
             twig.size = 0.2) +
  annotate(geom = "text",
           x = 4.4,
           y = 9, 
           label = paste0("italic(R)^{2} == ", round(r2_class[1],4)),
           color ="black",
           parse = TRUE, 
           size = 1.8) +
  #ggtitle("c)")+
  theme(plot.title = element_text(face = "bold", size = 8),
       legend.title = element_text(size = 5),
        legend.text = element_text(size = 5),
       legend.position = c(1, 0.18),
       legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 7),
       #axis.title.x = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.y = element_text(size = 6),
       axis.text.x = element_text(size = 6)) +
  scale_size(range = c(0.5, 3)) +
  xlab("PFAS class") +
  ylab("TMF") +
  scale_y_continuous(limits = c(0, 14), breaks = seq(0, 14, by = 1)) +
  scale_fill_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24")) +
  scale_color_manual(values = c("#66101F", "#597802", "#114B5F", "#FB8B24"))

ggsave(here("figs","figS13.png"),
       width = 8,
       height = 5)

fig4C_data <- TMF_data2_class %>% 
  select(Study_ID, FW_ID, PFAS_ID, Class, ln_TMF, ln_TMF_se)

write_csv(fig4C_data, here("Rdata", "fig4C_data.csv"))
```

```{r, eval=FALSE, echo=FALSE}
# Combine plots with specified heights
fig4 <- (fig4A / fig4B) + fig4C +
  plot_layout(heights = c(1, 1, 2))

# Save the combined plot
ggsave(here("figs", "fig4.pdf"), plot = fig4, width = 180, height = 140, dpi = 600, units = 'mm')

```

# Correlation assessment

```{r, include=FALSE}
TMF_data2_corr <- TMF_data2 %>%
  mutate(Breathing_type = recode(
    Breathing_type,
    "Water breathing through skin" = "Water \n breathing",
    "Water breathing" = "Water \n breathing",
    "Air breathing" = "Air \n breathing",
    )) %>% 
  mutate(Breathing_type_fw = recode(
    Breathing_type_fw,
    "not water-breathing only" = "not water \n breathing only",
    "water-breathing only" = "water \n breathing only",
    )) %>% 
  mutate(Sample_type = recode(
    Sample_type,
    "whole-organisms only" = "whole \n organisms only",
    "specific tissues" = "specific \n tissues",
    "specific tissues and whole-organisms" = "specific tissues \n and whole-organisms",
    )) %>% 
  filter(!is.na(Breathing_type) & Breathing_type != "") %>%
  group_by(Sample_type, Breathing_type_fw, Breathing_type) %>%
  summarise(Frequency = n()) %>%
  ungroup() #%>% 
  # mutate(TL_highest = case_when(
  #   TL_highest < 3 ~ "< 3",
  #   TL_highest >= 3 & TL_highest < 3.5 ~ "3 - 3.5",
  #   TL_highest >= 3.5 & TL_highest < 4 ~ "3.5 - 4",
  #   TL_highest >= 4 & TL_highest < 4.5 ~ "4 - 4.5",
  #   TL_highest >= 4.5 & TL_highest <= 5 ~ "4.5 - 5",
  #   TL_highest >= 5 ~ "more than 5",
  #   TRUE ~ as.character(TL_highest)  # Keep original value if it doesn't fit in the specified ranges
  # )) %>%
  #filter(!is.na(TL_highest))
```


```{r, echo=FALSE}
# Create the alluvial plot - Sample type and breathign type top predator
figS15 <- ggplot(TMF_data2_corr,
       aes(axis1 = Sample_type, axis2 = Breathing_type_fw, axis3 = Breathing_type, y = Frequency)) +
  geom_alluvium(aes(fill = Sample_type)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), size = 3.2, angle = 45) +
  scale_x_discrete(limits = c("Type of samples", "Breathing type (food web)", "Breathing type (top predator)"), expand = c(.05, .05)) +
  scale_fill_npg() +
  labs(x = "Categorical variables", y = "TMF frequency") +
  theme_classic() +
  theme(legend.position = "none")

figS15
```

```{r, eval=FALSE}
ggsave(here("figs/supplements","figS15.png"),
       width = 10,
       height = 7)
```

```{r, include=FALSE}
TMF_data2_loc_agg <- TMF_data2_loc %>%
  group_by(Regression_variable, Location) %>%
  summarise(Frequency = n()) %>%
  ungroup()

# Create the alluvial plot - Regression variable and location
ggplot(TMF_data2_loc_agg,
       aes(axis1 = Regression_variable, axis2 = Location, y = Frequency)) +
  geom_alluvium(aes(fill = Regression_variable)) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Regression variable", "Geographical location"), expand = c(.05, .05)) +
  labs(x = "Categories", y = "Frequency") +
  theme_minimal() +
  theme(legend.position = "none")
```

```{r}
cor.test(TMF_data2$fw_length, TMF_data2$TL_highest)
cor.test(TMF_data2$fw_length, TMF_data2$n_species)
```

# Full model

```{r}
TMF_data_fmodel <- TMF_data2 %>% 
  mutate(Sample_type = recode(
    Sample_type,
    "specific tissues and whole-organisms" = "mixed"
  )) %>% 
  mutate(Conc_determ_method = recode(
    Conc_determ_method,
    "polar lipid equivalent corrected concentrations" = "Normalized",
    "wet weight concentrations (ww)" = "Not normalized",
    "protein equivalent corrected concentrations (pw)" = "Normalized",
    "lipid equivalent corrected concentrations (lw)" = "Normalized",
    "dry weight concentrations (dw)" = "Not normalized",
    "apparent chemical activities corrected concentrations" = "Normalized",
    "albumin equivalent corrected concentrations" = "Normalized",
    "fresh weight (fw)" = "Not normalized")) %>%
  filter(!is.na(Breathing_type) & Breathing_type != "") %>% 
  mutate(Breathing_type = recode(
    Breathing_type,
    "Water breathing through skin" = "Water breathing",
    )) %>% 
  mutate(Class = recode(
    Class,
    "Precursor and/or intermediate" = "Precursor/intermediate"
  ))
  
VCV_fmodel <- vcalc(vi = TMF_data_fmodel$ln_TMF_se^2, 
             cluster = TMF_data_fmodel$FW_ID, 
             obs = TMF_data_fmodel$TMF_ID, 
             rho = 0.5)
```


```{r, eval=FALSE}
TMF_data_fmodel %>%
  filter(Censored_data_strategy == "Not provided") %>%
  tally()
#     n
# 1 281

sum(is.na(TMF_data_fmodel$TEF))
# [1] 83
sum(is.na(TMF_data_fmodel$TL_lowest))
# [1] 119
sum(is.na(TMF_data_fmodel$TL_highest))
# [1] 119
sum(is.na(TMF_data_fmodel$fw_length))
# [1] 119
full_model <- rma.mv(yi = ln_TMF,
                     V = VCV_fmodel, 
                     mods = ~  1 + 
                       Sample_type +
                       Conc_determ_method +
                       #Censored_data_strategy +
                       TEF +
                       Breathing_type_fw +
                       Breathing_type +
                       Class +
                       scale(Latitude_abs) +
                       #scale(TL_lowest) +
                       #scale(TL_highest) +
                       #scale(fw_length) +
                       scale(ccl),
                     random = list(~1|Study_ID, 
                                   ~1|FW_ID, 
                                   ~1|PFAS_ID, 
                                   ~1|TMF_ID 
                                   ),
                     test = "t",
                     data = TMF_data_fmodel,
                     sparse = TRUE)

save(full_model, file = here("Rmodels", "full_model.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "full_model.RData"))
summary(full_model)
r2_ml(full_model, TMF_data_fmodel)
```

# Model selection
 
```{r, eval=FALSE}
eval(metafor:::.MuMIn) # use eval() function to extract helper functions from MuMIn and make them usable in metafor.
mod.candidate <- dredge(full_model, beta = "none", evaluate = TRUE, rank = "AICc", trace=2) # dredge to produce all possible candidate models

# Save the candidate models
save(mod.candidate, file = here("Rmodels", "mod_candidate.RData"))
```

```{r}
# Next step, let’s select a sets of best models.
load(here("Rmodels", "mod_candidate.RData"))
subset(mod.candidate, delta <= 4, recalc.weights = FALSE)
# Sum of weights for each variable included in the mod.candidate
sw(mod.candidate)
```

```{r}
weights <- read_csv(here("Rdata", "aic_weights.csv")) #upload data from sw(mod.candidate)

weights <- weights %>% 
  mutate(weights_percentage = round( Sum_of_weights * 100))

weights$Predictor <- factor(weights$Predictor, levels = weights$Predictor[order(weights$weights_percentage, weights$R2_marginal)])


figS16 <- ggplot(weights, aes(Predictor, Sum_of_weights)) +
  geom_col(aes(fill = R2_marginal), width = 0.7) +  # Gradient fill based on R2_marginal
  geom_text(aes(label = paste0(weights_percentage, "%"), x = Predictor), 
            position = position_stack(vjust = 0.5), 
            size = 3) +
  geom_text(aes(label = paste("R2 =", sprintf("%.3f", R2_marginal)), x = Predictor, y = max(Sum_of_weights)), 
            position = position_stack(vjust = 1.07), 
            size = 2.5, color = "black") +
  theme_light() +
  coord_flip() +
  scale_fill_gradient(low = "skyblue", high = "royalblue", name = "R2 Marginal") +  # Color gradient
  scale_x_discrete(name = "Predictor") +
  scale_y_continuous(name = "AIC weights",
                     breaks = seq(0, 1, by = 0.2)) +
  theme(legend.position = "right",  # Move legend to the right
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.text = element_text(size = 10),
        panel.grid.major = element_line(color = "grey", 
                                        linewidth = 0.2, 
                                        linetype = "dashed"),
        panel.grid.minor = element_line(color = "grey", 
                                        linewidth = 0.2, 
                                        linetype = "dotted"))
figS16
```


```{r, eval=FALSE}
ggsave(here("figs/supplements","figS16.png"),
       width = 9,
       height = 4)
```

# Risk of Bias assessment

```{r}
TMF_data2_RoB <- TMF_data2 %>%
  filter(!if_any(c(Selection_bias, Measurement_bias, Reporting_bias, Funding_bias), ~ . == "High risk"))

VCV_RoB <- vcalc(vi = TMF_data2_RoB$ln_TMF_se^2, 
             cluster = TMF_data2_RoB$FW_ID,
             obs = TMF_data2_RoB$TMF_ID, 
             rho = 0.5)
```

```{r, eval=FALSE}
mod_RoB <- rma.mv(yi = ln_TMF, # Natural logarithm of the Trophic Magnification Factor
              V = VCV_RoB, # Variance co-variance matrix
              random = list(~1|Study_ID, 
                            ~1|FW_ID, 
                            ~1|PFAS_ID, 
                            ~1|TMF_ID 
                            ),
              test = "t", 
              sparse = T,
              data = TMF_data2_RoB)

save(mod_RoB, file = here("Rmodels", "mod_RoB.RData"))
```

```{r, warning=FALSE, echo=FALSE}
load(here("Rmodels", "mod_RoB.RData"))
summary(mod_RoB)
i2_ml(mod_RoB)

I2_mod_RoB <- orchaRd::i2_ml(mod_RoB)
figS21 <- orchard_plot_new(mod_RoB,
                        transfm = "percent",
                        mod = "1",
                        group = "Study_ID", 
                        xlab = "ln_TMF",
                        k.pos = "left",
                        alpha = 0.6,
                        trunk.size = 1.5,
                        branch.size = 2.7,
                        twig.size = 0.4,
                        colour = FALSE,
                        fill = FALSE) +  
  annotate(geom = "text",
           x = 1.3,
           y = 7.5, 
           label = paste0("italic(I)^{2} == ", round(I2_mod_RoB[1],4)),
           size = 6,
           color ="black",
           parse = TRUE) +
  scale_size_continuous(range = c(1, 10)) + # change point scaling
  theme(panel.border = element_rect(colour = "black", 
                                    fill = NA,
                                    size = 1.3), 
       legend.title = element_text(size = 16),
        legend.text = element_text(size = 15),
        axis.title.x = element_text(size = 18),
        axis.title.y = element_text(size = 18),
        axis.text.y = element_blank(),
       axis.text.x = element_text(size = 17)) +
  #ylim(NA, 10) +
  xlab("Intercept") +
  ylab("TMF") +
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, by = 1))

figS21
```

```{r, eval=FALSE}
ggsave(here("figs/supplements","figS21.png"),
       width = 10,
       height = 6)
```

# Publication bias

## Visual inspection - Funnel plot

```{r}
# Increase text size for x and y axes
par(cex.axis = 1.5)

# Increase label size for x and y axes
par(cex.lab = 1.5)

figS17 <- funnel(
  full_model, 
  yaxis = "seinv", # Inverse of standard error (precision) as the y axis
  level = c(90, 95),  # levels of statistical significance highlighted 
  shade = c("white", "gray55"), # shades for different levels of statistical significance
  back = "#EBEBEB",
  legend = FALSE, # display legend
  ylab = "Precision (1/SE)", 
  cex.lab = 1.5, 
  digits = 1, 
  xlim = c(-5,5)
  )
```

## Small study effect

```{r, eval=FALSE}
mod_se <- rma.mv(ln_TMF,
                     VCV,
                     mods = ~ ln_TMF_se,
                     random = list(~1|Study_ID,
                                   ~1|FW_ID,
                                   ~1|PFAS_ID,
                                   ~1|TMF_ID
                                   ),
                     method = "REML", 
                     test = "t", 
                     data = TMF_data2
                     )

save(mod_se, file = here("Rmodels", "mod_se.RData"))
summary(mod_se)
mod_pb <- rma.mv(ln_TMF,
                 VCV,
                     method = "REML", 
                     test = "t", 
                     data = TMF_data2
                     )


robust(mod_pb, cluster = FW_ID, clubSandwich = T)
```

```{r}
load(here("Rmodels", "mod_se.RData"))
summary(mod_se)
sse_bubble <- orchaRd::mod_results(mod_se,
                                  mod = "ln_TMF_se",
                                  group = "Study_ID",
                                  data = TMF_data2)

figS18 <- orchaRd::bubble_plot(sse_bubble,
                     group = "Study_ID",
                     mod = "ln_TMF_se",
            legend.pos = "bottom.right",
            k.pos = "top.right",
            ci.col = "red",
            pi.col = "black",
            est.col = "black") +
  ggtitle("") +
  theme(plot.title = element_text(size = 18),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 14)) +
  xlab("lnSE") +
  ylab("lnTMF")

figS18
```

```{r, eval=FALSE}
ggsave(here("figs/supplements","figS18.png"),
       width = 10,
       height = 6)
```

## Time-lag bias

```{r, eval=FALSE}
MLMR_mod_year.c <- metafor::rma.mv(ln_TMF,
                            VCV,
                            mods = ~ scale(year_publication),
                            random = list(~1|Study_ID,
                                          ~1|FW_ID,
                                          ~1|PFAS_ID,
                                          ~1|TMF_ID
                                          ),
                            test = "t", 
                            sparse = T,
                            data = TMF_data2)

save(MLMR_mod_year.c, file = here("Rmodels", "MLMR_mod_year.c.RData"))
```

```{r, echo=FALSE}
load(here("Rmodels", "MLMR_mod_year.c.RData"))
summary(MLMR_mod_year.c)
r2_pbias <- r2_ml(MLMR_mod_year.c, TMF_data2)
pb_bubble <- orchaRd::mod_results(MLMR_mod_year.c,
                                  mod = "year_publication",
                                  group = "Study_ID",
                                  data = dat)

fig5F <- bubble_plot_new(pb_bubble,
                     group = "Study_ID",
                     mod = "year_publication",
            legend.pos = "bottom.right",
            k.pos = "bottom.left",
            ci.col = "red",
            pi.col = "black",
            est.col = "black",
            g = TRUE) +
  annotate(geom ="text",
           x = 2017,
           y = 3,
           label = paste0("italic(R)^{2} == ", round(r2_pbias[1],4)),
           color = "black",
           parse = TRUE,
           size = 2) +
  ggtitle("F") +
  theme(plot.title = element_text(face = "bold", size = 9),
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6),
        legend.key = element_blank(),
        legend.key.size = unit(0.3, "cm"),
        axis.title.x = element_text(size = 8),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 7)) +
  scale_size(range = c(0.5, 3)) +
  xlab("Publication year") +
  ylab("ln TMF") +
  scale_x_continuous(breaks = seq(2003, 2024, by = 5), limits = c(2003, 2024))
```

```{r, eval=FALSE, echo=FALSE}
# Combine plots with specified heights
fig5 <- (fig5A + fig5B) / (fig5C  + fig5D) / (fig5E + fig5F)

# Save the combined plot
ggsave(here("figs", "fig5.pdf"), plot = fig5, width = 180, height = 175, dpi = 300, units = 'mm')

fig5F_data <- TMF_data2 %>% 
  select(Study_ID, FW_ID, PFAS_ID, TMF_ID, year_publication, ln_TMF, ln_TMF_se)

write_csv(fig5F_data, here("Rdata", "fig5F_data.csv"))
```

## Leave-one-out-analysis
```{r, eval=FALSE}
TMF_data2 <- TMF_data2 %>%
  mutate(leave_out = Study_ID)

TMF_data2$leave_out <- as.factor(TMF_data2$leave_out)


LeaveOneOut_effectsize <- list()
for (i in 1:length(levels(TMF_data2$leave_out))) {
  temp_dat <- TMF_data2 %>%
    filter(leave_out != levels(TMF_data2$leave_out)[i])
  
  VCV_leaveout <- vcalc(vi = temp_dat$ln_TMF_se^2,
                        cluster = temp_dat$FW_ID, 
                        rho = 0.5)
  
  LeaveOneOut_effectsize[[i]] <-  rma.mv(yi = ln_TMF, # Natural logarithm of the Trophic Magnification Factor
              V = VCV_leaveout, # Variance co-variance matrix
              random = list(~1|Study_ID, # Between-study effect
                            ~1|FW_ID, # Between food webs effect
                            ~1|PFAS_ID, # Between type of PFAS effect
                            ~1|TMF_ID # Within-study effect
                            ),
              test = "t", 
              sparse = T,
              data = temp_dat[temp_dat$leave_out != levels(temp_dat$leave_out)[i], ])
                                         
}

# writing function for extracting est, ci.lb, and ci.ub from all models
est.func <- function(model) {
  df <- data.frame(est = model$b, lower = model$ci.lb, upper = model$ci.ub)
  return(df)
}

# using dplyr to form data frame
MA_oneout <- lapply(LeaveOneOut_effectsize,function(x) est.func(x)) %>%
  bind_rows %>%
  mutate(left_out = levels(TMF_data2$leave_out))


# telling ggplot to stop reordering factors
MA_oneout$left_out <- as.factor(MA_oneout$left_out)
MA_oneout$left_out <- factor(MA_oneout$left_out, levels = MA_oneout$left_out)

# saving the runs
#saveRDS(MA_oneout, here("Rdata", "MA_oneout.RDS"))
```

```{r}
MA_oneout <- readRDS(here("Rdata", "MA_oneout.RDS"))

# plotting
figS19 <- ggplot(MA_oneout) + geom_hline(yintercept = 0, lty = 2, lwd = 1) +

  geom_hline(yintercept = mod$ci.lb, lty = 3, lwd = 0.75, colour = "black") +
  geom_hline(yintercept = mod$b, lty = 1, lwd = 0.75, colour = "black") + 
  geom_hline(yintercept = mod$ci.ub,
             lty = 3, lwd = 0.75, colour = "black") + 
  geom_pointrange(aes(x = left_out, y = est,
                      ymin = lower, ymax = upper)) + 
  xlab("Study left out") + 
  ylab("lnTMF, 95% CI") +
  coord_flip() + 
  theme(panel.grid.minor = element_blank()) + theme_bw() + theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor.x = element_blank()) + theme(axis.text.y = element_text(size = 6))

figS19
```


```{r, eval=FALSE}
#Save the plot
ggsave(here("figs/supplements","figS19.png"),
       width = 7,
       height = 10)
```