---
title: "Deduplication"
author: "Lorenzo Ricolfi"
date: "2024-04-08"
output: html_document
---
*Supplementary Material - deduplication code*

## Porpuse: This .Rmd document provides the code we used for deduplication of articles. The file named "articles.csv" contains the output of the searching process of databases. We merged the articles found searching databases using Rayyan.

### Setup and packages loading
```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(synthesisr)
library(tidystringdist)
library(bibliometrix)
```
### Loading file
```{r, include=FALSE}
dat <- read.csv(here("data/deduplication/from_Rayyan_combined.csv"))
dim(dat) #[1] 3744   21
```
### Tidy up and simplify titles removing all punctuation and extra white spaces
```{r, include=FALSE}
dat$title2 <- str_replace_all(dat$title,"[:punct:]","") %>% str_replace_all(.,"[ ]+", " ") %>% tolower()
```
### Remove extra title matches
```{r, include=FALSE}
dat2 <- distinct(dat, title2, .keep_all = TRUE) #select records with unique titles (removes exact duplicates)
dim(dat2) #[1] 2498   22
```
### Removing partial matches in titles
```{r, include=FALSE}
duplicates_string <- find_duplicates(dat2$title2, method = "string_osa", to_lower = TRUE, rm_punctuation = TRUE, threshold = 7)
# Manually review those titles to confirm they are duplicates
manual_checks <- review_duplicates(dat2$title, duplicates_string)
dat3 <- extract_unique_references(dat2, duplicates_string)
dim(dat3) #[1] 2359   23
```
### Drop columns "title2" and "n_duplicates"
```{r, include=FALSE}
dat4 <- select(dat3, -c(title2,n_duplicates))
dim(dat4) #[1] 2359   21
```
### Save as a .bib file to upload on Zotero. Then export from Zotero as .ris file to reimport into Rayyan
```{r, include=FALSE}
write_refs(dat4, format = "bib", file = here("data/deduplication/deduplicated.bib"))
```
