---
title: "split function"
author: "Lorenzo Ricolfi"
date: "2024-04-08"
output: html_document
---

The following code was written by Coralie Williams.

The following code randomly splits reference list for collaborative work between 2 collaborators and set proportions for each split.

Arguments: 
- x: data frame with reference list from Rayyan
- k: number of splits (collaborators in screening)
- p: vector of proportions of split, it must have two positive numerical values that sum to 1. 
- fileName: provided desired suffix of split files
- write: logical argument whether to save the pilot list as csv in current working directory.

#Loading packages
```{r}
library(here)
library(tidyverse)
```

#Writing the function
```{r}
random_split <- function(x, k, p, write=FALSE) {
  
  # check if input is valid
  if (!is.data.frame(x)) stop("x must be a data frame")
  if (k <= 0) stop("k must be a positive number")
  if (k > nrow(x)) stop("k must be a number smaller than the total number of entries in the dataframe")
  if (length(p) != k) stop("p must be a vector of length k")
  if (abs(sum(p) - 1) > 1e-10) stop("p must sum to 1")
  
  # shuffle randomly rows of the input dataframe
  x <- x[sample(nrow(x)), ]
  
  # initialize list where results will be stored
  result <- vector("list", k)
  
  # split the dataframe into k parts according to the proportions in p
  start_index <- 1
  
  for (i in 1:k) {
    
    # compute the number of rows for this split
    n <- round(nrow(x) * p[i])
    
    # extract the rows for this split
    result[[i]] <- x[start_index:(start_index + n - 1), ]
    
    # remove empty rows if paper list is not an even number
    result[[i]] <- result[[i]][!apply(is.na(result[[i]]), 1, all),]
    
    # update the start index for the next split
    start_index <- start_index + n
    
    if (write==T){
      # save as dataframe 
      split <- data.frame(result[[i]])
      # save dataframe in working directory
      write_csv(split, paste("split", i, ".csv", sep=""), na="")
    }
  }
  
  # return the result
  return(result)
  
  # print out message
  cat(paste(c("Reference list was randomly split into", k, "parts")))
  
}
```

#Loading data and applying the function
```{r}
articles <- read_csv(here("data/splitting","deduplicated_R+Rayyan.csv"), skip = 0)

set.seed(123)
# split
rand_split_list <- random_split(articles, 6, p=c(1/6,1/6,1/6,1/6,1/6,1/6))
split1 <- data.frame(rand_split_list[1])
split2 <- data.frame(rand_split_list[2])
split3 <- data.frame(rand_split_list[3])
split4 <- data.frame(rand_split_list[4])
split5 <- data.frame(rand_split_list[5])
split6 <- data.frame(rand_split_list[6])

# save files
write_csv(split1, here("data/splitting/split1.csv", na=""))
write_csv(split2, here("data/splitting/split2.csv", na=""))
write_csv(split3, here("data/splitting/split3.csv", na=""))
write_csv(split4, here("data/splitting/split4.csv", na=""))
write_csv(split5, here("data/splitting/split5.csv", na=""))
write_csv(split6, here("data/splitting/split6.csv", na=""))
```
