---
title: "Slope calculations"
author: "Lorenzo Ricolfi"
output:
  html_document:
    code_folding: show
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    toc_depth: 3
    number_sections: no
    theme: cerulean
  pdf_document:
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
#devtools::install_github("EIvimeyCook/ShinyDigitise")
library(tidyr)
library(dplyr)
library(here)
library(lmtest)
library(data.table)
library(metaDigitise)
library(sandwich)
library(ggplot2)
#library(shinyDigitise)
```

```{=html}
<style>
.warning {
    background-color: #ffdddd; /* Light red background */
    border-left: 6px solid #f44336; /* Red left border */
    padding: 10px;
    margin-bottom: 15px;
}
</style>
```

```{=html}
<style>
.info {
    background-color: #d9edf7; /* Light blue background */
    border-left: 6px solid #31708f; /* Dark blue left border */
    padding: 10px;
    margin-bottom: 15px;
}
</style>
```

```{=html}
<style>
.info2 {
    background-color: #90EE90; /* Light red background */
    border-left: 6px solid #006400; /* Red left border */
    padding: 10px;
    margin-bottom: 15px;
    font-size: 16px;
}
</style>
```

::: info2
Here, we calculate the Trophic magnification factor (TMF) for all those studies that do not report such value and/or its standard error. The TMF is calculated using PFAS concentrations and trophic levels (or stable nitrogen isotope values) data extracted from the included studies.
:::

# Data wrangling

```{r}
# Uploading data
raw_data <- read.csv(here("metaDigitise/Raw_data.csv"))
head(raw_data)
# Reshaping Data with pivot_wider
wide_data <- raw_data %>%
  pivot_wider(
    names_from = variable,
    values_from = c(mean, sd),
    names_glue = "{variable}_{.value}",
    id_cols = c(Study_ID, group_id)
  )
head(wide_data)
```

## S_052: Cara_2022

::: info
-   3 food webs: location 4, 5, and 8.
-   [PFAS] regressed on the original scale. We log-transformed them before running linear models.
-   Standard deviations were log-scaled using the Delta method (Taylor approximation).
-   Data were extracted from plots (Figure 6) using metaDigitise.
:::

```{r}
Cara_2022 <- wide_data %>% 
  filter(Study_ID == "S_052") %>%
  setDT() %>% 
  # melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  # dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE) %>% 
  # mutate(group_id = gsub("^(\\w+\\s[^,]+)", "\\1,", group_id)) %>% 
  separate(group_id, into = c("PFAS", "species", "location"), sep = ",\\s*", extra = "drop")


# Divide the Cara_2022 dataset into locations (food webs).

Cara_2022_loc4 <- Cara_2022 %>% 
  filter(location == "location 4") %>%
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.)))) %>% 
  mutate(log_PFOA_mean = log10(PFOA_mean)) %>%
  mutate(log_PFOA_sd = PFOA_sd/(PFOA_mean*log(10))) %>% #Delta method (Taylor aproximation)
  select_if(~ !all(is.na(.)))

#write.csv(Cara_2022_loc4, file = here("Rdata", "Cara_2022_loc4.csv"))

Cara_2022_loc5 <- Cara_2022 %>% 
  filter(location == "location 5") %>%
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.)))) %>% 
  mutate(log_PFOA_mean = log10(PFOA_mean)) %>%
  mutate(log_PFOA_sd = PFOA_sd/(PFOA_mean*log(10))) %>%
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean)) %>%
  mutate(log_PFUnDA_sd = PFUnDA_sd/(PFUnDA_mean*log(10))) %>%
  select_if(~ !all(is.na(.)))

#write.csv(Cara_2022_loc5, file = here("Rdata", "Cara_2022_loc5.csv"))

Cara_2022_loc8 <- Cara_2022 %>% 
  filter(location == "location 8") %>%
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.)))) %>% 
  mutate(log_PFOA_mean = log10(PFOA_mean)) %>%
  mutate(log_PFOA_sd = PFOA_sd/(PFOA_mean*log(10))) %>%
  mutate(log_PFTrDA_mean = log10(PFTrDA_mean)) %>%
  mutate(log_PFTrDA_sd = PFTrDA_sd/(PFTrDA_mean*log(10))) %>%
  select_if(~ !all(is.na(.)))

#write.csv(Cara_2022_loc8, file = here("Rdata", "Cara_2022_loc8.csv"))
```

## S_013: Martin_2004

::: info
-   3 food webs: benthic, pelagic, and whole food web.
-   Benthic food web only has 2 trophic levels included in the regression. Standard error cannot be calculated.
-   [PFAS] already ln-tranformed.
-   Data were extracted from plots (Figure 3) using metaDigitise.
:::

```{r}
Martin_2004 <- wide_data %>% 
  filter(Study_ID == "S_013") %>%
  select_if(~ !all(is.na(.))) %>% 
  setDT() %>% 
  # melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  # dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE) %>% 
  # mutate(group_id = gsub("^(\\w+\\s[^,]+)", "\\1,", group_id)) %>% 
  separate(group_id, into = c("PFAS", "species", "food_web"), sep = ",\\s*", extra = "drop")

Martin_2004_pelagic <- Martin_2004 %>% 
  filter(food_web == "pelagic food web") %>%
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.))))

#write.csv(Martin_2004_pelagic, file = here("Rdata", "Martin_2004_pelagic.csv"))

Martin_2004_benthic <- Martin_2004 %>% 
  filter(food_web == "benthic food web") %>%
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.))))

#write.csv(Martin_2004_benthic, file = here("Rdata", "Martin_2004_benthic.csv"))

Martin_2004_whole <- Martin_2004 %>%
  filter(food_web == "whole food web") %>%
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.))))

#write.csv(Martin_2004_whole, file = here("Rdata", "Martin_2004_whole.csv"))
```

## S_053: Koch_2020

::: info
-   2 food webs: aquatic and riparian
-   [PFAS] regressed on the original scale, although plots have y-axis on the log scale. We log-transformed them before running linear models.
-   Data were extracted from plots (Figure 4) using Webplot Digitizer.
-   [PFAS] regressed against delta15N.
:::

```{r}
Koch_2020 <- wide_data %>% 
  filter(Study_ID == "S_053") %>%
  select_if(~ !all(is.na(.))) %>% 
  setDT() %>% 
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.)))) %>% 
  # melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  # dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE) %>% 
  # mutate(group_id = gsub("^(\\w+\\s[^,]+)", "\\1,", group_id)) %>% 
  separate(group_id, into = c("PFAS", "species", "food_web"), sep = ",\\s*", extra = "drop") %>% 
  mutate(log_PFOS_mean = log10(PFOS_mean))

#write.csv(Koch_2020, file = here("Rdata", "Koch_2020.csv"))

Koch_2020_aquatic <- Koch_2020 %>% 
  filter(food_web == "aquatic food web") %>%
  select_if(~ !all(is.na(.)))
  
#write.csv(Koch_2020_aquatic, file = here("Rdata", "Koch_2020_aquatic.csv"))

Koch_2020_riparian <- Koch_2020 %>% 
  filter(food_web == "riparian food web") %>%
  select_if(~ !all(is.na(.)))

#write.csv(Koch_2020_riparian, file = here("Rdata", "Koch_2020_riparian.csv"))
```

## S_004: Mazzoni_2020

::: info
-   2 food webs: including and excluding zooplankton.
-   [PFAS] regressed on the original scale. We log-transformed them before running linear models.
-   Data were extracted from tables (Table 1 and Table S5).
:::

```{r}
Mazzoni_2020 <- wide_data %>% 
  filter(Study_ID == "S_004") %>%
  setDT() %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>% 
  # melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  # dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE) %>% 
  separate(group_id, into = c("PFAS", "food_web", "species"), sep = ",\\s*", extra = "drop")

Mazzoni_2020_fw1 <- Mazzoni_2020 %>% 
  filter(food_web == "food web 1") %>%
  mutate(log_PFDA_mean = log10(PFDA_mean)) %>%
  mutate(log_PFDoDA_mean = log10(PFDoDA_mean)) %>%
  mutate(log_PFNA_mean = log10(PFNA_mean)) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>%
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean)) %>%
  select_if(~ !all(is.na(.)))

#write.csv(Mazzoni_2020_fw1, file = here("Rdata", "Mazzoni_2020_fw1.csv"))
  
Mazzoni_2020_fw2 <- Mazzoni_2020 %>% 
  filter(food_web == "food web 2") %>%
  mutate(log_PFDA_mean = log10(PFDA_mean)) %>%
  mutate(log_PFDoDA_mean = log10(PFDoDA_mean)) %>%
  mutate(log_PFNA_mean = log10(PFNA_mean)) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>%
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean)) %>%
  select_if(~ !all(is.na(.)))

#write.csv(Mazzoni_2020_fw2, file = here("Rdata", "Mazzoni_2020_fw2.csv"))
```

## S_017: Liu_2018

::: info
-   1 food web.
-   [PFAS] regressed on the original scale. We ln-transformed them before running linear models.
-   Data were extracted from tables (Table 1) and plots (Figure 4) using Webplot Digitizer.
:::

```{r}
Liu_2018 <- wide_data %>% 
  filter(Study_ID == "S_017") %>%
  setDT() %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>% 
  mutate(ln_PFBA_mean = log(PFBA_mean)) %>%
  mutate(ln_PFOA_mean = log(PFOA_mean)) %>%
  mutate(ln_PFNA_mean = log(PFNA_mean)) %>%
  mutate(ln_PFDA_mean = log(PFDA_mean)) %>%
  mutate(ln_PFUnDA_mean = log(PFUnDA_mean)) %>%
  mutate(ln_PFDoDA_mean = log(PFDoDA_mean)) %>%
  mutate(ln_PFTrDA_mean = log(PFTrDA_mean)) %>%
  mutate(ln_PFOS_mean = log(PFOS_mean)) %>%
  select_if(~ !all(is.na(.)))

#write.csv(Liu_2018, file = here("Rdata", "Liu_2018.csv"))
```

## S_019: Gao_2020

::: info
-   1 food web.
-   [PFAS] already log-tranformed.
-   Data were extracted from plots (Figure 4) using metaDigitise.
:::

```{r}
Gao_2020 <- wide_data %>% 
  filter(Study_ID == "S_019") %>%
  select_if(~ !all(is.na(.))) %>%
  setDT()

#write.csv(Gao_2020, file = here("Rdata", "Gao_2020.csv"))
```

## S_021: Chen_2018

::: info
-   1 food web.
-   [PFAS] already ln-tranformed.
-   Data were extracted from tables (Table 6).
:::

```{r}
Chen_2018 <- wide_data %>% 
  filter(Study_ID == "S_021") %>%
  select_if(~ !all(is.na(.))) %>%
  setDT()

#write.csv(Chen_2018, file = here("Rdata", "Chen_2018.csv"))
```

## S_023: Du_2021

::: info
-   1 food web.
-   [PFAS] already log-tranformed.
-   Data were extracted from plots (Figure 4) using Webplot Digitizer.
:::

```{r}
Du_2021 <- wide_data %>% 
  filter(Study_ID == "S_023") %>%
  select_if(~ !all(is.na(.))) %>%
  setDT()

#write.csv(Du_2021, file = here("Rdata", "Du_2021.csv"))
```

## S_035: Ren_2022

::: info
-   1 food web: Port Austin (USA), food web including benthic organisms.
-   [PFAS] regressed on the original scale. We log-transformed them before running linear models.
-   Data were extracted from tables (Table 1).
:::

```{r}
Ren_2022 <- wide_data %>% 
  filter(Study_ID == "S_035") %>%
  select_if(~ !all(is.na(.))) %>%
  setDT() %>% 
  # melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  # dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE) %>% 
  separate(group_id, into = c("PFAS", "species"), sep = ",\\s*", extra = "drop") %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>%
  mutate(log_PFHxS_mean = log10(PFHxS_mean)) %>%
  mutate(log_PFOA_mean = log10(PFOA_mean)) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>%
  mutate(log_PFNA_mean = log10(PFNA_mean)) %>%
  mutate(log_PFDA_mean = log10(PFDA_mean)) %>%
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean)) %>%
  mutate(log_PFDoDA_mean = log10(PFDoDA_mean)) %>%
  mutate(log_PFTrDA_mean = log10(PFTrDA_mean)) %>%
  mutate(log_PFTeDA_mean = log10(PFTeDA_mean))

#write.csv(Ren_2022, file = here("Rdata", "Ren_2022.csv"))
```

## S_054: Koch_2021

::: info
-   2 food webs: freshwater and terrestrial.
-   [PFAS] already ln-tranformed.
-   [PFAS] regressed against delta15N.
-   Data were extracted from plots (Figure S10) using Webplot Digitizer.
:::

```{r}
Koch_2021 <- wide_data %>% 
  filter(Study_ID == "S_054") %>%
  select_if(~ !all(is.na(.))) %>%
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>% 
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>% 
  separate(group_id, into = c("PFAS", "food_web", "species"), sep = ",\\s*", extra = "drop") 
# food web 1 - freshwater
Koch_2021_freshwater <- Koch_2021 %>% 
  filter(food_web == "food web 1")
#write.csv(Koch_2021_freshwater, file = here("Rdata", "Koch_2021_freshwater.csv"))
# food web 2 - terrestrial
Koch_2021_terrestrial <- Koch_2021 %>% 
  filter(food_web == "food web 2")
#write.csv(Koch_2021_terrestrial, file = here("Rdata", "Koch_2021_terrestrial.csv"))
```

## S_056: Li_2008

::: info
-   2 food webs: Tilapia included and excluded.
-   [PFAS] already ln-tranformed.
-   Data were extracted from plots (Figure 3) using Webplot Digitizer.
:::

```{r}
Li_2008 <- wide_data %>% 
  filter(Study_ID == "S_056") %>%
  select_if(~ !all(is.na(.))) %>%
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>% 
  separate(group_id, into = c("PFAS", "food_web", "species"), sep = ",\\s*", extra = "drop")
# food web 1 - Tilapia excluded
Li_2008_fw1 <- Li_2008 %>% 
  filter(food_web == "food web 1")
#write.csv(Li_2008_fw1, file = here("Rdata", "Li_2008_fw1.csv"))
# food web 2 - Tilapia included
Li_2008_fw2 <- Li_2008 %>% 
  filter(food_web == "food web 2")
#write.csv(Li_2008_fw2, file = here("Rdata", "Li_2008_fw2.csv"))
```

## S_057: Pan_2010

::: info
-   1 food web.
-   [PFAS] regressed on the original scale. We log-transformed them before running linear models.
-   Data were extracted from plots (Figure S1) using Webplot Digitizer.
:::

```{r}
Pan_2010 <- wide_data %>% 
  filter(Study_ID == "S_057") %>%
  select_if(~ !all(is.na(.))) %>%
  mutate(log_PFCs_mean = log10(PFCs_mean)) %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.))))

#write.csv(Pan_2010, file = here("Rdata", "Pan_2010.csv"))
```

## S_058: Van de Vijver_2003

::: info
-   1 food web.
-   [PFAS] regressed on the original scale. We log-transformed them before running linear models.
-   Data were extracted from plots (Figure 3) using Webplot Digitizer.
:::

```{r}
Van_de_Vijver_2003 <- wide_data %>% 
  filter(Study_ID == "S_058") %>%
  select_if(~ !all(is.na(.))) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.))))

#write.csv(Van_de_Vijver_2003, file = here("Rdata", "Van_de_Vijver_2003.csv"))
```

## S_064: Barghi_2018

::: info
-   1 food web.
-   [PFAS] regressed on the original scale. We log-transformed them before running linear models.
-   Data were extracted from plots (Figure S2) using Webplot Digitizer.
:::

```{r}
Barghi_2018 <- wide_data %>% 
  filter(Study_ID == "S_061") %>% 
  setDT() %>%
  select_if(~ !all(is.na(.))) %>%
  mutate(log_PFNA_mean = log10(PFNA_mean)) %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.))))

#write.csv(Barghi_2018, file = here("Rdata", "Barghi_2018.csv"))
```

## S_060: Kobayashi_2018

::: info
-   1 food web.
-   [PFAS] on the original scale. We log-transformed them before running linear models.
-   Data were extracted from tables (Table 1).
-   Standard deviations were log-scaled using the Delta method (Taylor approximation).
:::

```{r}
Kobayashi_2018 <- wide_data %>% 
  filter(Study_ID == "S_060") %>% 
  setDT() %>%
  select_if(~ !all(is.na(.))) %>%
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>% 
  mutate(log_PFHxS_mean = log10(PFHxS_mean)) %>% 
  mutate(log_PFHxS_sd = PFHxS_sd/(PFHxS_mean*log(10))) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>% 
  mutate(log_PFOS_sd = PFOS_sd/(PFOS_mean*log(10))) %>%
  mutate(log_PFPeA_mean = log10(PFPeA_mean)) %>% 
  mutate(log_PFPeA_sd = PFPeA_sd/(PFPeA_mean*log(10))) %>%
  mutate(log_PFHxA_mean = log10(PFHxA_mean)) %>% 
  mutate(log_PFHxA_sd = PFHxA_sd/(PFHxA_mean*log(10))) %>%
  mutate(log_PFHpA_mean = log10(PFHpA_mean)) %>% 
  mutate(log_PFHpA_sd = PFHpA_sd/(PFHpA_mean*log(10))) %>%
  mutate(log_PFOA_mean = log10(PFOA_mean)) %>% 
  mutate(log_PFOA_sd = PFOA_sd/(PFOA_mean*log(10))) %>%
  mutate(log_PFNA_mean = log10(PFNA_mean)) %>% 
  mutate(log_PFNA_sd = PFNA_sd/(PFNA_mean*log(10))) %>%
  mutate(log_PFDA_mean = log10(PFDA_mean)) %>% 
  mutate(log_PFDA_sd = PFDA_sd/(PFDA_mean*log(10))) %>%
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean)) %>% 
  mutate(log_PFUnDA_sd = PFUnDA_sd/(PFUnDA_mean*log(10)))

#write.csv(Kobayashi_2018, file = here("Rdata", "Kobayashi_2018.csv"))
```

## S_047: Heimstad_2024

::: info
-   1 food web.
-   [PFAS] regressed on the original scale, although plots have y-axis on the log scale. We log-transformed them before running linear models.
-   Data extracted from plots (Figure S10 - S12) using Webplot Digitizer.
:::

```{r}
Heimstad_2024 <- wide_data %>% 
  filter(Study_ID == "S_047") %>% 
  setDT() %>%
  select_if(~ !all(is.na(.))) %>% 
  mutate(log_PFDoDA_mean = log10(PFDoDA_mean)) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>% 
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean))

# write.csv(Heimstad_2024, file = here("Rdata", "Heimstad_2024.csv"))
```

## S_024: Li_2021

::: info
- 1 food web.
- [PFAS] already log-tranformed.
- [PFAS] regressed against trophic levels.
- Data were extracted from plots (Figure 4, Figure S7, Figure S8) using Webplot Digitizer.
:::

```{r}
Li_2021 <- wide_data %>% 
  filter(Study_ID == "S_024") %>% 
  setDT() %>%
  select_if(~ !all(is.na(.)))

#write.csv(Li_2021, file = here("Rdata", "Li_2021.csv"))
```

## S_025: Pan_2021

::: info
- 1 food web.
- [PFAS] already log-tranformed.
- [PFAS] regressed against trophic levels.
- Data were extracted from plots (Figure 5) using Webplot Digitizer.
:::

```{r}
Pan_2021 <- wide_data %>% 
  filter(Study_ID == "S_025") %>% 
  setDT() %>%
  select_if(~ !all(is.na(.)))

#write.csv(Pan_2021, file = here("Rdata", "Pan_2021.csv"))
```

## S_059: Jiao_2023

::: info
- 1 food web.
- [PFAS] measured in several tissues.
- [PFAS] already ln-tranformed.
- [PFAS] regressed against trophic levels.
- Data were extracted from plots (Figure 4c) using Webplot Digitizer.
:::

```{r}
Jiao_2023 <- wide_data %>% 
  filter(Study_ID == "S_059") %>% 
  setDT() %>%
  separate(group_id, into = c("PFAS", "tissue", "species"), sep = ",\\s*", extra = "drop") %>% 
  mutate(across(where(is.character), ~na_if(., ""))) %>% 
  select_if(~ !all(is.na(.)))

#write.csv(Jiao_2023, file = here("Rdata", "Jiao_2023.csv"))

# Divide the Jiao_2023 dataset into tissues.

Jiao_2023_blood <- Jiao_2023 %>% 
  filter(tissue == "blood")
#write.csv(Jiao_2023_blood, file = here("Rdata", "Jiao_2023_blood.csv"))
Jiao_2023_gill <- Jiao_2023 %>% 
  filter(tissue == "gill")
#write.csv(Jiao_2023_gill, file = here("Rdata", "Jiao_2023_gill.csv"))
Jiao_2023_heart <- Jiao_2023 %>% 
  filter(tissue == "heart")
#write.csv(Jiao_2023_heart, file = here("Rdata", "Jiao_2023_heart.csv"))
Jiao_2023_liver <- Jiao_2023 %>% 
  filter(tissue == "liver")
#write.csv(Jiao_2023_liver, file = here("Rdata", "Jiao_2023_liver.csv"))
Jiao_2023_kidney <- Jiao_2023 %>% 
  filter(tissue == "kidney")
#write.csv(Jiao_2023_kidney, file = here("Rdata", "Jiao_2023_kidney.csv"))
Jiao_2023_pancreas <- Jiao_2023 %>% 
  filter(tissue == "pancreas")
#write.csv(Jiao_2023_pancreas, file = here("Rdata", "Jiao_2023_pancreas.csv"))
Jiao_2023_muscle <- Jiao_2023 %>% 
  filter(tissue == "muscle")
#write.csv(Jiao_2023_muscle, file = here("Rdata", "Jiao_2023_muscle.csv"))
```

## S_062: Miniero_2014

::: info
- 1 food web.
- [PFOS] provided on the original scale.
- TL values provided.
- Data were extracted from tables (Table 1 and Table SM-1).
:::

```{r}
Miniero_2014 <- wide_data %>% 
  filter(Study_ID == "S_062") %>%
  select_if(~ !all(is.na(.))) %>%
  setDT() %>%
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>% 
  mutate(log_PFOS_mean = log10(PFOS_mean))
  # melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  # dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE) 
  

#write.csv(Miniero_2014, file = here("Rdata", "Miniero_2014.csv"))
```

## S_063: Chen_2023

::: info
- 1 food web.
- [PFAS] provided on the original scale.
- TL values provided.
- Data were extracted from tables (Table 1 and Table S5).
:::

```{r}
Chen_2023 <- wide_data %>% 
  filter(Study_ID == "S_063") %>%
  select_if(~ !all(is.na(.))) %>%
  setDT() %>%
  mutate(log_PFBA_mean = log10(PFBA_mean)) %>%
  mutate(log_PFPeA_mean = log10(PFPeA_mean)) %>% 
  mutate(log_PFHxA_mean = log10(PFHxA_mean)) %>% 
  mutate(log_PFBS_mean = log10(PFBS_mean)) %>%
  mutate(log_PFHpA_mean = log10(PFHpA_mean)) %>%
  mutate(log_PFOA_mean = log10(PFOA_mean)) %>% 
  mutate(log_PF4OPeA_mean = log10(PF4OPeA_mean)) %>% 
  mutate(log_PFNA_mean = log10(PFNA_mean)) %>%
  mutate(log_PFDA_mean = log10(PFDA_mean)) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>% 
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean)) %>%
  mutate(log_62ClPFESA_mean = log10(a62ClPFESA_mean)) %>% 
  mutate(log_PFDoDA_mean = log10(PFDoDA_mean)) %>% 
  mutate(log_PFTrDA_mean = log10(PFTrDA_mean)) %>%
  mutate(log_PFTeDA_mean = log10(PFTeDA_mean)) %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>% 
  melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE)

#write.csv(Chen_2023, file = here("Rdata", "Chen_2023.csv"))
```
## S_065: Yordy_2013

::: info
- 1 food web.
- [PFCs] provided on the original scale.
- [PFCs] regressed against stable nitrogen isotopes.
- Data were extracted from Table 1.
:::

```{r}
Yordy_2013 <- wide_data %>% 
  filter(Study_ID == "S_064") %>%
  select_if(~ !all(is.na(.))) %>%
  setDT() %>% 
  mutate(across(ends_with("mean"), ~ as.numeric(as.character(.)))) %>%
  mutate(log_PFCs_mean = log10(PFCs_mean)) %>% 
  melt(id.vars = c("group_id"), na.rm = TRUE) %>% 
  dcast(group_id ~ variable, value.var = "value", fun.aggregate = max, na.rm = TRUE)

write.csv(Yordy_2013, file = here("Rdata", "Yordy_2013.csv"))
```

## S_066: Mo_2024

::: info
- 1 food web.
- [PFAS] provided on the original scale.
- [PFAS] regressed against stable nitrogen isotopes.
- Data were extracted from Table 1.
:::

```{r}
Mo_2024 <- wide_data %>% 
  setDT() %>% 
  filter(Study_ID == "S_065") %>%
  select_if(~ !all(is.na(.))) %>%
  mutate(across(ends_with("mean") | ends_with("sd"), ~ as.numeric(as.character(.)))) %>%
  mutate(log_PFBA_mean = log10(PFBA_mean)) %>% 
  mutate(log_PFHxA_mean = log10(PFHxA_mean)) %>%
  mutate(log_PFHpA_mean = log10(PFHpA_mean)) %>%
  mutate(log_PFOA_mean = log10(PFOA_mean)) %>%
  mutate(log_PFNA_mean = log10(PFNA_mean)) %>%
  mutate(log_PFDA_mean = log10(PFDA_mean)) %>%
  mutate(log_PFUnDA_mean = log10(PFUnDA_mean)) %>%
  mutate(log_PFDoDA_mean = log10(PFDoDA_mean)) %>%
  mutate(log_PFTrDA_mean = log10(PFTrDA_mean)) %>%
  mutate(log_PFTeDA_mean = log10(PFTeDA_mean)) %>%
  mutate(log_PFBS_mean = log10(PFBS_mean)) %>%
  mutate(log_PFHxS_mean = log10(PFHxS_mean)) %>%
  mutate(log_PFHpS_mean = log10(PFHpS_mean)) %>%
  mutate(log_PFOS_mean = log10(PFOS_mean)) %>%
  mutate(log_HFPO_DA_mean = log10(HFPO_DA_mean)) %>%
  mutate(log_HFPO_TrA_mean = log10(HFPO_TrA_mean)) %>%
  mutate(log_62ClPFESA_mean = log10(a62ClPFESA_mean)) %>%
  mutate(log_82ClPFESA_mean = log10(a82ClPFESA_mean)) %>%
  mutate(log_OBS_mean = log10(OBS_mean)) %>%
  mutate(log_FOSA_mean = log10(FOSA_mean))

#write.csv(Mo_2024, file = here("Rdata", "Mo_2024.csv"))
```

# Linear models

## S_052: Cara_2022

::: info
-   It provides standard deviations of individual observations. Weights were assigned (inverse of square standard deviation).
:::

### First food web - "location 4"

```{r}
Cara_2022_loc4 <- read.csv(here("RData", "Cara_2022_loc4.csv"))

Cara_2022_loc4_PFOA_weights <- 1 / (Cara_2022_loc4$log_PFOA_sd^2) # weights as the inverse of square standard deviation. Please note we are taking the assumption that n is exactly the same for each observation. This is an assumption that must be taken in order to use the standard deviation of observations as weights.

Cara_2022_loc4_lm_model_PFOA <- lm(log_PFOA_mean ~ TL_mean, 
                                   data = Cara_2022_loc4,
                                   weights = Cara_2022_loc4_PFOA_weights)

Cara_2022_loc4_PFOA_slope <- coef(Cara_2022_loc4_lm_model_PFOA)["TL_mean"]
#plot(residuals(Cara_2022_loc4_lm_model_PFOA))
#coeftest(Cara_2022_loc4_lm_model_PFOA, vcov. = vcovHC)
# or
summary(Cara_2022_loc4_lm_model_PFOA)
```

```{r}
ggplot(Cara_2022_loc4, aes(x = TL_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Cara_2022_loc4_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Second food web - "location 5"

```{r}
Cara_2022_loc5 <- read.csv(here("RData", "Cara_2022_loc5.csv"))

Cara_2022_loc5_PFOA_weights <- 1 / (Cara_2022_loc5$log_PFOA_sd^2)
Cara_2022_loc5_PFUnDA_weights <- 1 / (Cara_2022_loc5$log_PFUnDA_sd^2)

Cara_2022_loc5_lm_model_PFOA <- lm(log_PFOA_mean ~ TL_mean, 
                                   data = Cara_2022_loc5,
                                   weights = Cara_2022_loc5_PFOA_weights)

Cara_2022_loc5_PFOA_slope <- coef(Cara_2022_loc5_lm_model_PFOA)["TL_mean"]

summary(Cara_2022_loc5_lm_model_PFOA)
```

```{r}
ggplot(Cara_2022_loc5, aes(x = TL_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Cara_2022_loc5_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Cara_2022_loc5_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean, 
                                     data = Cara_2022_loc5, 
                                     weights = Cara_2022_loc5_PFUnDA_weights)

Cara_2022_loc5_PFUnDA_slope <- coef(Cara_2022_loc5_lm_model_PFUnDA)["TL_mean"]

summary(Cara_2022_loc5_lm_model_PFUnDA)
```

```{r}
ggplot(Cara_2022_loc5, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Cara_2022_loc5_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Third food web - "location 8"

```{r}
Cara_2022_loc8 <- read.csv(here("RData", "Cara_2022_loc8.csv"))

Cara_2022_loc8_PFOA_weights <- 1 / (Cara_2022_loc8$log_PFOA_sd^2)
Cara_2022_loc8_PFTrDA_weights <- 1 / (Cara_2022_loc8$log_PFTrDA_sd^2)

Cara_2022_loc8_lm_model_PFOA <- lm(log_PFOA_mean ~ TL_mean, 
                                   data = Cara_2022_loc8,
                                   weights = Cara_2022_loc8_PFOA_weights)

Cara_2022_loc8_PFOA_slope <- coef(Cara_2022_loc8_lm_model_PFOA)["TL_mean"]

summary(Cara_2022_loc8_lm_model_PFOA)
```

```{r}
ggplot(Cara_2022_loc8, aes(x = TL_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Cara_2022_loc8_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Cara_2022_loc8_lm_model_PFTrDA <- lm(log_PFTrDA_mean ~ TL_mean, 
                                     data = Cara_2022_loc8, 
                                     weights = Cara_2022_loc8_PFTrDA_weights)

Cara_2022_loc8_PFTrDA_slope <- coef(Cara_2022_loc8_lm_model_PFTrDA)["TL_mean"]

summary(Cara_2022_loc8_lm_model_PFTrDA)
```

```{r}
ggplot(Cara_2022_loc8, aes(x = TL_mean, y = log_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Cara_2022_loc8_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_013: Martin_2004

::: info
-   It provides standard errors of individual observations. Weights were assigned (inverse of standard error).
:::

### Benthic food web

::: warning
WARNING! Benthic food web includes only two trophic levels! It cannot be considered a food web.
:::

SE values for benthic food web slope cannot be calculated.

```{r}
Martin_2004_benthic <- read.csv(here("RData/Martin_2004_benthic.csv"))

Martin_2004_benthic_PFOS_weights <- 1 / Martin_2004_benthic$se^2 # weights as the inverse of standard error

# PFOS
Martin_2004_benthic_lm_model_PFOS <- lm(ln_PFOS_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFOS_slope <- coef(Martin_2004_benthic_lm_model_PFOS)["TL_mean"]

#plot(residuals(Martin_2004_benthic_lm_model_PFOS))

summary(Martin_2004_benthic_lm_model_PFOS)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Martin_2004_benthic_lm_model_PFOA <- lm(ln_PFOA_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFOA_slope <- coef(Martin_2004_benthic_lm_model_PFOA)["TL_mean"]

summary(Martin_2004_benthic_lm_model_PFOA)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Martin_2004_benthic_lm_model_PFNA <- lm(ln_PFNA_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFNA_slope <- coef(Martin_2004_benthic_lm_model_PFNA)["TL_mean"]

summary(Martin_2004_benthic_lm_model_PFNA)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Martin_2004_benthic_lm_model_PFDA <- lm(ln_PFDA_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFDA_slope <- coef(Martin_2004_benthic_lm_model_PFDA)["TL_mean"]

summary(Martin_2004_benthic_lm_model_PFDA)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Martin_2004_benthic_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFUnDA_slope <- coef(Martin_2004_benthic_lm_model_PFUnDA)["TL_mean"]

summary(Martin_2004_benthic_lm_model_PFUnDA)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Martin_2004_benthic_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFDoDA_slope <- coef(Martin_2004_benthic_lm_model_PFDoDA)["TL_mean"]

summary(Martin_2004_benthic_lm_model_PFDoDA)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Martin_2004_benthic_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFTrDA_slope <- coef(Martin_2004_benthic_lm_model_PFTrDA)["TL_mean"]

summary(Martin_2004_benthic_lm_model_PFTrDA)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTeDA
Martin_2004_benthic_lm_model_PFTeDA <- lm(ln_PFTeDA_mean ~ TL_mean, 
                                        data = Martin_2004_benthic,
                                        weights = Martin_2004_benthic_PFOS_weights)

Martin_2004_benthic_PFTeDA_slope <- coef(Martin_2004_benthic_lm_model_PFTeDA)["TL_mean"]

summary(Martin_2004_benthic_lm_model_PFTeDA)
```

```{r}
ggplot(Martin_2004_benthic, aes(x = TL_mean, y = ln_PFTeDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFTeDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_benthic_PFTeDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Pelagic food web

```{r}
Martin_2004_pelagic <- read.csv(here("RData", "Martin_2004_pelagic.csv"))

Martin_2004_pelagic_weights <- Martin_2004_pelagic$se^2

# PFOS
Martin_2004_pelagic_lm_model_PFOS <- lm(ln_PFOS_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic,
                                        weights = Martin_2004_pelagic_weights)

Martin_2004_pelagic_PFOS_slope <- coef(Martin_2004_pelagic_lm_model_PFOS)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFOS)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Martin_2004_pelagic_lm_model_PFOA <- lm(ln_PFOA_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic,
                                        weights = Martin_2004_pelagic_weights)

Martin_2004_pelagic_PFOA_slope <- coef(Martin_2004_pelagic_lm_model_PFOA)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFOA)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Martin_2004_pelagic_lm_model_PFNA <- lm(ln_PFNA_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic,
                                        weights = Martin_2004_pelagic_weights)

Martin_2004_pelagic_PFNA_slope <- coef(Martin_2004_pelagic_lm_model_PFNA)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFNA)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Martin_2004_pelagic_lm_model_PFDA <- lm(ln_PFDA_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic,
                                        weights = Martin_2004_pelagic_weights)

Martin_2004_pelagic_PFDA_slope <- coef(Martin_2004_pelagic_lm_model_PFDA)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFDA)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Martin_2004_pelagic_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic,
                                        weights = Martin_2004_pelagic_weights)

Martin_2004_pelagic_PFUnDA_slope <- coef(Martin_2004_pelagic_lm_model_PFUnDA)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFUnDA)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Martin_2004_pelagic_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic,
                                        weights = Martin_2004_pelagic_weights)

Martin_2004_pelagic_PFDoDA_slope <- coef(Martin_2004_pelagic_lm_model_PFDoDA)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFDoDA)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Martin_2004_pelagic_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic,
                                        weights = Martin_2004_pelagic_weights)

Martin_2004_pelagic_PFTrDA_slope <- coef(Martin_2004_pelagic_lm_model_PFTrDA)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFTrDA)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTeDA
Martin_2004_pelagic_lm_model_PFTeDA <- lm(ln_PFTeDA_mean ~ TL_mean, 
                                        data = Martin_2004_pelagic)

Martin_2004_pelagic_PFTeDA_slope <- coef(Martin_2004_pelagic_lm_model_PFTeDA)["TL_mean"]

summary(Martin_2004_pelagic_lm_model_PFTeDA)
```

```{r}
ggplot(Martin_2004_pelagic, aes(x = TL_mean, y = ln_PFTeDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFTeDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_pelagic_PFTeDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Whole food web

```{r}
Martin_2004_whole <- read.csv(here("RData", "Martin_2004_whole.csv"))

Martin_2004_whole_FOSA_weights <- 1 / Martin_2004_whole$se^2

Martin_2004_whole_lm_model_FOSA <- lm(ln_FOSA_mean ~ TL_mean, 
                                        data = Martin_2004_whole,
                                        weights = Martin_2004_whole_FOSA_weights)

Martin_2004_whole_FOSA_slope <- coef(Martin_2004_whole_lm_model_FOSA)["TL_mean"]

summary(Martin_2004_whole_lm_model_FOSA)
```

```{r}
ggplot(Martin_2004_whole, aes(x = TL_mean, y = ln_FOSA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [FOSA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Martin_2004_whole_FOSA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_053: Koch_2020

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

### Aquatic food web

```{r}
Koch_2020_aquatic <- read.csv(here("Rdata", "Koch_2020_aquatic.csv"))

Koch_2020_aquatic_lm_model_PFOS <- lm(log_PFOS_mean ~ delta_15N_mean,
                                      data = Koch_2020_aquatic)

Koch_2020_aquatic_PFOS_slope <- coef(Koch_2020_aquatic_lm_model_PFOS)["delta_15N_mean"]

summary(Koch_2020_aquatic_lm_model_PFOS)
```

```{r}
ggplot(Koch_2020_aquatic, aes(x = delta_15N_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Koch_2020_aquatic_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Riparian food web

```{r}
Koch_2020_riparian <- read.csv(here("Rdata", "Koch_2020_riparian.csv"))

Koch_2020_riparian_lm_model_PFOS <- lm(log_PFOS_mean ~ delta_15N_mean,
                                      data = Koch_2020_riparian)

Koch_2020_riparian_PFOS_slope <- coef(Koch_2020_riparian_lm_model_PFOS)["delta_15N_mean"]

summary(Koch_2020_riparian_lm_model_PFOS)
```

```{r}
ggplot(Koch_2020_riparian, aes(x = delta_15N_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Koch_2020_riparian_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_004: Mazzoni_2020

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

### Food web 1 - including zooplankton

```{r}
Mazzoni_2020_fw1 <- read.csv(here("Rdata", "Mazzoni_2020_fw1.csv"))

# PFDA
Mazzoni_2020_fw1_lm_model_PFDA <- lm(log_PFDA_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw1)

Mazzoni_2020_fw1_PFDA_slope <- coef(Mazzoni_2020_fw1_lm_model_PFDA)["TL_mean"]

summary(Mazzoni_2020_fw1_lm_model_PFDA)
```

```{r}
ggplot(Mazzoni_2020_fw1, aes(x = TL_mean, y = log_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw1_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Mazzoni_2020_fw1_lm_model_PFDoDA <- lm(log_PFDoDA_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw1)

Mazzoni_2020_fw1_PFDoDA_slope <- coef(Mazzoni_2020_fw1_lm_model_PFDoDA)["TL_mean"]

summary(Mazzoni_2020_fw1_lm_model_PFDoDA)
```

```{r}
ggplot(Mazzoni_2020_fw1, aes(x = TL_mean, y = log_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw1_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Mazzoni_2020_fw1_lm_model_PFNA <- lm(log_PFNA_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw1)

Mazzoni_2020_fw1_PFNA_slope <- coef(Mazzoni_2020_fw1_lm_model_PFNA)["TL_mean"]

summary(Mazzoni_2020_fw1_lm_model_PFNA)
```

```{r}
ggplot(Mazzoni_2020_fw1, aes(x = TL_mean, y = log_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw1_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS - Note: The study already provides the TMS and SE for this compound
Mazzoni_2020_fw1_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean, data = Mazzoni_2020_fw1)

Mazzoni_2020_fw1_PFOS_slope <- coef(Mazzoni_2020_fw1_lm_model_PFOS)["TL_mean"]

summary(Mazzoni_2020_fw1_lm_model_PFOS)
```

```{r}
ggplot(Mazzoni_2020_fw1, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw1_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Mazzoni_2020_fw1_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw1)

Mazzoni_2020_fw1_PFUnDA_slope <- coef(Mazzoni_2020_fw1_lm_model_PFUnDA)["TL_mean"]

summary(Mazzoni_2020_fw1_lm_model_PFUnDA)
```

```{r}
ggplot(Mazzoni_2020_fw1, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw1_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Food web 2 - excluding zooplankton

```{r}
Mazzoni_2020_fw2 <- read.csv(here("Rdata", "Mazzoni_2020_fw2.csv"))

# PFDA
Mazzoni_2020_fw2_lm_model_PFDA <- lm(log_PFDA_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw2)

Mazzoni_2020_fw2_PFDA_slope <- coef(Mazzoni_2020_fw2_lm_model_PFDA)["TL_mean"]

summary(Mazzoni_2020_fw2_lm_model_PFDA)
```

```{r}
ggplot(Mazzoni_2020_fw2, aes(x = TL_mean, y = log_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw2_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Mazzoni_2020_fw2_lm_model_PFDoDA <- lm(log_PFDoDA_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw2)

Mazzoni_2020_fw2_PFDoDA_slope <- coef(Mazzoni_2020_fw2_lm_model_PFDoDA)["TL_mean"]

summary(Mazzoni_2020_fw2_lm_model_PFDoDA)
```

```{r}
ggplot(Mazzoni_2020_fw2, aes(x = TL_mean, y = log_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw2_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Mazzoni_2020_fw2_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw2)

Mazzoni_2020_fw2_PFOS_slope <- coef(Mazzoni_2020_fw2_lm_model_PFOS)["TL_mean"]

summary(Mazzoni_2020_fw2_lm_model_PFOS)
```

```{r}
ggplot(Mazzoni_2020_fw2, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw2_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Mazzoni_2020_fw2_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean,
                                      data = Mazzoni_2020_fw2)

Mazzoni_2020_fw2_PFUnDA_slope <- coef(Mazzoni_2020_fw2_lm_model_PFUnDA)["TL_mean"]

summary(Mazzoni_2020_fw2_lm_model_PFUnDA)
```

```{r}
ggplot(Mazzoni_2020_fw2, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mazzoni_2020_fw2_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_017: Liu_2018

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Liu_2018 <- read.csv(here("Rdata", "Liu_2018.csv"))
# PFBA
Liu_2018_lm_model_PFBA <- lm(ln_PFBA_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFBA_slope <- coef(Liu_2018_lm_model_PFBA)["TL_mean"]

summary(Liu_2018_lm_model_PFBA)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFBA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFBA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFBA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Liu_2018_lm_model_PFOA <- lm(ln_PFOA_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFOA_slope <- coef(Liu_2018_lm_model_PFOA)["TL_mean"]


summary(Liu_2018_lm_model_PFOA)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Liu_2018_lm_model_PFNA <- lm(ln_PFNA_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFNA_slope <- coef(Liu_2018_lm_model_PFNA)["TL_mean"]

summary(Liu_2018_lm_model_PFNA)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Liu_2018_lm_model_PFDA <- lm(ln_PFDA_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFDA_slope <- coef(Liu_2018_lm_model_PFDA)["TL_mean"]

summary(Liu_2018_lm_model_PFDA)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Liu_2018_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFUnDA_slope <- coef(Liu_2018_lm_model_PFUnDA)["TL_mean"]

summary(Liu_2018_lm_model_PFUnDA)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Liu_2018_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFDoDA_slope <- coef(Liu_2018_lm_model_PFDoDA)["TL_mean"]

summary(Liu_2018_lm_model_PFDoDA)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA 
Liu_2018_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFTrDA_slope <- coef(Liu_2018_lm_model_PFTrDA)["TL_mean"]

summary(Liu_2018_lm_model_PFTrDA)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Liu_2018_lm_model_PFOS <- lm(ln_PFOS_mean ~ TL_mean,
                             data = Liu_2018)

Liu_2018_PFOS_slope <- coef(Liu_2018_lm_model_PFOS)["TL_mean"]

summary(Liu_2018_lm_model_PFOS)
```

```{r}
ggplot(Liu_2018, aes(x = TL_mean, y = ln_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Liu_2018_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_019: Gao_2020

::: info
-   It provides standard deviations of individual observations. Weights were assigned (inverse of square standard deviation).
:::

```{r}
Gao_2020 <- read.csv(here("Rdata", "Gao_2020.csv"))
Gao_2020_PFHxS_weights <- 1 / (Gao_2020$log_PFHxS_sd^2)
Gao_2020_PFOS_weights <- 1 / (Gao_2020$log_PFOS_sd^2)
Gao_2020_PFBA_weights <- 1 / (Gao_2020$log_PFBA_sd^2)

# PFHxS
Gao_2020_lm_model_PFHxS <- lm(log_PFHxS_mean ~ TL_mean,
                              data = Gao_2020,
                              weights = Gao_2020_PFHxS_weights)

Gao_2020_PFHxS_slope <- coef(Gao_2020_lm_model_PFHxS)["TL_mean"]

summary(Gao_2020_lm_model_PFHxS)
```

```{r}
ggplot(Gao_2020, aes(x = TL_mean, y = log_PFHxS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFHxS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Gao_2020_PFHxS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Gao_2020_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                             data = Gao_2020,
                             weights = Gao_2020_PFOS_weights)

Gao_2020_PFOS_slope <- coef(Gao_2020_lm_model_PFOS)["TL_mean"]

summary(Gao_2020_lm_model_PFOS)
```

```{r}
ggplot(Gao_2020, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Gao_2020_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFBA
Gao_2020_lm_model_PFBA <- lm(log_PFBA_mean ~ TL_mean,
                             data = Gao_2020,
                             weights = Gao_2020_PFBA_weights)

Gao_2020_PFBA_slope <- coef(Gao_2020_lm_model_PFBA)["TL_mean"]

summary(Gao_2020_lm_model_PFBA)
```

```{r}
ggplot(Gao_2020, aes(x = TL_mean, y = log_PFBA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFBA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Gao_2020_PFBA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_021: Chen_2018

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Chen_2018 <- read.csv(here("Rdata", "Chen_2018.csv"))

# PFOS
Chen_2018_lm_model_PFOS <- lm(ln_PFOS_mean ~ TL_mean,
                             data = Chen_2018)

Chen_2018_PFOS_slope <- coef(Chen_2018_lm_model_PFOS)["TL_mean"]

summary(Chen_2018_lm_model_PFOS)
```

```{r}
ggplot(Chen_2018, aes(x = TL_mean, y = ln_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2018_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Chen_2018_lm_model_PFDA <- lm(ln_PFDA_mean ~ TL_mean,
                             data = Chen_2018)

Chen_2018_PFDA_slope <- coef(Chen_2018_lm_model_PFDA)["TL_mean"]

summary(Chen_2018_lm_model_PFDA)
```

```{r}
ggplot(Chen_2018, aes(x = TL_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2018_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Chen_2018_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ TL_mean,
                             data = Chen_2018)

Chen_2018_PFUnDA_slope <- coef(Chen_2018_lm_model_PFUnDA)["TL_mean"]

summary(Chen_2018_lm_model_PFUnDA)
```

```{r}
ggplot(Chen_2018, aes(x = TL_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2018_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Chen_2018_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ TL_mean,
                             data = Chen_2018)

Chen_2018_PFDoDA_slope <- coef(Chen_2018_lm_model_PFDoDA)["TL_mean"]

summary(Chen_2018_lm_model_PFDoDA)
```

```{r}
ggplot(Chen_2018, aes(x = TL_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2018_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_023: Du_2021

::: info
-   .
:::

```{r}
Du_2021 <- read.csv(here("Rdata", "Du_2021.csv"))

# PFBA
Du_2021_lm_model_PFBA <- lm(log_PFBA_mean ~ TL_mean,
                             data = Du_2021)

Du_2021_PFBA_slope <- coef(Du_2021_lm_model_PFBA)["TL_mean"]

summary(Du_2021_lm_model_PFBA)
```

```{r}
ggplot(Du_2021, aes(x = TL_mean, y = log_PFBA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFBA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Du_2021_PFBA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHxA
Du_2021_lm_model_PFHxA <- lm(log_PFHxA_mean ~ TL_mean,
                             data = Du_2021)

Du_2021_PFHxA_slope <- coef(Du_2021_lm_model_PFHxA)["TL_mean"]

summary(Du_2021_lm_model_PFHxA)
```

```{r}
ggplot(Du_2021, aes(x = TL_mean, y = log_PFHxA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFHxA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Du_2021_PFHxA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Du_2021_lm_model_PFOA <- lm(log_PFOA_mean ~ TL_mean,
                             data = Du_2021)

Du_2021_PFOA_slope <- coef(Du_2021_lm_model_PFOA)["TL_mean"]

summary(Du_2021_lm_model_PFOA)
```

```{r}
ggplot(Du_2021, aes(x = TL_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Du_2021_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Du_2021_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean,
                             data = Du_2021)

Du_2021_PFUnDA_slope <- coef(Du_2021_lm_model_PFUnDA)["TL_mean"]

summary(Du_2021_lm_model_PFUnDA)
```

```{r}
ggplot(Du_2021, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Du_2021_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Du_2021_lm_model_PFTrDA <- lm(log_PFTrDA_mean ~ TL_mean,
                             data = Du_2021)

Du_2021_PFTrDA_slope <- coef(Du_2021_lm_model_PFTrDA)["TL_mean"]

summary(Du_2021_lm_model_PFTrDA)
```

```{r}
ggplot(Du_2021, aes(x = TL_mean, y = log_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Du_2021_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFBS
Du_2021_lm_model_PFBS <- lm(log_PFBS_mean ~ TL_mean,
                             data = Du_2021)

Du_2021_PFBS_slope <- coef(Du_2021_lm_model_PFBS)["TL_mean"]

summary(Du_2021_lm_model_PFBS)
```

```{r}
ggplot(Du_2021, aes(x = TL_mean, y = log_PFBS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFBS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Du_2021_PFBS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Du_2021_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                             data = Du_2021)

Du_2021_PFOS_slope <- coef(Du_2021_lm_model_PFOS)["TL_mean"]

summary(Du_2021_lm_model_PFOS)
```

```{r}
ggplot(Du_2021, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Du_2021_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_035: Ren_2022

::: info
-   It provides standard errors of individual observations. Weights were assigned (inverse of standard error).
:::

```{r}
Ren_2022 <- read.csv(here("Rdata", "Ren_2022.csv"))

Ren_2022_weights <- 1 / Ren_2022$se^2

# PFHxS
Ren_2022_lm_model_PFHxS <- lm(log_PFHxS_mean ~ TL_mean,
                              data = Ren_2022,
                              weights = Ren_2022_weights)

Ren_2022_PFHxS_slope <- coef(Ren_2022_lm_model_PFHxS)["TL_mean"]

summary(Ren_2022_lm_model_PFHxS)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFHxS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFHxS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFHxS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS - we cannot assign weights because SE = 0
Ren_2022_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFOS_slope <- coef(Ren_2022_lm_model_PFOS)["TL_mean"]

summary(Ren_2022_lm_model_PFOS)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Ren_2022_lm_model_PFOA <- lm(log_PFOA_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFOA_slope <- coef(Ren_2022_lm_model_PFOA)["TL_mean"]

summary(Ren_2022_lm_model_PFOA)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Ren_2022_lm_model_PFNA <- lm(log_PFNA_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFNA_slope <- coef(Ren_2022_lm_model_PFNA)["TL_mean"]

summary(Ren_2022_lm_model_PFNA)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Ren_2022_lm_model_PFDA <- lm(log_PFDA_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFDA_slope <- coef(Ren_2022_lm_model_PFDA)["TL_mean"]

summary(Ren_2022_lm_model_PFDA)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Ren_2022_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFUnDA_slope <- coef(Ren_2022_lm_model_PFUnDA)["TL_mean"]

summary(Ren_2022_lm_model_PFUnDA)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Ren_2022_lm_model_PFDoDA <- lm(log_PFDoDA_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFDoDA_slope <- coef(Ren_2022_lm_model_PFDoDA)["TL_mean"]

summary(Ren_2022_lm_model_PFDoDA)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Ren_2022_lm_model_PFTrDA <- lm(log_PFTrDA_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFTrDA_slope <- coef(Ren_2022_lm_model_PFTrDA)["TL_mean"]

summary(Ren_2022_lm_model_PFTrDA)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTeDA
Ren_2022_lm_model_PFTeDA <- lm(log_PFTeDA_mean ~ TL_mean,
                              data = Ren_2022)

Ren_2022_PFTeDA_slope <- coef(Ren_2022_lm_model_PFTeDA)["TL_mean"]

summary(Ren_2022_lm_model_PFTeDA)
```

```{r}
ggplot(Ren_2022, aes(x = TL_mean, y = log_PFTeDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFTeDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Ren_2022_PFTeDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_054: Koch_2021

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

### Food web 1 - freshwater

```{r}
Koch_2021_freshwater <- read.csv(here("Rdata", "Koch_2021_freshwater.csv"))
Koch_2021_freshwater_lm_model_PFOS <- lm(log_PFOS_mean ~ delta_15N_mean,
                                         data = Koch_2021_freshwater)

Koch_2021_freshwater_PFOS_slope <- coef(Koch_2021_freshwater_lm_model_PFOS)["delta_15N_mean"]

summary(Koch_2021_freshwater_lm_model_PFOS)
```

```{r}
ggplot(Koch_2021_freshwater, aes(x = delta_15N_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Koch_2021_freshwater_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Food web 2 - terrestrial

```{r}
Koch_2021_terrestrial <- read.csv(here("Rdata", "Koch_2021_terrestrial.csv"))

Koch_2021_terrestrial_lm_model_PFOS <- lm(log_PFOS_mean ~ delta_15N_mean,
                                         data = Koch_2021_terrestrial)

Koch_2021_terrestrial_PFOS_slope <- coef(Koch_2021_terrestrial_lm_model_PFOS)["delta_15N_mean"]

summary(Koch_2021_terrestrial_lm_model_PFOS)
```

```{r}
ggplot(Koch_2021_terrestrial, aes(x = delta_15N_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Koch_2021_terrestrial_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_056: Li_2008

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

### Food web 1 - Tilapia excluded

```{r}
Li_2008_fw1 <- read.csv(here("Rdata", "Li_2008_fw1.csv"))
Li_2008_fw1_lm_model_PFOS <- lm(ln_PFOS_mean ~ TL_mean,
                                data = Li_2008_fw1)

Li_2008_fw1_PFOS_slope <- coef(Li_2008_fw1_lm_model_PFOS)["TL_mean"]

summary(Li_2008_fw1_lm_model_PFOS)
```

```{r}
ggplot(Li_2008_fw1, aes(x = TL_mean, y = ln_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2008_fw1_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

### Food web 2 - Tilapia included

```{r}
Li_2008_fw2 <- read.csv(here("Rdata", "Li_2008_fw2.csv"))
Li_2008_fw2_lm_model_PFOS <- lm(ln_PFOS_mean ~ TL_mean,
                                data = Li_2008_fw2)

Li_2008_fw2_PFOS_slope <- coef(Li_2008_fw2_lm_model_PFOS)["TL_mean"]

summary(Li_2008_fw2_lm_model_PFOS)
```

```{r}
ggplot(Li_2008_fw2, aes(x = TL_mean, y = ln_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2008_fw2_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_057: Pan_2010

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Pan_2010 <- read.csv(here("Rdata", "Pan_2010.csv"))
Pan_2010_lm_model_PFOS <- lm(log_PFCs_mean ~ TL_mean,
                                data = Pan_2010)

Pan_2010_PFOS_slope <- coef(Pan_2010_lm_model_PFOS)["TL_mean"]

summary(Pan_2010_lm_model_PFOS)
```

```{r}
ggplot(Pan_2010, aes(x = TL_mean, y = log_PFCs_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Pan_2010_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_058: Van de Vijver_2003

::: info
-   .
:::

```{r}
Van_de_Vijver_2003 <- read.csv(here("Rdata", "Van_de_Vijver_2003.csv"))
Van_de_Vijver_2003_lm_model_PFOS <- lm(log_PFOS_mean ~ delta_15N_mean,
                                       data = Van_de_Vijver_2003)

Van_de_Vijver_2003_PFOS_slope <- coef(Van_de_Vijver_2003_lm_model_PFOS)["delta_15N_mean"]

summary(Van_de_Vijver_2003_lm_model_PFOS)
```

```{r}
ggplot(Van_de_Vijver_2003, aes(x = delta_15N_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Van_de_Vijver_2003_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_064: Barghi_2018

::: info
-   .
:::

```{r}
Barghi_2018 <- read.csv(here("Rdata", "Barghi_2018.csv"))

Barghi_2018_lm_model_PFNA <- lm(log_PFNA_mean ~ delta_15N_mean,
                                       data = Barghi_2018)

Barghi_2018_PFNA_slope <- coef(Barghi_2018_lm_model_PFNA)["delta_15N_mean"]

summary(Barghi_2018_lm_model_PFNA)
```

```{r}
ggplot(Barghi_2018, aes(x = delta_15N_mean, y = log_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Barghi_2018_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_060: Kobayashi_2018

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Kobayashi_2018 <- read.csv(here("Rdata", "Kobayashi_2018.csv"))

# PFHxS
Kobayashi_2018_lm_model_PFHxS <- lm(log_PFHxS_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFHxS_slope <- coef(Kobayashi_2018_lm_model_PFHxS)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFHxS)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFHxS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFHxS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFHxS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Kobayashi_2018_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFOS_slope <- coef(Kobayashi_2018_lm_model_PFOS)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFOS)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFPeA
Kobayashi_2018_lm_model_PFPeA <- lm(log_PFPeA_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFPeA_slope <- coef(Kobayashi_2018_lm_model_PFPeA)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFPeA)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFPeA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFPeA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFPeA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHxA
Kobayashi_2018_lm_model_PFHxA <- lm(log_PFHxA_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFHxA_slope <- coef(Kobayashi_2018_lm_model_PFHxA)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFHxA)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFHxA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFHxA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFHxA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHpA
Kobayashi_2018_lm_model_PFHpA <- lm(log_PFHpA_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFHpA_slope <- coef(Kobayashi_2018_lm_model_PFHpA)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFHpA)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFHpA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFHpA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFHpA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Kobayashi_2018_lm_model_PFOA <- lm(log_PFOA_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFOA_slope <- coef(Kobayashi_2018_lm_model_PFOA)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFOA)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Kobayashi_2018_lm_model_PFNA <- lm(log_PFNA_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFNA_slope <- coef(Kobayashi_2018_lm_model_PFNA)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFNA)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Kobayashi_2018_lm_model_PFDA <- lm(log_PFDA_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFDA_slope <- coef(Kobayashi_2018_lm_model_PFDA)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFDA)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Kobayashi_2018_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean,
                                    data = Kobayashi_2018)

Kobayashi_2018_PFUnDA_slope <- coef(Kobayashi_2018_lm_model_PFUnDA)["TL_mean"]

summary(Kobayashi_2018_lm_model_PFUnDA)
```

```{r}
ggplot(Kobayashi_2018, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Kobayashi_2018_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_047: Heimstad_2024

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Heimstad_2024 <- read.csv(here("Rdata", "Heimstad_2024.csv"))

# PFOS
Heimstad_2024_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                                    data = Heimstad_2024)

Heimstad_2024_PFOS_slope <- coef(Heimstad_2024_lm_model_PFOS)["TL_mean"]

summary(Heimstad_2024_lm_model_PFOS)
```

```{r}
ggplot(Heimstad_2024, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Heimstad_2024_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Heimstad_2024_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean,
                                    data = Heimstad_2024)

Heimstad_2024_PFUnDA_slope <- coef(Heimstad_2024_lm_model_PFUnDA)["TL_mean"]

summary(Heimstad_2024_lm_model_PFUnDA)
```

```{r}
ggplot(Heimstad_2024, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Heimstad_2024_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Heimstad_2024_lm_model_PFDoDA <- lm(log_PFDoDA_mean ~ TL_mean,
                                    data = Heimstad_2024)

Heimstad_2024_PFDoDA_slope <- coef(Heimstad_2024_lm_model_PFDoDA)["TL_mean"]

summary(Heimstad_2024_lm_model_PFDoDA)
```

```{r}
ggplot(Heimstad_2024, aes(x = TL_mean, y = log_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Heimstad_2024_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_024: Li_2021

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Li_2021 <- read.csv(here("Rdata", "Li_2021.csv"))

# HFPO-TeA
Li_2021_lm_model_HFPOTeA <- lm(log_HFPO.TeA_mean ~ TL_mean,
                                    data = Li_2021)

Li_2021_HFPOTeA_slope <- coef(Li_2021_lm_model_HFPOTeA)["TL_mean"]

summary(Li_2021_lm_model_HFPOTeA)
```

```{r}
ggplot(Li_2021, aes(x = TL_mean, y = log_HFPO.TeA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [HFPOTeA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2021_HFPOTeA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# HFPO-TrA
Li_2021_lm_model_HFPOTrA <- lm(log_HFPO.TrA_mean ~ TL_mean,
                                    data = Li_2021)

Li_2021_HFPOTrA_slope <- coef(Li_2021_lm_model_HFPOTrA)["TL_mean"]

summary(Li_2021_lm_model_HFPOTrA)
```

```{r}
ggplot(Li_2021, aes(x = TL_mean, y = log_HFPO.TrA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [HFPOTrA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2021_HFPOTrA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFO5DoA
Li_2021_lm_model_PFO5DoA <- lm(log_PFO5DoA_mean ~ TL_mean,
                                    data = Li_2021)

Li_2021_PFO5DoA_slope <- coef(Li_2021_lm_model_PFO5DoA)["TL_mean"]

summary(Li_2021_lm_model_PFO5DoA)
```

```{r}
ggplot(Li_2021, aes(x = TL_mean, y = log_PFO5DoA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFO5DoA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2021_PFO5DoA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# H-PFMO2OSA
Li_2021_lm_model_HPFMO2OSA <- lm(log_H.PFMO2OSA_mean ~ TL_mean,
                                    data = Li_2021)

Li_2021_HPFMO2OSA_slope <- coef(Li_2021_lm_model_HPFMO2OSA)["TL_mean"]

summary(Li_2021_lm_model_HPFMO2OSA)
```

```{r}
ggplot(Li_2021, aes(x = TL_mean, y = log_H.PFMO2OSA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [HPFMO2OSA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2021_HPFMO2OSA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Li_2021_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                                    data = Li_2021)

Li_2021_PFOS_slope <- coef(Li_2021_lm_model_PFOS)["TL_mean"]

summary(Li_2021_lm_model_PFOS)
```

```{r}
ggplot(Li_2021, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2021_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFMOAA
Li_2021_lm_model_PFMOAA <- lm(log_PFMOAA_mean ~ TL_mean,
                                    data = Li_2021)

Li_2021_PFMOAA_slope <- coef(Li_2021_lm_model_PFMOAA)["TL_mean"]

summary(Li_2021_lm_model_PFMOAA)
```

```{r}
ggplot(Li_2021, aes(x = TL_mean, y = log_PFMOAA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFMOAA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2021_PFMOAA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFBA
Li_2021_lm_model_PFBA <- lm(log_PFBA_mean ~ TL_mean,
                                    data = Li_2021)

Li_2021_PFBA_slope <- coef(Li_2021_lm_model_PFBA)["TL_mean"]

summary(Li_2021_lm_model_PFBA)
```

```{r}
ggplot(Li_2021, aes(x = TL_mean, y = log_PFBA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFBA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Li_2021_PFBA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_025: Pan_2021

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Pan_2021 <- read.csv(here("Rdata", "Pan_2021.csv"))

# 6:2 Cl-PFESA
Pan_2021_lm_model_62ClPFESA <- lm(log_62ClPFESA_mean ~ TL_mean,
                                    data = Pan_2021)

Pan_2021_62ClPFESA_slope <- coef(Pan_2021_lm_model_62ClPFESA)["TL_mean"]

summary(Pan_2021_lm_model_62ClPFESA)
```

```{r}
ggplot(Pan_2021, aes(x = TL_mean, y = log_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [62ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Pan_2021_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Pan_2021_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                                    data = Pan_2021)

Pan_2021_PFOS_slope <- coef(Pan_2021_lm_model_PFOS)["TL_mean"]

summary(Pan_2021_lm_model_PFOS)
```

```{r}
ggplot(Pan_2021, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "Trophic level",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Pan_2021_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_059: Jiao_2023

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Jiao_2023_blood <- read.csv(here("Rdata", "Jiao_2023_blood.csv"))

# PFDA
Jiao_2023_blood_lm_model_PFDA <- lm(ln_PFDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_PFDA_slope <- coef(Jiao_2023_blood_lm_model_PFDA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_PFDA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Jiao_2023_blood_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_PFUnDA_slope <- coef(Jiao_2023_blood_lm_model_PFUnDA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_PFUnDA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Jiao_2023_blood_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_PFDoDA_slope <- coef(Jiao_2023_blood_lm_model_PFDoDA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_PFDoDA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Jiao_2023_blood_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_PFTrDA_slope <- coef(Jiao_2023_blood_lm_model_PFTrDA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_PFTrDA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Jiao_2023_blood_lm_model_PFOS <- lm(ln_PFOS_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_PFOS_slope <- coef(Jiao_2023_blood_lm_model_PFOS)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_PFOS)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# FOSA
Jiao_2023_blood_lm_model_FOSA <- lm(ln_FOSA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_FOSA_slope <- coef(Jiao_2023_blood_lm_model_FOSA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_FOSA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_FOSA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [FOSA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_FOSA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 62ClPFESA
Jiao_2023_blood_lm_model_62ClPFESA <- lm(ln_62ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_62ClPFESA_slope <- coef(Jiao_2023_blood_lm_model_62ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_62ClPFESA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [6:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 82ClPFESA
Jiao_2023_blood_lm_model_82ClPFESA <- lm(ln_82ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_82ClPFESA_slope <- coef(Jiao_2023_blood_lm_model_82ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_82ClPFESA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_82ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [8:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_82ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 102ClPFESA
Jiao_2023_blood_lm_model_102ClPFESA <- lm(ln_102ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_102ClPFESA_slope <- coef(Jiao_2023_blood_lm_model_102ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_102ClPFESA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_102ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [10:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_102ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 103FTCA
Jiao_2023_blood_lm_model_103FTCA <- lm(ln_103FTCA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_blood)

Jiao_2023_blood_103FTCA_slope <- coef(Jiao_2023_blood_lm_model_103FTCA)["delta_15N_mean"]

summary(Jiao_2023_blood_lm_model_103FTCA)
```

```{r}
ggplot(Jiao_2023_blood, aes(x = delta_15N_mean, y = ln_103FTCA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [10:3 FTCA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_blood_103FTCA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Jiao_2023_gill <- read.csv(here("Rdata", "Jiao_2023_gill.csv"))

# PFDA
Jiao_2023_gill_lm_model_PFDA <- lm(ln_PFDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_gill)

Jiao_2023_gill_PFDA_slope <- coef(Jiao_2023_gill_lm_model_PFDA)["delta_15N_mean"]

summary(Jiao_2023_gill_lm_model_PFDA)
```

```{r}
ggplot(Jiao_2023_gill, aes(x = delta_15N_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_gill_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Jiao_2023_gill_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_gill)

Jiao_2023_gill_PFDoDA_slope <- coef(Jiao_2023_gill_lm_model_PFDoDA)["delta_15N_mean"]

summary(Jiao_2023_gill_lm_model_PFDoDA)
```

```{r}
ggplot(Jiao_2023_gill, aes(x = delta_15N_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_gill_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Jiao_2023_gill_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_gill)

Jiao_2023_gill_PFTrDA_slope <- coef(Jiao_2023_gill_lm_model_PFTrDA)["delta_15N_mean"]

summary(Jiao_2023_gill_lm_model_PFTrDA)
```

```{r}
ggplot(Jiao_2023_gill, aes(x = delta_15N_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_gill_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 82ClPFESA
Jiao_2023_gill_lm_model_82ClPFESA <- lm(ln_82ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_gill)

Jiao_2023_gill_82ClPFESA_slope <- coef(Jiao_2023_gill_lm_model_82ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_gill_lm_model_82ClPFESA)
```

```{r}
ggplot(Jiao_2023_gill, aes(x = delta_15N_mean, y = ln_82ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [8:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_gill_82ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Jiao_2023_heart <- read.csv(here("Rdata", "Jiao_2023_heart.csv"))

# PFDA
Jiao_2023_heart_lm_model_PFDA <- lm(ln_PFDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_heart)

Jiao_2023_heart_PFDA_slope <- coef(Jiao_2023_heart_lm_model_PFDA)["delta_15N_mean"]

summary(Jiao_2023_heart_lm_model_PFDA)
```

```{r}
ggplot(Jiao_2023_heart, aes(x = delta_15N_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [8:2 PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_heart_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Jiao_2023_heart_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_heart)

Jiao_2023_heart_PFUnDA_slope <- coef(Jiao_2023_heart_lm_model_PFUnDA)["delta_15N_mean"]

summary(Jiao_2023_heart_lm_model_PFUnDA)
```

```{r}
ggplot(Jiao_2023_heart, aes(x = delta_15N_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [8:2 PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_heart_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Jiao_2023_heart_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_heart)

Jiao_2023_heart_PFDoDA_slope <- coef(Jiao_2023_heart_lm_model_PFDoDA)["delta_15N_mean"]

summary(Jiao_2023_heart_lm_model_PFDoDA)
```

```{r}
ggplot(Jiao_2023_heart, aes(x = delta_15N_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_heart_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Jiao_2023_heart_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_heart)

Jiao_2023_heart_PFTrDA_slope <- coef(Jiao_2023_heart_lm_model_PFTrDA)["delta_15N_mean"]

summary(Jiao_2023_heart_lm_model_PFTrDA)
```

```{r}
ggplot(Jiao_2023_heart, aes(x = delta_15N_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_heart_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 62ClPFESA
Jiao_2023_heart_lm_model_62ClPFESA <- lm(ln_62ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_heart)

Jiao_2023_heart_62ClPFESA_slope <- coef(Jiao_2023_heart_lm_model_62ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_heart_lm_model_62ClPFESA)
```

```{r}
ggplot(Jiao_2023_heart, aes(x = delta_15N_mean, y = ln_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [6:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_heart_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Jiao_2023_kidney <- read.csv(here("Rdata", "Jiao_2023_kidney.csv"))

# PFUnDA
Jiao_2023_kidney_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_kidney)

Jiao_2023_kidney_PFUnDA_slope <- coef(Jiao_2023_kidney_lm_model_PFUnDA)["delta_15N_mean"]

summary(Jiao_2023_kidney_lm_model_PFUnDA)
```

```{r}
ggplot(Jiao_2023_kidney, aes(x = delta_15N_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_kidney_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Jiao_2023_kidney_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_kidney)

Jiao_2023_kidney_PFDoDA_slope <- coef(Jiao_2023_kidney_lm_model_PFDoDA)["delta_15N_mean"]

summary(Jiao_2023_kidney_lm_model_PFDoDA)
```

```{r}
ggplot(Jiao_2023_kidney, aes(x = delta_15N_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_kidney_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Jiao_2023_kidney_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_kidney)

Jiao_2023_kidney_PFTrDA_slope <- coef(Jiao_2023_kidney_lm_model_PFTrDA)["delta_15N_mean"]

summary(Jiao_2023_kidney_lm_model_PFTrDA)
```

```{r}
ggplot(Jiao_2023_kidney, aes(x = delta_15N_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_kidney_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Jiao_2023_liver <- read.csv(here("Rdata", "Jiao_2023_liver.csv"))

# PFDA
Jiao_2023_liver_lm_model_PFDA <- lm(ln_PFDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_liver)

Jiao_2023_liver_PFDA_slope <- coef(Jiao_2023_liver_lm_model_PFDA)["delta_15N_mean"]

summary(Jiao_2023_liver_lm_model_PFDA)
```

```{r}
ggplot(Jiao_2023_liver, aes(x = delta_15N_mean, y = ln_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_liver_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Jiao_2023_liver_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_liver)

Jiao_2023_liver_PFUnDA_slope <- coef(Jiao_2023_liver_lm_model_PFUnDA)["delta_15N_mean"]

summary(Jiao_2023_liver_lm_model_PFUnDA)
```

```{r}
ggplot(Jiao_2023_liver, aes(x = delta_15N_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_liver_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Jiao_2023_liver_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_liver)

Jiao_2023_liver_PFDoDA_slope <- coef(Jiao_2023_liver_lm_model_PFDoDA)["delta_15N_mean"]

summary(Jiao_2023_liver_lm_model_PFDoDA)
```

```{r}
ggplot(Jiao_2023_liver, aes(x = delta_15N_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_liver_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Jiao_2023_liver_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_liver)

Jiao_2023_liver_PFTrDA_slope <- coef(Jiao_2023_liver_lm_model_PFTrDA)["delta_15N_mean"]

summary(Jiao_2023_liver_lm_model_PFTrDA)
```

```{r}
ggplot(Jiao_2023_liver, aes(x = delta_15N_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_liver_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 62ClPFESA
Jiao_2023_liver_lm_model_62ClPFESA <- lm(ln_62ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_liver)

Jiao_2023_liver_62ClPFESA_slope <- coef(Jiao_2023_liver_lm_model_62ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_liver_lm_model_62ClPFESA)
```

```{r}
ggplot(Jiao_2023_liver, aes(x = delta_15N_mean, y = ln_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [6:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_liver_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 82ClPFESA
Jiao_2023_liver_lm_model_82ClPFESA <- lm(ln_82ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_liver)

Jiao_2023_liver_82ClPFESA_slope <- coef(Jiao_2023_liver_lm_model_82ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_liver_lm_model_82ClPFESA)
```

```{r}
ggplot(Jiao_2023_liver, aes(x = delta_15N_mean, y = ln_82ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [8:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_liver_82ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Jiao_2023_muscle <- read.csv(here("Rdata", "Jiao_2023_muscle.csv"))

# PFDoDA
Jiao_2023_muscle_lm_model_PFDoDA <- lm(ln_PFDoDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_muscle)

Jiao_2023_muscle_PFDoDA_slope <- coef(Jiao_2023_muscle_lm_model_PFDoDA)["delta_15N_mean"]

summary(Jiao_2023_muscle_lm_model_PFDoDA)
```

```{r}
ggplot(Jiao_2023_muscle, aes(x = delta_15N_mean, y = ln_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_muscle_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Jiao_2023_muscle_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_muscle)

Jiao_2023_muscle_PFTrDA_slope <- coef(Jiao_2023_muscle_lm_model_PFTrDA)["delta_15N_mean"]

summary(Jiao_2023_muscle_lm_model_PFTrDA)
```

```{r}
ggplot(Jiao_2023_muscle, aes(x = delta_15N_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_muscle_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 62ClPFESA
Jiao_2023_muscle_lm_model_62ClPFESA <- lm(ln_62ClPFESA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_muscle)

Jiao_2023_muscle_62ClPFESA_slope <- coef(Jiao_2023_muscle_lm_model_62ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_muscle_lm_model_62ClPFESA)
```

```{r}
ggplot(Jiao_2023_muscle, aes(x = delta_15N_mean, y = ln_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [6:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_muscle_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
Jiao_2023_pancreas <- read.csv(here("Rdata", "Jiao_2023_pancreas.csv"))

# PFUnDA
Jiao_2023_pancreas_lm_model_PFUnDA <- lm(ln_PFUnDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_pancreas)

Jiao_2023_pancreas_PFUnDA_slope <- coef(Jiao_2023_pancreas_lm_model_PFUnDA)["delta_15N_mean"]

summary(Jiao_2023_pancreas_lm_model_PFUnDA)
```

```{r}
ggplot(Jiao_2023_pancreas, aes(x = delta_15N_mean, y = ln_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_pancreas_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Jiao_2023_pancreas_lm_model_PFTrDA <- lm(ln_PFTrDA_mean ~ delta_15N_mean,
                                    data = Jiao_2023_pancreas)

Jiao_2023_pancreas_PFTrDA_slope <- coef(Jiao_2023_pancreas_lm_model_PFTrDA)["delta_15N_mean"]

summary(Jiao_2023_pancreas_lm_model_PFTrDA)
```

```{r}
ggplot(Jiao_2023_pancreas, aes(x = delta_15N_mean, y = ln_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_pancreas_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 62ClPFESA
Jiao_2023_pancreas_lm_model_62ClPFESA <- lm(ln_62ClPFESA_mean ~ delta_15N_mean,
                                            data = Jiao_2023_pancreas)

Jiao_2023_pancreas_62ClPFESA_slope <- coef(Jiao_2023_pancreas_lm_model_62ClPFESA)["delta_15N_mean"]

summary(Jiao_2023_pancreas_lm_model_62ClPFESA)
```

```{r}
ggplot(Jiao_2023_pancreas, aes(x = delta_15N_mean, y = ln_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "ln [6:2 ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Jiao_2023_pancreas_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_062: Miniero_2014

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Miniero_2014 <- read.csv(here("Rdata", "Miniero_2014.csv"))

Miniero_2014_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                             data = Miniero_2014)

Miniero_2014_PFOS_slope <- coef(Miniero_2014_lm_model_PFOS)["TL_mean"]

summary(Miniero_2014_lm_model_PFOS)
```

```{r}
ggplot(Miniero_2014, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Miniero_2014_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_063: Chen_2023

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Chen_2023 <- read.csv(here("Rdata", "Chen_2023.csv"))
# PFBA
Chen_2023_lm_model_PFBA <- lm(log_PFBA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFBA_slope <- coef(Chen_2023_lm_model_PFBA)["TL_mean"]

summary(Chen_2023_lm_model_PFBA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFBA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFBA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFBA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
#PFPeA
Chen_2023_lm_model_PFPeA <- lm(log_PFPeA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFPeA_slope <- coef(Chen_2023_lm_model_PFPeA)["TL_mean"]

summary(Chen_2023_lm_model_PFPeA)
```
```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFPeA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFPeA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFPeA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHxA
Chen_2023_lm_model_PFHxA <- lm(log_PFHxA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFHxA_slope <- coef(Chen_2023_lm_model_PFHxA)["TL_mean"]

summary(Chen_2023_lm_model_PFHxA)
```
```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFHxA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFHxA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFHxA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFBS
Chen_2023_lm_model_PFBS <- lm(log_PFBS_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFBS_slope <- coef(Chen_2023_lm_model_PFBS)["TL_mean"]

summary(Chen_2023_lm_model_PFBS)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFBS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFBS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFBS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHpA
Chen_2023_lm_model_PFHpA <- lm(log_PFHpA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFHpA_slope <- coef(Chen_2023_lm_model_PFHpA)["TL_mean"]

summary(Chen_2023_lm_model_PFHpA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFHpA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFHpA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFHpA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Chen_2023_lm_model_PFOA <- lm(log_PFOA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFOA_slope <- coef(Chen_2023_lm_model_PFOA)["TL_mean"]

summary(Chen_2023_lm_model_PFOA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PF4OPeA
Chen_2023_lm_model_PF4OPeA <- lm(log_PF4OPeA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PF4OPeA_slope <- coef(Chen_2023_lm_model_PF4OPeA)["TL_mean"]

summary(Chen_2023_lm_model_PF4OPeA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PF4OPeA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PF4OPeA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PF4OPeA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Chen_2023_lm_model_PFNA <- lm(log_PFNA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFNA_slope <- coef(Chen_2023_lm_model_PFNA)["TL_mean"]

summary(Chen_2023_lm_model_PFNA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PF4OPeA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Chen_2023_lm_model_PFDA <- lm(log_PFDA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFDA_slope <- coef(Chen_2023_lm_model_PFDA)["TL_mean"]

summary(Chen_2023_lm_model_PFDA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Chen_2023_lm_model_PFOS <- lm(log_PFOS_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFOS_slope <- coef(Chen_2023_lm_model_PFOS)["TL_mean"]

summary(Chen_2023_lm_model_PFOS)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Chen_2023_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFUnDA_slope <- coef(Chen_2023_lm_model_PFUnDA)["TL_mean"]

summary(Chen_2023_lm_model_PFUnDA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 62ClPFESA
Chen_2023_lm_model_62ClPFESA <- lm(log_62ClPFESA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_62ClPFESA_slope <- coef(Chen_2023_lm_model_62ClPFESA)["TL_mean"]

summary(Chen_2023_lm_model_62ClPFESA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [62ClPFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Chen_2023_lm_model_PFDoDA <- lm(log_PFDoDA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFDoDA_slope <- coef(Chen_2023_lm_model_PFDoDA)["TL_mean"]

summary(Chen_2023_lm_model_PFDoDA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Chen_2023_lm_model_PFTrDA <- lm(log_PFTrDA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFTrDA_slope <- coef(Chen_2023_lm_model_PFTrDA)["TL_mean"]

summary(Chen_2023_lm_model_PFTrDA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFTrDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTeDA
Chen_2023_lm_model_PFTeDA <- lm(log_PFTeDA_mean ~ TL_mean,
                             data = Chen_2023)

Chen_2023_PFTeDA_slope <- coef(Chen_2023_lm_model_PFTeDA)["TL_mean"]

summary(Chen_2023_lm_model_PFTeDA)
```

```{r}
ggplot(Chen_2023, aes(x = TL_mean, y = log_PFTeDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "TL",
       y = "log [PFTeDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Chen_2023_PFTeDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_065: Yordy_2013

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Yordy_2013 <- read.csv(here("Rdata", "Yordy_2013.csv"))
# PFBA
Yordy_2013_lm_model_PFCs <- lm(log_PFCs_mean ~ delta_15N_mean,
                             data = Yordy_2013)

Yordy_2013_PFCs_slope <- coef(Yordy_2013_lm_model_PFCs)["delta_15N_mean"]

summary(Yordy_2013_lm_model_PFCs)
```

```{r}
ggplot(Yordy_2013, aes(x = delta_15N_mean, y = log_PFCs_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFCs]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Yordy_2013_PFCs_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

## S_066: Mo_2024

::: info
-   It does not provide standard error or standard deviation values of individual observations. Weights cannot be assigned.
:::

```{r}
Mo_2024 <- read.csv(here("Rdata", "Mo_2024.csv"))
# PFBA
Mo_2024_lm_model_PFBA <- lm(log_PFBA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFBA_slope <- coef(Mo_2024_lm_model_PFBA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFBA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFBA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFBA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFBA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHxA
Mo_2024_lm_model_PFHxA <- lm(log_PFHxA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFHxA_slope <- coef(Mo_2024_lm_model_PFHxA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFHxA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFHxA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFHxA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFHxA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHpA
Mo_2024_lm_model_PFHpA <- lm(log_PFHpA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFHpA_slope <- coef(Mo_2024_lm_model_PFHpA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFHpA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFHpA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFHpA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFHpA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOA
Mo_2024_lm_model_PFOA <- lm(log_PFOA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFOA_slope <- coef(Mo_2024_lm_model_PFOA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFOA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFOA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFOA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFOA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFNA
Mo_2024_lm_model_PFNA <- lm(log_PFNA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFNA_slope <- coef(Mo_2024_lm_model_PFNA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFNA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFNA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFNA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFNA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDA
Mo_2024_lm_model_PFDA <- lm(log_PFDA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFDA_slope <- coef(Mo_2024_lm_model_PFDA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFDA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFUnDA
Mo_2024_lm_model_PFUnDA <- lm(log_PFUnDA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFUnDA_slope <- coef(Mo_2024_lm_model_PFUnDA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFUnDA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFUnDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFUnDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFUnDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFDoDA
Mo_2024_lm_model_PFDoDA <- lm(log_PFDoDA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFDoDA_slope <- coef(Mo_2024_lm_model_PFDoDA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFDoDA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFDoDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFDoDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTrDA
Mo_2024_lm_model_PFTrDA <- lm(log_PFTrDA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFTrDA_slope <- coef(Mo_2024_lm_model_PFTrDA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFTrDA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFTrDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFDoDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFTrDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFTeDA
Mo_2024_lm_model_PFTeDA <- lm(log_PFTeDA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFTeDA_slope <- coef(Mo_2024_lm_model_PFTeDA)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFTeDA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFTeDA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFTeDA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFTeDA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFBS
Mo_2024_lm_model_PFBS <- lm(log_PFBS_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFBS_slope <- coef(Mo_2024_lm_model_PFBS)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFBS)
```
```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFBS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFBS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFBS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHxS
Mo_2024_lm_model_PFHxS <- lm(log_PFHxS_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFHxS_slope <- coef(Mo_2024_lm_model_PFHxS)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFHxS)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFHxS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFHxS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFHxS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFHpS
Mo_2024_lm_model_PFHpS <- lm(log_PFHpS_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFHpS_slope <- coef(Mo_2024_lm_model_PFHpS)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFHpS)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFHpS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFHpS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFHpS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# PFOS
Mo_2024_lm_model_PFOS <- lm(log_PFOS_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_PFOS_slope <- coef(Mo_2024_lm_model_PFOS)["delta_15N_mean"]

summary(Mo_2024_lm_model_PFOS)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_PFOS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [PFOS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_PFOS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# HFPO_DA
Mo_2024_lm_model_HFPO_DA <- lm(log_HFPO_DA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_HFPO_DA_slope <- coef(Mo_2024_lm_model_HFPO_DA)["delta_15N_mean"]

summary(Mo_2024_lm_model_HFPO_DA)
```
```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_HFPO_DA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [HFPO-DA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_HFPO_DA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# HFPO_TrA
Mo_2024_lm_model_HFPO_TrA <- lm(log_HFPO_TrA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_HFPO_TrA_slope <- coef(Mo_2024_lm_model_HFPO_TrA)["delta_15N_mean"]

summary(Mo_2024_lm_model_HFPO_TrA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_HFPO_TrA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [HFPO-TrA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_HFPO_TrA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 62ClPFESA
Mo_2024_lm_model_62ClPFESA <- lm(log_62ClPFESA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_62ClPFESA_slope <- coef(Mo_2024_lm_model_62ClPFESA)["delta_15N_mean"]

summary(Mo_2024_lm_model_62ClPFESA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_62ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [6:2 Cl-PFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_62ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# 82ClPFESA
Mo_2024_lm_model_82ClPFESA <- lm(log_82ClPFESA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_82ClPFESA_slope <- coef(Mo_2024_lm_model_82ClPFESA)["delta_15N_mean"]

summary(Mo_2024_lm_model_82ClPFESA)
```
```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_82ClPFESA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [8:2 Cl-PFESA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_82ClPFESA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# FOSA
Mo_2024_lm_model_FOSA <- lm(log_FOSA_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_FOSA_slope <- coef(Mo_2024_lm_model_FOSA)["delta_15N_mean"]

summary(Mo_2024_lm_model_FOSA)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_FOSA_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [FOSA]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_FOSA_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```

```{r}
# OBS
Mo_2024_lm_model_OBS <- lm(log_OBS_mean ~ delta_15N_mean,
                             data = Mo_2024)

Mo_2024_OBS_slope <- coef(Mo_2024_lm_model_OBS)["delta_15N_mean"]

summary(Mo_2024_lm_model_OBS)
```

```{r}
ggplot(Mo_2024, aes(x = delta_15N_mean, y = log_OBS_mean)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "red", linewidth = 0.5) +
  labs(x = "delta 15N",
       y = "log [OBS]") +
  theme_minimal() +
  annotate("text", x = Inf, y = Inf, label = paste("slope =", round(Mo_2024_OBS_slope, 3)), 
           hjust = 3, vjust = 5.5, size = 4, color = "red")
```


# References

-  Barghi_2018: Barghi, M., Jin, X., Lee, S., Jeong, Y., Yu, J. P., Paek, W. K., & Moon, H. B. (2018). Accumulation and exposure assessment of persistent chlorinated and fluorinated contaminants in Korean birds. Science of The Total Environment, 645, 220-228.
-  Cara_2022: Cara, B., Lies, T., Thimo, G., Robin, L., & Lieven, B. (2022). Bioaccumulation and trophic transfer of perfluorinated alkyl substances (PFAS) in marine biota from the Belgian North Sea: distribution and human health risk implications. Environmental Pollution, 311, 119907.
-  Chen_2018: Chen, H., Han, J., Cheng, J., Sun, R., Wang, X., Han, G., ... & He, X. (2018). Distribution, bioaccumulation and trophic transfer of chlorinated polyfluoroalkyl ether sulfonic acids in the marine food web of Bohai, China. Environmental Pollution, 241, 504-510.
-  Chen, Z., Zhang, J., Diao, J., Su, C., Sun, Q., Zhou, Y., ... & Wang, T. (2023). Bioaccumulation and risk mitigation of legacy and novel perfluoroalkyl substances in seafood: Insights from trophic transfer and cooking method. Environment International, 177, 108023.
-  Du_2021: Du, D., Lu, Y., Zhou, Y., Li, Q., Zhang, M., Han, G., ... & Jeppesen, E. (2021). Bioaccumulation, trophic transfer and biomagnification of perfluoroalkyl acids (PFAAs) in the marine food web of the South China Sea. Journal of hazardous materials, 405, 124681.
-  Gao_2020: Gao, K., Miao, X., Fu, J., Chen, Y., Li, H., Pan, W., ... & Jiang, G. (2020). Occurrence and trophic transfer of per-and polyfluoroalkyl substances in an Antarctic ecosystem. Environmental Pollution, 257, 113383.
-  Heimstad_2024: Heimstad, E. S., Nygrd, T., Moe, B., & Herzke, D. (2024). New insights from an eight-year study on per-and polyfluoroalkyl substances in an urban terrestrial ecosystem. Environmental Pollution, 347, 123735.
-  Jiao_2023: Jiao, Z., Yu, N., Mao, J., Yang, Q., Jiao, L., Wang, X., ... & Wei, S. (2023). The occurrence, tissue distribution, and PBT potential of per-and polyfluoroalkyl substances in the freshwater organisms from the Yangtze river via nontarget analysis. Journal of Hazardous Materials, 458, 131868.
-  Kobayashi_2018: Kobayashi, J., Maeda, Y., Imuta, Y., Ishihara, F., Nakashima, N., Komorita, T., & Sakurai, T. (2018). Bioaccumulation patterns of perfluoroalkyl acids in an estuary of the Ariake Sea, Japan. Bulletin of environmental contamination and toxicology, 100, 536-540.
-  Koch_2020: Koch, A., Jonsson, M., Yeung, L. W., Karrman, A., Ahrens, L., Ekblad, A., & Wang, T. (2020). Per-and polyfluoroalkyl-contaminated freshwater impacts adjacent riparian food webs. Environmental Science & Technology, 54(19), 11951-11960.
-  Koch_2021: Koch, A., Jonsson, M., Yeung, L. W., Karrman, A., Ahrens, L., Ekblad, A., & Wang, T. (2021). Quantification of biodriven transfer of per-and polyfluoroalkyl substances from the aquatic to the terrestrial environment via emergent insects. Environmental Science & Technology, 55(12), 7900-7909.
-  Li_2008: Li, X., Yeung, L. W. Y., Xu, M., Taniyasu, S., Lam, P. K., Yamashita, N., & Dai, J. (2008). Perfluorooctane sulfonate (PFOS) and other fluorochemicals in fish blood collected near the outfall of wastewater treatment plant (WWTP) in Beijing. Environmental Pollution, 156(3), 1298-1303.
-  Li_2021: Li, Y., Yao, J., Zhang, J., Pan, Y., Dai, J., Ji, C., & Tang, J. (2021). First report on the bioaccumulation and trophic transfer of perfluoroalkyl ether carboxylic acids in estuarine food web. Environmental Science & Technology, 56(10), 6046-6055.
-  Liu_2018: Liu, W., He, W., Wu, J., Qin, N., He, Q., & Xu, F. (2018). Residues, bioaccumulations and biomagnification of perfluoroalkyl acids (PFAAs) in aquatic animals from Lake Chaohu, China. Environmental Pollution, 240, 607-614.
-  Mazzoni_2020: Mazzoni, M., Ferrario, C., Bettinetti, R., Piscia, R., Cicala, D., Volta, P., ... & Polesello, S. (2020). Trophic magnification of legacy (PCB, DDT and Hg) and emerging pollutants (PFAS) in the fish community of a small protected Southern Alpine Lake (Lake Mergozzo, Northern Italy). Water, 12(6), 1591.
-  Miniero_2014: Miniero, R., Abate, V., Brambilla, G., Davoli, E., De Felip, E., De Filippis, S. P., ... & Di Domenico, A. (2014). Persistent toxic substances in Mediterranean aquatic species. Science of the total environment, 494, 18-27.
-  Mo_2024: Mo, L., Wan, N., Zhou, B., Shao, M., Zhang, X., Li, M., ... & Mai, B. (2024). Per-and polyfluoroalkyl substances in waterbird feathers around Poyang Lake, China: Compound and species-specific bioaccumulation. Ecotoxicology and Environmental Safety, 273, 116141.
-  Pan_2010: Pan, Y., Shi, Y., Wang, Y., Cai, Y., & Jiang, G. (2010). Investigation of perfluorinated compounds (PFCs) in mollusks from coastal waters in the Bohai Sea of China. Journal of Environmental Monitoring, 12(2), 508-513.
-  Pan_2021: Pan, C. G., Xiao, S. K., Yu, K. F., Wu, Q., & Wang, Y. H. (2021). Legacy and alternative per-and polyfluoroalkyl substances in a subtropical marine food web from the Beibu Gulf, South China: Fate, trophic transfer and health risk assessment. Journal of Hazardous Materials, 403, 123618.
-  Ren_2022: Ren, J., Point, A. D., Baygi, S. F., Fernando, S., Hopke, P. K., Holsen, T. M., & Crimmins, B. S. (2022). Bioaccumulation of polyfluoroalkyl substances in the Lake Huron aquatic food web. Science of The Total Environment, 819, 152974.
-  Van de Vijver_2003: Van de Vijver, K. I., Hoff, P. T., Das, K., Van Dongen, W., Esmans, E. L., Jauniaux, T., ... & De Coen, W. (2003). Perfluorinated chemicals infiltrate ocean waters: link between exposure levels and stable isotope ratios in marine mammals. Environmental science & technology, 37(24), 5545-5550.